### 2014-05-01 doc/ProposalSrc/lostvaults.tex
Updated Proposal PDF and added pdf + laTeX source to documents folder.

\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png}

\title{The Lost Vaults: Uneasy Alliance\\\small{An online multi-user Dungeon Client and Server.}\\\small{Project Proposal for group 4}}

\author{Felix Färjsjö\\(19911225-4678) \and Jimmy Holm\\(19870928-0138) \and Fredrik Larsson\\(19890422-0590) \and Anna Nilsson\\(19910804-0628) \and Philip Åkerfeldt\\(19920508-1335)}

\date{\today\\Version 1.0}

\begin{document}
\maketitle
\newpage
\begin{abstract}
A proposal for implementing a concurrent server model as the basis for an online, multi-user dungeon role playing game in Scala.
\end{abstract}

\tableofcontents

\section{Introduction}
The final product of this project will be a fully functional and interactive multiplayer online role playing game, or MORPG, called The Lost Vaults.

The main challenges that we expect to face are writing network code as well as learning a new programming language.

The relation between the concept of concurrency and our project is the ability to have more than one player active in the game at the same time and their interaction with each other.

The game is a semi-traditional MUD, in which users connect to a central server and get the ability of interacting with other players and take on quests in parties. The game takes place in one of two locations, the city and the dungeon - the city being where the players may recoup from previous adventures, restock on supplies and form parties to delve back into the dungeon. The second location is the dungeon, a procedurally generated set of rooms populated with monsters, traps and treasures. The dungeon is procedurally generated and instanced in such a way that each party of players has its own dungeon, uniquely generated when the party delves down into the magical caves underneath the city. Once inside, the party is given one or several quests they should take on while exploring.

A quest can be finding an object and bringing it back to the surface, killing a number of monsters or collecting a set amount of gold. The party works together to accomplish the goals, but at the same time only one of the party members reaps the rewards, making the party a tense and fragile alliance of rogues. Gold earned in the dungeon can be spent in the city on equipment and consumables to increase the player’s chance of surviving in the dungeon and taking on more difficult and threatening monsters.
\part{Design}
\section{System Architecture}
The system architecture is in this document divided into  Client-side archiecture and Server-side architecture. Being written in Scala, the application runs in the Java Virtual Machine and as such, both client and server should be able to run on any platform supporting Java VM 1.7.
\subsection{Client-side}
The design goal for the Lost Vaults client is to create something akin to a remote terminal, where no logic is performed beyond sending requests, and receiving and interpreting request responses. Ultimately, we aim to accomplish a client-side implementation that is easily extensible when the server's implementation of game logic increases, i.e. a system we can add to by simply adding new requests and responses.
\begin{figure}[hbt]
\centering
\includegraphics[width=1.0\textwidth]{clientmockup}
\caption{\label{fig:Client}User Interface mockup of the Lost Vaults Client.}
\end{figure}
As seen in Figure \ref{fig:Client} the client window is divided into several text areas displaying relevant information to the player. The main area is for regular server responses and will contain for example room descriptions, player chat messages, system information messages and similar.
The right side of the client is reserved for persistent information that the player may need to quickly reference. The top division contains information about the player's own character, listing the player's health and combat stats as well as the group's remaining food.

The bottom om the window contains the command input field, where the player types in commands in accordance to a strict syntax listed under the server architecture below.
Upon starting the client, the player is faced with the login window shown in the center of the mockup, where the player can enter their username and password as well as the server IP address to connect to.

The client GUI will be implemented using Java's Swing UI library and integrated into Scala to utilize Akka's TCP capabilities, as shown in figure \ref{fig:ClientArch}.
\begin{figure}[hbt]
\centering
\caption{\label{fig:ClientArch}[TODO: Insert Client-system architecture figure]}
\end{figure}
\subsection{Server-side}
The server-side system architecture is further divided into the sections Concurrency model, Actor Model and Class Model. The first describes our choice of concurrency model and the 
reasoning behind it, the second describes  the function of the five major actor types of the Lost Vaults server and the final gives a more in-depth description of the 
class relationships used by the server.
\subsubsection{Concurrency Model}
We are opting to use the Actor Model for the project as we during our initial design discussion managed to isolate behaviour into several smaller and largely independent sections, 
which could with ease be made to share data only through message passing and thus avoiding the problem of deadlocks by removing shared data from the equation.

In order to implement this kind of system with the greatest efficiency, we have chosen Scala as the language for the server as scalability is one of the fundamental design goals 
of the language. We then decided to use Akka as our actor library and to make use of Akka's TCP library for network communication. Akka's TCP library and its ease of use also 
guided our decision towards choosing Scala as the language of choice even for the client, as mentioned in the previous section.

\subsubsection{Actor Model}
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{serveractormodel}
\caption{\label{fig:ServerActorModel}Diagram of the server actors' interactions.}
\end{figure}
The server side is divided up into several processes using Akka's actor library to enforce the actor concurrency model in accordance with figure \ref{fig:ServerActorModel}. Only two types 
of actors communicate directly with the network through TCP/IP, the Connection Manager actor and the Player actors. The Connection Manager actor serves as the entry point for incoming
connections, and is in charge of spawning Player actors as new top-level actors before registering them as the newly established connection's listener. As the listener, the Player actor
will receive and send data over the network through the established connection. The Player actor is in charge of all things related to the clients, such as the specific player's attributes,
is in charge of verifying login attempts through communication with the PlayerMap and it is through the Player actors that the other actors can send messages over the network when necessary.

The PlayerMap actor and GroupMap actor serves two specific utility functions, the first of which is to map a string, the names of all connected players, to the actors controlling the player 
with that name. Through this actor, another actor can quickly and easily send messages to a specific actor based on its name - an important feature for commands acting on other players, 
such as \textit{WHISPER}. It also allows a quick and simple way for the Player actor to ensure no more than one player of a given name exists on the server at any given time.

The GroupMap actor performs a similar function as PlayerMap, however it links player names with player groups instead of player actors. A player group, as described in the game design 
section of this document, is a collection of one or more players who together can enter a dungeon that is procedurally generated for them. The purpose of this actor is to facilitate 
forming and joining other groups of players. Using the GroupMap, it is enough to join a player by name to be included into that player's group, or have a new group formed for them.

The fourth type of actor used by the Lost Vaults server is the Dungeon actor, the actor performing all game logic. There is a special case of Dungeon actor which is called the City actor, 
which is a Dungeon actor that is persistent over the lifetime of the server and has special behaviour to handle the socializing aspect of chatting and forming groups as well as trading 
with NPC merchants. The ordinary case of the Dungeon Actor is in charge of generating and handling a procedural dungeon of multiple, interconnected rooms layed out in a two-dimensional 
grid. It is in these dungeon rooms that players will have the ability to complete quests, find treasure, etc. The Dungeon actor is in charge of coordinating all the players that are 
currently present in the dungeon, and make sure that commands such as \textit{SAY} are relayed to the relevant players. With the exception of the City actor, the Dungeon actors are 
in charge of their own lifespan after having been spawned by the City actor, and a Dungeon actor will stop itself once there are no more players within it.
\subsubsection{Class Model}
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{serveruml1}
\caption{\label{fig:ServerUML}The server's class relationship model.}
\end{figure}
Figure \ref{fig:ServerUML} show the relationship between the different classes of the Lost Vaults server implementation and the multiplicity of relevant relationships. They are divided 
into three categories; the Utility Layer, the Network Communicators and the Game Logic. The Utility Layer provide supporting functionality to the other classes and exactly one of each 
class should exist at any given time. The Network Communicators are the ones that relate back to the network through Akka's TCP library. Of the two, ConMan, the connection manager class, 
is to be considered a singleton and only one instance should exist at any given time. The Player class however has one instance for each open connection.

The Game Logic section contains all the internal classes as well as the Dungeon class. The Dungeon class is the bridge between the Network Communicators and the Game Logic and it is 
only through a Dungeon class that a Player can perform any actions apart from the server-wide \textit{WHISPER} command. The Dungeon class keeps track of explored and unexplored rooms, 
quests, groups, objects and NPCs. The Dungeon also keeps track of all Players currently connected and associated with the given dungeon.
\subsection{Network Messages}
\begin{center}
\begin{tabular}{|l|c|l|}
\hline
Message & Direction & Description\\
\hline
\textit{SAY [msg]} & Client $\rightarrow$ Server & Chat message sent from client to server.\\
\hline
\textit{SAY [name] [msg]} & Client $\leftarrow$ Server & The Chat message sent by [name] and relayed to the relevant clients.\\
\hline
\textit{WHISPER [to] [msg]} & Client $\rightarrow$ Server & A private message sent from a player to another player named [to].\\
\hline
\textit{WHISPER [from] [to] [msg]} & Client $\leftarrow$ Server & A private message sent from a player named [from], to another player named [to].\\
\hline
\textit{LOGIN [name]} & Client $\rightarrow$ Server & A request to sign onto the server using [name] as the player's username.\\
\hline
\textit{LOGINOK} & Client $\leftarrow$ Server & Response from server that a login request has been accepted.\\
\hline
\textit{LOGINFAIL} & Client $\leftarrow$ Server & Response from server that a login request has been denied.\\
\hline
[TODO: & Insert the rest & of the messages.]\\
\hline
\end{tabular}
\end{center}
\section{Game Design}
[TODO: Describe game design here!]
\part{Development Process}
\section{Development Tools}
For this project we intend to use a number of tools that we see fit for the project.
Since we will be working in Scala we will be writing our code in Eclipse. The reason we chose Eclipse was because it is, according to us, by far the easiest way to develop code when writing in Java or Scala. Since all of the development of the code will be done in Eclipse there will be no need to worry about using Make or a similar tool to automatically build software since that feature is already a pre-existing part of the program.

To handle the version control we intend to use the reliable and well known tool Git. We will most certainly use the repository previously created by our group to host the files for the project. The reason we chose Git was mainly because all of the members of the project are well acquainted with the tool and we have been encouraged to use the tool in previous projects.
For the testing of our code we will use JUnit since we will be working in an environment that is very similar to Java.

For assembling our documentation we will use Scaladoc since it is a tool we are all familiar with and it’s also pleasant to be able to put our efforts elsewhere and focus on more important parts.

\section{Process evaluation}
We applied the Osborn principles for brainstorming with a small addition to the process. In the brainstorming process we went around the table and each group member had to add at least a couple of ideas before we let anyone who had an idea add them to the list of possible ideas. This led to many ideas which might lead to other group members coming up with new ideas from the proposed idea.

The initial brainstorming went as expected with a long list of possible project ideas as the result. No ideas were criticised during the brainstorming and all the group members' ideas were shared. Nothing specific could be improved about our brainstorming session.

During the brainstorming session three main project ideas were presented. The first idea was to make an online multiplayer game and the two others were simulation programs, one to simulate the traffic situation in a city and one to simulate an ecosystem. We divided the group into three focus groups that looked deeper into these three options. After this, each group were given time to present their respective fields, and after discussing pros and cons for the potential of each idea, we decided to choose the online multiplayer game. The reasons for this was that the complexity was intriguing, and that there was potential to develop the game further in case of extra time. Some of the interesting parts of the online game, besides being the most fun, was to learn about networking and our chosen programming language, Scala.

Focusing on quantity in the first stage of brainstorming led to a good brainstorming process with plenty of ideas and doing so we found that it was easier to decide on a high quality idea when ideas could be put on the table and refined by the group as a whole, rather than feeling that any idea had to be fully formed before being suggested.

\end{document}

### 2014-05-01 doc/index.js
Cleanup doc folder.

@@ -1,1 +1,0 @@
-Index.PACKAGES = {"lostvaults" : [{"object" : "lostvaults\/Parser$.html", "name" : "lostvaults.Parser"}], "lostvaults.client" : [{"object" : "lostvaults\/client\/ConnClosed$.html", "name" : "lostvaults.client.ConnClosed"}, {"class" : "lostvaults\/client\/GUI.html", "name" : "lostvaults.client.GUI"}, {"object" : "lostvaults\/client\/main$.html", "name" : "lostvaults.client.main"}, {"trait" : "lostvaults\/client\/MyMsg.html", "name" : "lostvaults.client.MyMsg"}, {"object" : "lostvaults\/client\/Ok$.html", "name" : "lostvaults.client.Ok"}, {"object" : "lostvaults\/client\/playGame$.html", "class" : "lostvaults\/client\/playGame.html", "name" : "lostvaults.client.playGame"}, {"class" : "lostvaults\/client\/playGameCommunication.html", "name" : "lostvaults.client.playGameCommunication"}, {"case class" : "lostvaults\/client\/Print.html", "name" : "lostvaults.client.Print"}, {"object" : "lostvaults\/client\/ShutDown$.html", "name" : "lostvaults.client.ShutDown"}, {"object" : "lostvaults\/client\/TCPClientxxx$.html", "class" : "lostvaults\/client\/TCPClientxxx.html", "name" : "lostvaults.client.TCPClientxxx"}], "lostvaults.server" : [{"class" : "lostvaults\/server\/ConMan.html", "name" : "lostvaults.server.ConMan"}, {"trait" : "lostvaults\/server\/ConManMsg.html", "name" : "lostvaults.server.ConManMsg"}, {"object" : "lostvaults\/server\/ConManShutDown$.html", "name" : "lostvaults.server.ConManShutDown"}, {"class" : "lostvaults\/server\/Dungeon.html", "name" : "lostvaults.server.Dungeon"}, {"object" : "lostvaults\/server\/DungeonMakeCity$.html", "name" : "lostvaults.server.DungeonMakeCity"}, {"case class" : "lostvaults\/server\/GameAddPlayer.html", "name" : "lostvaults.server.GameAddPlayer"}, {"case class" : "lostvaults\/server\/GameMoveToDungeon.html", "name" : "lostvaults.server.GameMoveToDungeon"}, {"trait" : "lostvaults\/server\/GameMsg.html", "name" : "lostvaults.serve
[…]

### 2014-05-02 doc/ProposalSrc/lostvaults.tex

@@
 \usepackage{graphicx}
+\usepackage{appendix}
+\usepackage{longtable}
 \DeclareGraphicsExtensions{.png}
@@
 
-\date{\today\\Version 1.0}
+\date{\today\\Version 2.0}
 
@@
 \tableofcontents
-
+\listoffigures
+\newpage
 \section{Introduction}
@@
 Being written in Scala, the application runs in the Java Virtual Machine and as such, both client and server should be able to run on any platform supporting Java VM 1.7.
-\subsection{Client-side}
-The design goal for the Lost Vaults client is to create something akin to a remote terminal, where no logic is performed beyond sending requests, and receiving and interpreting request responses.
-Ultimately, we aim to accomplish a client-side implementation that is easily extensible when the server's implementation of game logic increases, i.e.
-a system we can add to by simply adding new requests and responses.
 \begin{figure}[hbt]
@@
 \end{figure}
+\subsection{Client-side}
+The design goal for the Lost Vaults client is to create something akin to a remote terminal, where no logic is performed beyond sending requests, and receiving and interpreting request responses.
+Ultimately, we aim to accomplish a client-side implementation that is easily extensible when the server's implementation of game logic increases, i.e.
+a system we can add to by simply adding new requests and responses.
+
 As seen in Figure \ref{fig:Client} the client window is divided into several text areas displaying relevant information to the player.
@@
 
-The bottom om the window contains the command input field, where the player types in commands in accordance to a strict syntax listed under the server architecture below.
+The bottom of the window contains the command input field, where the player types in commands in accordance to a strict syntax listed under the server architecture below.
 Upon starting the client, the player is faced with the login window shown in the center of the mockup, where the player can enter their username and password as well as the server IP address to connect to.
 
-The client GUI will be implemented using Java's Swing UI library and integrated into Scala to utilize Akka's TCP capabilities, as shown in figure \ref{fig:ClientArch}.
+The client GUI will be implemented using Java's Swing UI library and integrated into Scala to utilize Akka's TCP capabilities.
+\subsubsection{Class Model}
+The client is structured up into four distinct classes as described by figure \ref{fig:ClientArch}.
+The classes PlayGame and PlayGameCommunication work together to create a bridge between the TCP layer and the GUI, with PlayGame accepting messages from TCPClient and passing it along to the GUI through PlayGameCommunication.
+Likewise, the GUI sends data over the network  using method calls in PlayGameCommunication which passes it along to PlayGame and then TCPClient.
 \begin{figure}[hbt]
 \centering
-\caption{\label{fig:ClientArch}[TODO: Insert Client-system architecture figure]}
+\includegraphics[width=1.0\textwidth]{clientuml1}
+\caption{\label{fig:ClientArch}Client class relationship model.}
 \end{figure}
@@
 quests, groups, objects and NPCs. The Dungeon also keeps track of all Players currently connected and associated with the given dungeon.
-\subsection{Network Messages}
-\begin{center}
-\begin{tabular}{|l|c|l|}
-\hline
-Message & Direction & Description\\
-\hline
-\textit{SAY [msg]} & Client $\rightarrow$ Server & Chat message sent from client to server.\\
-\hline
-\textit{SAY [name] [msg]} & Client $\leftarrow$ Server & The Chat message sent by [name] and relayed to the relevant clients.\\
-\hline
-\textit{WHISPER [to] [msg]} & Client $\rightarrow$ Server & A private message sent from a player to another player named [to].\\
-\hline
-\textit{WHISPER [from] [to] [msg]} & Client $\leftarrow$ Server & A private message sent from a player named [from], to another player named [to].\\
-\hline
-\textit{LOGIN [name]} & Client $\rightarrow$ Server & A request to sign onto the server using [name] as the player's username.\\
-\hline
-\textit{LOGINOK} & Client $\leftarrow$ Server & Response from server that a login request has been accepted.\\
-\hline
-\textit{LOGINFAIL} & Client $\leftarrow$ Server & Response from server that a login request has been denied.\\
-\hline
-[TODO: & Insert the rest & of the messages.]\\
-\hline
-\end{tabular}
-\end{center}
 \section{Game Design}
@@
 Focusing on quantity in the first stage of brainstorming led to a good brainstorming process with plenty of ideas and doing so we found that it was easier to decide on a high quality idea when ideas could be put on the table and refined by the group as a whole, rather than feeling that any idea had to be fully formed before being suggested.
+\newpage
+\part{Appendices}
+\begin{appendices}
+\section{Network Messages}\label{app:NetworkMessages}
+\begin{longtable}{|l|c|p{8 cm}|}
+\hline
+Message & Direction & Description\\
+\hline
+\endhead
+\textit{SAY [msg]} & Client $\rightarrow$ Server & Chat message sent from client to server.\\
+\hline
+\textit{SAY [name] [msg]} & Client $\leftarrow$ Server & The Chat message sent by [name] and relayed to the relevant clients.\\
+\hline
+\textit{WHISPER [to] [msg]} & Client $\rightarrow$ Server & A private message sent from a player to another player named [to].\\
+\hline
+\textit{WHISPER [from] [to] [msg]} & Client $\leftarrow$ Server & A private message sent from a player named [from], to another player named [to].\\
+\hline
+\textit{LOGIN [name]} & Client $\rightarrow$ Server & A request to sign onto the server using [name] as the player's username.\\
+\hline
+\textit{LOGINOK} & Client $\leftarrow$ Server & Response from server that a login request has been accepted.\\
+\hline
+\textit{LOGINFAIL} & Client $\leftarrow$ Server & Response from server that a login request has been denied.\\
+\hline
+\textit{BYE} & Client $\leftarrow$ Server & Connection Closed message sent from server to client.\\
+\hline
+\textit{SYSTEM} & Client $\leftarrow$ Server & System mesage sent from the server to the client.\\
+\hline
+\textit{INVENTORY} & Client $\rightarrow$ Server & Request from a client to list a player's current inventory.\\
+\hline
+\textit{INVENTORY [list]} & Client $\leftarrow$ Server & Response to a client's inventory request. [list] is a comma delimited list of item names.\\
+\hline
+\textit{ROOMENTER [name]} & Client $\leftarrow$ Server & Notification that a player named [name] has entered the room which the client receiving the message is in.\\
+\hline
+\textit{ROOMLEAVE [name]} & Client $\leftarrow$ Server & Notification that a player named [name] has left the room which the client receiving the message is in.\\
+\hline
+\textit{ROOMLIST [list]} & Client $\leftarrow$ Server & Notification that the list of players in the client's current room should be repopulated. [list] is a space-delimited list of names.\\
+\hline
+\textit{ROOMITEMS [list]} & Client $\leftarrow$ Server & Notification of all the items in the current room. [list] is a comma delimited list of all the items in the room.\\
+\hline
+\textit{ROOMDESC [description} & Client $\leftarrow$ Server & Notification of the client's current room's description.\\
+\hline
+\textit{ROOMEXITS [list]} & Client $\leftarrow$ Server & Notification of all possible exits from the client's current room.\\
+\hline
+\textit{DESCRIBE} & Client $\rightarrow$ Server & Request for a room description of the client's current room.\\
+\hline
+\textit{ITEMS} & Client $\rightarrow$ Server & Request for a list of items in the client's current room.\\
+\hline
+\textit{EXITS} & Client $\rightarrow$ Server & Request for a list of exits in the client's current room.\\
+\hline
+\textit{HELP} & Client $\rightarrow$ Server & Request for a list of available commands and their descriptions.\\
+\hline
+\textit{DUNGEONENTER [name]} & Client $\leftarrow$ Server & Notification that a player named [name] has entered the same dungeon the client is currently in.\\
+\hline
+\textit{DUNGEONLEAVE [name]} & Client $\leftarrow$ Server & Notification that a player named [name] has left the room which the client receiving the message is in.\\
+\hline
+\textit{DUNGEONLIST [list]} & Client $\leftarrow$ Server & Notification that the list of players in the client's current room should be repopulated. [list] is a space-delimited list of names.\\
+\hline
+\end{longtable}
+\end{appendices}
 

### 2014-05-02 src/lostvaults/client/Main.scala
Fixed refactoring problems.

@@ -1,7 +1,7 @@
 package lostvaults.client
 import akka.actor.{ Actor, ActorRef, ActorSystem, Props, Terminated }
 
-object main {
+object Main {
   val system = ActorSystem("GameClient")
   var Running = true
 

### 2014-05-02 src/lostvaults/client/PlayGame.scala

@@ -8,7 +8,7 @@ object playGame {
 }
 
 class playGame extends Actor {
-  val TCPActorRef = context.actorOf(TCPClientxxx.props(self))
+  val TCPActorRef = context.actorOf(TCPClient.props(self))
   val game = playGameCommunication
   game.setGame(this)
 

### 2014-05-02 src/lostvaults/client/TCPClient.scala

@@ -11,11 +11,11 @@ case object ConnClosed extends MyMsg
 case object ShutDown extends MyMsg
 case object Ok extends MyMsg
 
-object TCPClientxxx {
-  def props(listener: ActorRef): Props = Props(new TCPClientxxx(listener))
+object TCPClient {
+  def props(listener: ActorRef): Props = Props(new TCPClient(listener))
 }
 
-class TCPClientxxx(listener: ActorRef) extends Actor {
+class TCPClient(listener: ActorRef) extends Actor {
   import Tcp._
   import context.system
   val manager = IO(Tcp)

### 2014-05-02 src/lostvaults/server/Dungeon.scala

@@ -9,7 +9,7 @@ import lostvaults.Parser
  */
 case object DungeonMakeCity
 /**
- * Dungeon is an actor class in charge of carrying the main logic of the game,
+ * Dungeon is an actor class in charge of carrying the Main logic of the game,
  *  either as a dungeon or as the special-case City actor. The dungeon allows for
  *  interaction between players, such as chatting etc, while making sure that
  *  players who are not in the same logical space cannot interact with each other.
@@ -18,7 +18,7 @@ class Dungeon extends Actor {
   import context.become
   import scala.collection.mutable.Set
   var PSet: Set[String] = Set()
-  val PMap = main.PMap.get
+  val PMap = Main.PMap.get
   def receive() = {
     case DungeonMakeCity => {
       become(CityReceive)

### 2014-05-02 src/lostvaults/server/Main.scala

@@ -1,9 +1,8 @@
 package lostvaults.server
 import akka.actor.{ActorSystem, ActorRef, Props, Inbox}
-import akka.pattern.ask
 import scala.concurrent.duration._
 import akka.util.Timeout
-object main {
+object Main {
   var PMap: Option[ActorRef] = None
   val system = ActorSystem("LostVaultsServer")
   var City: Option[ActorRef] = None

### 2014-05-02 src/lostvaults/server/Player.scala

@@ -8,7 +8,7 @@ class Player extends Actor {
   import Tcp._
   import context.{ system, become, unbecome }
   var connection = self
-  val PMap = main.PMap.get
+  val PMap = Main.PMap.get
   var name = ""
   var dungeon = self
   var whisperTo = ""
@@ -32,7 +32,7 @@ class Player extends Actor {
           } else {
             connection ! Write(ByteString("LoginOk"))
             PMap ! PMapAddPlayer(name, self)
-            dungeon = main.City.get
+            dungeon = Main.City.get
             dungeon ! GameAddPlayer(name)
             become(LoggedIn)
           }

### 2014-05-03 src/lostvaults/client/GUI.java
Fixed GUI. Only missing is stats.

@@ -8,145 +8,366 @@ import java.awt.event.*;
 public class GUI {
 
 
-	String name;
+    String name;
 
-	int screenWidth;
-	int screenHeight;
+    int screenWidth;
+    int screenHeight;
 
-	JTextArea dynamicInfo = new JTextArea();
-	JTextField commandInputField = new JTextField();
-	JTextArea staticInfo = new JTextArea();
-	JLabel stats = new JLabel();
-	JFrame window = new JFrame("The Lost Vaults");
-	public String getName() { return name; }
-	public GUI() {
-		// / Set fonts on frames above
-		Font font = new Font("Serif", Font.BOLD + Font.ITALIC, 14);
-		dynamicInfo.setFont(font);
-		dynamicInfo.setForeground(new Color(0x3D1515));
-		commandInputField.setFont(font);
-		staticInfo.setFont(font);
-		staticInfo.setForeground(new Color(0x3D1515));
-		stats.setFont(font);
-		stats.setForeground(new Color(0xDE9D5C));
-		// /--------------------------------------
+    JTextArea dynamicInfo = new JTextArea();
+    JTextField commandInputField = new JTextField();
 
-		// create the window in which everything is situated
-		
-		// Dimension screenSize = Toolkit.getDefaultToolkit().getScreenSize();
-		screenWidth = 1000; // screenSize.width;
-		screenHeight = 600; // screenSize.height;
-		window.setSize(screenWidth, screenHeight);
-		// window.setUndecorated(true); //true -> no exit button
-		window.setLayout(new BorderLayout());
-		window.setDefaultCloseOperation(JFrame.EXIT_ON_CLOSE);
+    JTextArea dungeonPlayers = new JTextArea();
+    JTextArea roomPlayers = new JTextArea();
+    JTextArea others = new JTextArea();
+    JTextArea items = new JTextArea();
+    JTextArea exits = new JTextArea();
+    JLabel stats = new JLabel();
+    JFrame window = new JFrame("The Lost Vaults");
+    
+    
+    Color darkBackground = new Color(0x800000);
+    Color lightBackground = new Color(0xDAC8A3);
+    Color textColor = new Color(0x3D1515);
+    Color lightTextColor = new Color(0xDE9D5C);
+    Color mediumBackground = new Color(0xC2A366);
[…]

### 2014-05-03 src/lostvaults/client/PlayGame.scala

@@ -18,36 +18,62 @@ class playGame extends Actor {
 
   def receive = {
     case "Connect failed" => {
-      game.updateDynamicInfo("\nConnect failed")
+      game.updateDynamicInfo("Connect failed\n")
       context stop self
     }
     case "Connected" =>
-      game.updateDynamicInfo("\nConnected")
+      game.updateDynamicInfo("Connected\n")
     case c: String => {
       println(c)
       val firstWord = Parser.findWord(c, 0)
       firstWord match {
-        case "LoginOK" =>
-          game.updateDynamicInfo("\nYou are logged in")
-        case "LoginFail" =>
+	case "DUNGEONLIST" => 
+	  game.setDungeonPlayers(Parser.findRest(c, 0))
+	case "DUNGEONJOIN" =>
+	  game.addDungeonPlayer(Parser.findRest(c, 0))
+	case "DUNGEONLEFT" =>
+	  game.removeDungeonPlayer(Parser.findRest(c, 0))
+	case "ROOMLIST" =>
+	  game.setRoomPlayers(Parser.findRest(c, 0))
+	case "ROOMJOIN" =>
+	  game.addRoomPlayer(Parser.findRest(c, 0))
+	case "ROOMLEFT" =>
+	  game.removeRoomPlayer(Parser.findRest(c, 0))
+	case "OTHERLIST" =>
+	  game.setOthers(Parser.findRest(c, 0))
+	case "OTHERJOIN" =>
+	  game.addOther(Parser.findRest(c, 0))
+	case "OTHERLEFT" =>
+	  game.removeOther(Parser.findRest(c, 0))
+	case "ITEMLIST" =>
+	  game.setItems(Parser.findRest(c, 0))
+	case "ITEMJOIN" =>
+	  game.addItem(Parser.findRest(c, 0))
+	case "ITEMLEFT" =>
+	  game.removeItem(Parser.findRest(c, 0))
+	case "ROOMEXITS" =>
+	  game.setExits(Parser.findRest(c, 0))
+        case "LOGINOK" =>
+          game.updateDynamicInfo("You are logged in\n")
+        case "LOGINFAIL" =>
           game.updateDynamicInfo("\nI'm sorry, but you cannot use that username")
-        case "Say" => {
+        case "SAY" => {
           if (game.getName == Parser.findWord(c, 1))
-            game.updateDynamicInfo("\nYou say: " + Parser.findRest(c, 1))
+            game.updateDynamicInfo("You say: " + Parser.findRest(c, 1) + "\n")
           else
[…]

### 2014-05-03 src/lostvaults/client/PlayGameCommunication.scala

@@ -5,10 +5,9 @@ object playGameCommunication {
 	var gui = new GUI()
  
   def setGame(_game : playGame) {
-	  game = _game
-	}
-	
-	
+    game = _game
+  }
+		
   def sendMessage(msg : String){
 	  game.sendMessage(msg)
   }
@@ -16,6 +15,51 @@ object playGameCommunication {
   def updateDynamicInfo(msg: String){
 	  gui.updateDynamicInfo(msg)  
   }
+  def setDungeonPlayers(playerList : String) {
+	gui.setDungeonPlayers(playerList)
+  }
+  def addDungeonPlayer(player : String) {
+	gui.addDungeonPlayer(player)
+  }
+  def removeDungeonPlayer(player : String) {
+    gui.removeDungeonPlayer(player)
+  }
+
+  
+  def setRoomPlayers(playerList : String) {
+    gui.setRoomPlayers(playerList)
+  } 
+  def addRoomPlayer(player : String) {
+    gui.addRoomPlayer(player)
+  }
+  def removeRoomPlayer(player : String) {
+    gui.removeRoomPlayer(player)
+  }
+
+  def setOthers(otherList : String) {
+    gui.setOthers(otherList)
+  }
+  def addOther(other : String) {
+    gui.addOther(other)
+  }
+  def removeOther(other : String) {
+    gui.removeOther(other)
+  }
+
+  def setItems(itemList : String) {
+    gui.setItems(itemList)
+  }
+  def addItem(item : String) {
+    gui.addItem(item)
+  }
+  def removeItem(item : String) {
+    gui.removeItem(item)
+  }
+
+  def setExits(exits : String) {
+    gui.setExits(exits);
+  }
+
   def getName():String = {
     gui.getName()
   }

### 2014-05-04 doc/ProposalSrc/lostvaults.tex
Updated proposal after proofreading.

@@
 \section{Introduction}
-The final product of this project will be a fully functional and interactive multiplayer online role playing game, or MORPG, called The Lost Vaults.
+Concurrency is becoming a more and more important facet of software development as computers rely more heavily on parallel processing and the way we write programs has to change to face 
+the challenges that follow making use of this increase in processing power. As a way for us to explore these challenges and their solutions, we opted to work on a server-client 
+system over a TCP/IP network connection. The problem we attempt to solve is maintaining a responsive environment for multiple, simultaneous connections as well as multiple active and 
+independent sections of program logic. We represent this problem through a multi-user dungeon or MUD, a form of online multiplayer game, where we aim to make sure that the server maintains 
+stable performance regardless of the number of connected users and we have decided to call this game Lost Vaults.
 
-The main challenges that we expect to face are writing network code as well as learning a new programming language.
+Lost Vaults is a semi-traditional MUD where users interact with other players and take on quests in parties 
+of multiple players working towards a common goal while still looking out first and foremost for themselves. It is possible to adventure as a group of one person, but the focus of the 
+game will be the group dynamic offered by interaction with other players. 
+The game takes place in one of two locations, the city and the dungeon; the city being where the players may recoup from previous adventures, restock on supplies and 
+form parties to delve back into the dungeon. The second location is the dungeon, a procedurally generated set of rooms populated with monsters, traps and treasures.
+The dungeon is procedurally generated and instanced in such a way that each party of players has its own dungeon, uniquely generated when the party delves down into 
+the magical caves underneath the city. Once inside, the party is given one or several quests they should take on while exploring.
+
+A quest can be finding an object and bringing it back to the surface, killing a number of monsters or collecting a set amount of gold. The party works together to accomplish 
+the goals, but at the same time only one of the party members reaps the rewards, making the party a tense and fragile alliance of rogues. Gold earned in the dungeon can be 
+spent in the city on equipment and consumables to increase the player’s chance of surviving in the dungeon and taking on more difficult and threatening monsters.
+
+The final product of this project will be a fully functional and interactive multiplayer online role playing game called The Lost Vaults.
 
 The relation between the concept of concurrency and our project is the ability to have more than one player active in the game at the same time and their interaction with each other.
-
-The game is a semi-traditional MUD, in which users connect to a central server and get the ability of interacting with other players and take on quests in parties.
-The game takes place in one of two locations, the city and the dungeon - the city being where the players may recoup from previous adventures, restock on supplies and form parties to delve back into the dungeon.
-The second location is the dungeon, a procedurally generated set of rooms populated with monsters, traps and treasures.
-The dungeon is procedurally generated and instanced in such a way that each party of players has its own dungeon, uniquely generated when the party delves down into the magical caves underneath the city.
-Once inside, the party is given one or several quests they should take on while exploring.
-
-A quest can be finding an object and bringing it back to the surface, killing a number of monsters or collecting a set amount of gold.
-The party works together to accomplish the goals, but at the same time only one of the party members reaps the rewards, making the party a tense and fragile alliance of rogues.
-Gold earned in the dungeon can be spent in the city on equipment and consumables to increase the player’s chance of surviving in the dungeon and taking on more difficult and threatening monsters.
 \part{Design}
 \section{System Architecture}
-The system architecture is in this document divided into  Client-side archiecture and Server-side architecture.
-Being written in Scala, the application runs in the Java Virtual Machine and as such, both client and server should be able to run on any platform supporting Java VM 1.7.
+The system architecture is in this document divided into  Client-side architecture and Server-side architecture. Being written in Scala, the application runs in the Java Virtual Machine and 
+as such, both client and server should be able to run on any platform supporting Java VM 1.7.
 \begin{figure}[hbt]
@@
 As seen in Figure \ref{fig:Client} the client window is divided into several text areas displaying relevant information to the player.
-The main area is for regular server responses and will contain for example room descriptions, player chat messages, system information messages and similar.
+The main area is for regular server responses and will contain room descriptions, player chat messages, system information messages and similar.
 The right side of the client is reserved for persistent information that the player may need to quickly reference.
@@
 In order to implement this kind of system with the greatest efficiency, we have chosen Scala as the language for the server as scalability is one of the fundamental design goals 
-of the language. We then decided to use Akka as our actor library and to make use of Akka's TCP library for network communication. Akka's TCP library and its ease of use also 
-guided our decision towards choosing Scala as the language of choice even for the client, as mentioned in the previous section.
+of the language.
+Per recommendation by the Scala language creators themselves and because of the library's strengths and ease of use, we decided to use Akka as our actor library and to make use of Akka's TCP
+library for network communication.
+Its simple integration also  guided our decision towards choosing Scala and Akka as the language and library of choice even for the client, as mentioned in the previous section.
 
@@
 will receive and send data over the network through the established connection. The Player actor is in charge of all things related to the clients, such as the specific player's attributes,
-is in charge of verifying login attempts through communication with the PlayerMap and it is through the Player actors that the other actors can send messages over the network when necessary.
+as well as verifying login attempts through communication with the PlayerMap and it is through the Player actors that the other actors can send messages over the network when necessary.
 
@@
 
-The fourth type of actor used by the Lost Vaults server is the Dungeon actor, the actor performing all game logic. There is a special case of Dungeon actor which is called the City actor, 
-which is a Dungeon actor that is persistent over the lifetime of the server and has special behaviour to handle the socializing aspect of chatting and forming groups as well as trading 
-with NPC merchants. The ordinary case of the Dungeon Actor is in charge of generating and handling a procedural dungeon of multiple, interconnected rooms layed out in a two-dimensional 
+The fourth type of actor used by the Lost Vaults server is the Dungeon actor, the actor performing all game logic. There is a special case of Dungeon actor which is called the City actor. 
+The City actor is a Dungeon actor that is persistent over the lifetime of the server and has special behaviour to handle the socializing aspect of chatting and forming groups as well as trading 
+with NPC \footnote{Non-Playable Character} merchants.
+The ordinary case of the Dungeon Actor is in charge of generating and handling a procedural dungeon of multiple, interconnected rooms layed out in a two-dimensional
 grid. It is in these dungeon rooms that players will have the ability to complete quests, find treasure, etc. The Dungeon actor is in charge of coordinating all the players that are 
@@
 \section{Development Tools}
-For this project we intend to use a number of tools that we see fit for the project.
-Since we will be working in Scala we will be writing our code in Eclipse.
-The reason we chose Eclipse was because it is, according to us, by far the easiest way to develop code when writing in Java or Scala.
-Since all of the development of the code will be done in Eclipse there will be no need to worry about using Make or a similar tool to automatically build software since that feature is already a pre-existing part of the program.
+For this project we intend to use a number of tools to facilitate development.
+Since we will be working in Scala we will be writing our code in Eclipse. We decided to use Eclipse because we consider it far the easiest way to develop code 
+when writing in Java or Scala. Despite writing our code in Eclipse, however, we make use of the Ant build system to automate compilation and building of our client and server, ready
+to be run in a Java virtual machine.
 
-To handle the version control we intend to use the reliable and well known tool Git.
-We will most certainly use the repository previously created by our group to host the files for the project.
-The reason we chose Git was mainly because all of the members of the project are well acquainted with the tool and we have been encouraged to use the tool in previous projects.
-For the testing of our code we will use JUnit since we will be working in an environment that is very similar to Java.
+To handle version control we intend to use the reliable and well known tool Git. We setup a fresh git repository on GitHub.com specifically for this project and we chose 
+Git because it is a powerful tool we are all familiar with.
 
-For assembling our documentation we will use Scaladoc since it is a tool we are all familiar with and it’s also pleasant to be able to put our efforts elsewhere and focus on more important parts.
+Testing of our code will be done through the JUnit and ScalaTest frameworks and the Ant Build script will allow automatic building and running of the test suites.
+
+For assembling our documentation we will use Scaladoc since it is similar to JavaDoc, a tool we are all familiar with and Ant has been amended to automatically build our documentations.
 
 \section{Process evaluation}
-We applied the Osborn principles for brainstorming with a small addition to the process.
-In the brainstorming process we went around the table and each group member had to add at least a couple of ideas before we let anyone who had an idea add them to the list of possible ideas.
-This led to many ideas which might lead to other group members coming up with new ideas from the proposed idea.
+We applied the Osborn principles for brainstorming with a small addition to the process. In the brainstorming process we went around the table and each group member had 
+to add at least a couple of ideas before we let anyone who had an idea add them to the list of possible ideas. This led to many ideas which might lead to other group members 
+coming up with new ideas from the proposed idea
 
-The initial brainstorming went as expected with a long list of possible project ideas as the result.
-No ideas were criticised during the brainstorming and all the group members' ideas were shared.
-Nothing specific could be improved about our brainstorming session.
+The initial brainstorming went as expected with a long list of possible project ideas as the result. No ideas were criticised during the brainstorming and all the group members' 
+ideas were shared. Nothing specific could be improved about our brainstorming session.
 
-During the brainstorming session three main project ideas were presented.
-The first idea was to make an online multiplayer game and the two others were simulation programs, one to simulate the traffic situation in a city and one to simulate an ecosystem.
-We divided the group into three focus groups that looked deeper into these three options.
-After this, each group were given time to present their respective fields, and after discussing pros and cons for the potential of each idea, we decided to choose the online multiplayer game.
-The reasons for this was that the complexity was intriguing, and that there was potential to develop the game further in case of extra time.
-Some of the interesting parts of the online game, besides being the most fun, was to learn about networking and our chosen programming language, Scala.
+During the brainstorming session three main project ideas were presented. The first idea was to make an online multiplayer game and the two others were simulation programs, 
+one to simulate the traffic situation in a city and one to simulate an ecosystem. We divided the group into three focus groups that looked deeper into these three options. 
+After this, each group were given time to present their respective fields, and after discussing pros and cons for the potential of each idea, we decided to choose the online 
+multiplayer game. The reasons for this was that the complexity was intriguing, and that there was potential to develop the game further in case of extra time. Some of the 
+interesting parts of the online game, besides being the most fun, was to learn about networking and our chosen programming language, Scala.
 
-Focusing on quantity in the first stage of brainstorming led to a good brainstorming process with plenty of ideas and doing so we found that it was easier to decide on a high quality idea when ideas could be put on the table and refined by the group as a whole, rather than feeling that any idea had to be fully formed before being suggested.
+Focusing on quantity in the first stage of brainstorming led to a good brainstorming process with plenty of ideas and doing so we found that it was easier to decide on a high 
+quality idea when ideas could be put on the table and refined by the group as a whole, rather than feeling that any idea had to be fully formed before being suggested.
+
+The main challenges that we expect to face during the development of both client and server are writing network code as well as learning a new programming language.
 \newpage
@@
 \hline
+\textit{LOGOUT} & Client $\rightarrow$ Server & A Request to sign out of the server.\\
+\hline
 \textit{LOGINOK} & Client $\leftarrow$ Server & Response from server that a login request has been accepted.\\
@@
 \hline
-\textit{ROOMLIST [list]} & Client $\leftarrow$ Server & Notification that the list of players in the client's current room should be repopulated. [list] is a space-delimited list of names.\\
+\textit{ROOMLIST [list]} & Client $\leftarrow$ Server & Notification that the list of players in the client's current room should be repopulated. [list] is a newline-delimited list of names.\\
 \hline
-\textit{ROOMITEMS [list]} & Client $\leftarrow$ Server & Notification of all the items in the current room. [list] is a comma delimited list of all the items in the room.\\
+\textit{NPCLIST [list]}  & Client $\leftarrow$ Server & Notification that the list of NPCs should be updated. [list] is a newline-delimited list of NPC names.\\
+\hline
+\textit{ROOMITEMS [list]} & Client $\leftarrow$ Server & Notification of all the items in the current room. [list] is a newline- delimited list of all the items in the room.\\
 \hline
@@
 \textit{ROOMEXITS [list]} & Client $\leftarrow$ Server & Notification of all possible exits from the client's current room.\\
+\hline
+\textit{ROOMPLAYERS} & Client $\rightarrow$ Server & Request for a list of players in the client's current room.\\
+\hline
+\textit{DUNGEONPLAYERS} & Client $\rightarrow$ Server & Request for a list of players in the client's current dungeon.\\
+\hline
+\textit{ROOMNPCS} & Client $\rightarrow$ Server & Request for a list of NPCs in the client's current room.\\
 \hline
@@
 \hline
-\textit{DUNGEONLIST [list]} & Client $\leftarrow$ Server & Notification that the list of players in the client's current room should be repopulated. [list] is a space-delimited list of names.\\
+\textit{DUNGEONLIST [list]} & Client $\leftarrow$ Server & Notification that the list of players in the client's current room should be repopulated. [list] is a newline-delimited list of names.\\
 \hline

### 2014-05-04 doc/ProposalSrc/lostvaults.tex
Updated proposal after proofreading.

@@
 \section{Introduction}
-Concurrency is becoming a more and more important facet of software development as computers rely more heavily on parallel processing and the way we write programs has to change to face 
-the challenges that follow making use of this increase in processing power. As a way for us to explore these challenges and their solutions, we opted to work on a server-client 
-system over a TCP/IP network connection. The problem we attempt to solve is maintaining a responsive environment for multiple, simultaneous connections as well as multiple active and 
-independent sections of program logic. We represent this problem through a multi-user dungeon or MUD, a form of online multiplayer game, where we aim to make sure that the server maintains 
+Concurrency is becoming a more and more important facet of software development as computers rely more heavily on parallel processing. Because of this the way we write programs has to change 
+to tackle the new type of problems that arise from making use of this different kind of architecture. As a way for us to explore these challenges and their solutions, we opted to work on a 
+server-client system over a TCP/IP network connection. The problem we attempt to solve is maintaining a responsive environment for multiple, simultaneous connections as well as multiple 
+active and independent sections of program logic. We represent this problem through a multi-user dungeon or MUD, a form of online multiplayer game, where we aim to make sure that the server maintains 
 stable performance regardless of the number of connected users and we have decided to call this game Lost Vaults.

### 2014-05-04 doc/ProposalSrc/lostvaults.tex
Almost final version of proposal V. 2.0

--- 2014-05-04 doc/ProposalSrc/lostvaults.tex
@@
 \section{Introduction}
-Concurrency is becoming a more and more important facet of software development as computers rely more heavily on parallel processing and the way we write programs has to change to face 
-the challenges that follow making use of this increase in processing power. As a way for us to explore these challenges and their solutions, we opted to work on a server-client 
-system over a TCP/IP network connection. The problem we attempt to solve is maintaining a responsive environment for multiple, simultaneous connections as well as multiple active and 
-independent sections of program logic. We represent this problem through a multi-user dungeon or MUD, a form of online multiplayer game, where we aim to make sure that the server maintains 
-stable performance regardless of the number of connected users and we have decided to call this game Lost Vaults.
+Concurrency is becoming a more and more important facet of software development as computers rely more heavily on parallel processing and because of this the way we write programs has to change. 
+This new kind of architecture brings with it a new type of problems, and without adapting we will not be able to make use of the increase in processing power. 
+As a way for us to explore these challenges and their solutions, we opted to work on a server-client system over a TCP/IP network connection.
+The problem we attempt to solve is maintaining a responsive
+environment for multiple, simultaneous connections as well as multiple active and independent sections of program logic. We represent this problem through a multi-user dungeon or 
+MUD, a form of online multiplayer game, where we aim to make sure that the server maintains stable performance regardless of the number of connected users.
 
-Lost Vaults is a semi-traditional MUD where users interact with other players and take on quests in parties 
+We decided to call the game Lost Vaults and it is a semi-traditional MUD where users interact with other players and take on quests in parties 
 of multiple players working towards a common goal while still looking out first and foremost for themselves. It is possible to adventure as a group of one person, but the focus of the 
@@
 \section{Game Design}
-[TODO: Describe game design here!]
+\subsection{Dungeon}
+The meat of the game takes place in procedurally generated dungeons, each unique to the group of players who enter that dungeon. Once a dungeon has been created and a group has 
+been assigned to it, no new players may enter that dungeon. A player who dies in the dungeon will be forced to leave the dungeon, as described below, and a player who has left the dungeon 
+may not reenter it.
+
+The dungeon's room are created procedurally on demand. That is to say, a new room is only created when a player tries to enter a room that does not yet exist. There are exceptions to 
+this, as will be described in the quest section of this document.
+\subsubsection{Rooms}
+The dungeon is made up of interconnected rooms, which may have one or more exits, each representing a door on one of the room's four walls. A room may contain any number of players, monsters 
+and items. A room may also contain a ``trap'' which can be harmful as well as beneficial, performing an action on the first player to enter that room. Players may attack any other player or 
+NPC occupying the same room. Combat is described in more detail below. When the combat is between players, neither player currently fighting may escape the room until one of them has fallen. 
+Escaping from a battle with an NPC will cost the escaping player one extra food.
+\subsubsection{Food}
+Food is the main type of resource to be managed in the game as food is needed to explore the dungeon. Each player has their own supply of food, starting at a minimum of five pieces of food 
+and additional food can be bought from the city merchant or be found in the dungeon. When a player enters a room that player has not yet explored, one piece of food is subtracted from their 
+personal supply. Entering a room previously explored by that player does not consume food. The players' progress is therefore limited by how much food they bring with them into the dungeon.
+\subsubsection{Leaving The Dungeon}
+Upon leaving the dungeon, all the consumables found or brought down will be lost to the player (food and potions rot), and all treasure items that are found are sold off for gold. 
+Furthermore, every player leaving a dungeon is awarded gold for the quests they have completed both as a group or individually. Dead players do not gain gold for completed quests.
+
+If a player dies, they are forced to leave the dungeon, and gain no gold from either treasures found or quests completed.
+\subsection{Player}
+The player has four distinct attributes to aid her in her adventure. Life signifies the current health of the player, when life reaches zero the player dies and she will face the penalty 
+described below. Defense represents her ability to withstand damage and is in direct opposite to the Attack attribute of an opposing entity. Attack then is the ability to inflict damage, 
+and the damage calculation is a simple calculation of subtracting the defender's defense score from the attacker's attack score. The result, if greater than zero, is then subtracted from 
+the defender's current life. If the defender's life reaches zero, she dies. The final attribute is food, and as described above it represents the player's ability to explore the dungeon 
+as well as her ability to flee from combat against foes that are too dangerous. 
+\subsection{Combat}
+Lost Vaults uses a turn-based combat system, where each participant get their chance to attack any of the other occupants in the room. Attacking another player forces them to join in the 
+combat, denying them the ability to escape the room. During player versus player combat, neither player may send a private message or perform a dungeon wide yell command, limiting their 
+ability to communicate to only the room they're occupying. Combat against an NPC does not have this limitation, and players may both escape at the cost of one additional food, and they 
+may use yells to call in aid from their allies.
+\subsubsection{Death}
+Dying in Lost Vaults carries a penalty in the form of losing all consumable items and treasures the dying player carries, as well as being forced back into the city without the possibility 
+to rejoin their comrades still exploring the dungeon. This means all progress made inside the dungeon is lost upon death, as well as all gold spent preparing for the adventure. All treasure 
+and consumables held by the dying player will be left on the floor of the room in which she died.
+\subsection{Quests}
+When entering a dungeon, the group is given one or more quests to complete which will net them extra gold upon leaving. However, individual players may also be given an additional quest, 
+which they alone stand to gain from and which is in direct opposition to the group's best interest.
+\subsubsection{Group Quests}
+Group quests are quests that all players of the group benefit from, and completing the quest is in everyone's best interest. The reward for a completed quest is given to each player who 
+is alive to leave the dungeon after completion. The group quests are as follows.
+
+\textit{Kill a specified monster}. The group is tasked to kill a specific monster, appropriate to the strength of the group. The monster is placed in a random location and a path is 
+guaranteed from the start to the monster's room.\\
+\textit{Find an item}. A specific piece of treasure is to be located and taken out of the dungeon. Similarly to the previous quest, a room is created containing the item and a path is 
+guaranteed to it from the start.\\
+\textit{Kill X monsters}. A specified number of monsters are to be slain. The types of monsters do not matter, and every killed monster works towards this goal.\\
+\textit{Every ally must leave}. This quest works against traiterous players. Whenever a player gains the Kill a specified player or Kill all other players quests, the group gains this quest.
+In order for this quest to be completed, not only does everyone not tasked with a kill quest leave the dungeon but the player who does have that quest must not. That is to say, the 
+traitor has to bee rooted out of the group and killed in order for the group to accomplish this quest. This quest does not require a traitor be present, but if a traitor is present this 
+quest will always accompany it.
+\subsubsection{Player Quests}
+Player quests are quests given to individual players and they alone stand to gain from it. It's in opposition to the best interest of the rest of the group and their rewards are 
+greater than the others, providing an incentive to complete them. The player quests are as follows.
+
+\textit{Kill a specified player}. The player is tasked with killing one of the other players in his or her group and then manage to leave the dungeon alive. There is no requirement to leave 
+the dungeon immediately, however, but an enterprising player may continue to play as part of the group if possible, reaping the rewards from the group quests as well. However, the group 
+knows that someone has been tasked to kill someone else through the \textit{Every ally must leave} quest. The player does not have to be the one killing the target, as long as the target 
+does not exit the dungeon alive.\\
+\textit{Earn the most money}. Be the player who has earned the most gold during the adventure, either by making sure other players do not leave or by taking all treasure that they come across.\\
+\textit{Kill all other players}. The player is tasked with being the only one to leave the dungeon alive. Not only do they stand to gain the reward of all items found in the dungeon, they also gain 
+a substantial reward for completing this quest, greater than any other quest available. Completion of this quest will be difficult and require more than brute strength on the part of the player. 
+Similarly to the \textit{Kill a specified player} quest, this will force a \textit{Every ally must leave} quest on the group.
+\subsection{Items}
+Lost Vaults have three subsets of items, as described below.
+
+\subsubsection{Equipment}
+Equipment provide the player a bonus to their attack or defense score, making them stronger or more resiliant. Equipment is the only way to increase the player characters' powers and 
+equipment is upgraded either by purchasing them from the city merchant or finding them in the dungeon. The player may only hold one offensive and one defensive equipment item at a time and 
+finding or buying new equipment means the old equipment is dropped or lost respectively.
+
+\subsubsection{Consumables}
+Consumables come in two further flavours, food and potions. Food allow players to progress deeper into the dungeon and potions recover Life when used. Consumables are good for exactly 
+one round of adventuring and both potions and food can be found in dungeons or bought from the city merchant. Consumables may also be given from player to player. Consumables are lost 
+either when the player dies or when the player leaves the dungeon they are in.
+
+\subsubsection{Treasure}
+Treasure is a type of item which has no practical use but instead has a monetary value. When a player exits a dungeon, the treasures she holds are converted into gold which is rewarded 
+to the player carrying the item. It is a personal reward and only the player carrying a treasure item gains its value upon exit.
 \part{Development Process}

### 2014-05-05 src/lostvaults/client/GUI.java
GUIFIX

@@ -23,7 +23,7 @@ public class GUI {
     JTextArea exits = new JTextArea();
     JLabel stats = new JLabel();
     JFrame window = new JFrame("The Lost Vaults");
-    
+
     
     Color darkBackground = new Color(0x800000);
     Color lightBackground = new Color(0xDAC8A3);
@@ -36,9 +36,8 @@ public class GUI {
     Font bigFont = new Font("Serif", Font.BOLD + Font.ITALIC, 15);
 
     public String getName() { return name; }
-    public GUI() {
 
-				
+    public GUI() {				
 	// Dimension screenSize = Toolkit.getDefaultToolkit().getScreenSize();
 	screenWidth = 1000; // screenSize.width;
 	screenHeight = 600; // screenSize.height;
@@ -57,131 +56,50 @@ public class GUI {
 	dynamicInfoScroll.setBorder(BorderFactory.createEmptyBorder());
 
 
-
-
-
 	stats.setText("HP: 20/20 \t Food: 30/30");
 	stats.setFont(font);
 	stats.setForeground(lightTextColor);
 
 
-	dungeonPlayers.setFont(font);
-	dungeonPlayers.setForeground(textColor);
-	dungeonPlayers.setBackground(mediumBackground);
-	dungeonPlayers.setEditable(false);
-	JScrollPane dungeonPlayersScroll = new JScrollPane(dungeonPlayers); 
-	dungeonPlayersScroll.setBorder(BorderFactory.createEmptyBorder());
-	JLabel dungeonPlayersLabel = new JLabel("Players in Dungeon: ");
-	dungeonPlayersLabel.setForeground(textColor);
-	dungeonPlayersLabel.setFont(bigFont);
-	JPanel dungeonPlayersPanel = new JPanel(new BorderLayout());
-	dungeonPlayersPanel.setPreferredSize(new Dimension(0, screenHeight/5));
-	dungeonPlayersPanel.setBackground(darkMediumBackground);
-	dungeonPlayersPanel.setBorder(BorderFactory.createLineBorder(darkBackground, 2));
-	dungeonPlayersPanel.add(dungeonPlayersLabel, BorderLayout.NORTH);
-	dungeonPlayersPanel.add(dungeonPlayersScroll, BorderLayout.CENTER);
-
-
-
-	roomPlayers.setFont(font);
-	roomPlayers.setForeground(textColor);
[…]

### 2014-05-05 src/lostvaults/client/PlayGame.scala
changed some things and started working with the /help command

@@ -27,32 +27,32 @@ class playGame extends Actor {
       println(c)
       val firstWord = Parser.findWord(c, 0)
       firstWord match {
-	case "DUNGEONLIST" => 
-	  game.setDungeonPlayers(Parser.findRest(c, 0))
-	case "DUNGEONJOIN" =>
-	  game.addDungeonPlayer(Parser.findRest(c, 0))
-	case "DUNGEONLEFT" =>
-	  game.removeDungeonPlayer(Parser.findRest(c, 0))
-	case "ROOMLIST" =>
-	  game.setRoomPlayers(Parser.findRest(c, 0))
-	case "ROOMJOIN" =>
-	  game.addRoomPlayer(Parser.findRest(c, 0))
-	case "ROOMLEFT" =>
-	  game.removeRoomPlayer(Parser.findRest(c, 0))
-	case "OTHERLIST" =>
-	  game.setOthers(Parser.findRest(c, 0))
-	case "OTHERJOIN" =>
-	  game.addOther(Parser.findRest(c, 0))
-	case "OTHERLEFT" =>
-	  game.removeOther(Parser.findRest(c, 0))
-	case "ITEMLIST" =>
-	  game.setItems(Parser.findRest(c, 0))
-	case "ITEMJOIN" =>
-	  game.addItem(Parser.findRest(c, 0))
-	case "ITEMLEFT" =>
-	  game.removeItem(Parser.findRest(c, 0))
-	case "ROOMEXITS" =>
-	  game.setExits(Parser.findRest(c, 0))
+        case "DUNGEONLIST" =>
+          game.setDungeonPlayers(Parser.findRest(c, 0))
+        case "DUNGEONJOIN" =>
+          game.addDungeonPlayer(Parser.findRest(c, 0))
+        case "DUNGEONLEFT" =>
+          game.removeDungeonPlayer(Parser.findRest(c, 0))
+        case "ROOMLIST" =>
+          game.setRoomPlayers(Parser.findRest(c, 0))
+        case "ROOMJOIN" =>
+          game.addRoomPlayer(Parser.findRest(c, 0))
+        case "ROOMLEFT" =>
+          game.removeRoomPlayer(Parser.findRest(c, 0))
+        case "OTHERLIST" =>
+          game.setOthers(Parser.findRest(c, 0))
+        case "OTHERJOIN" =>
+          game.addOther(Parser.findRest(c, 0))
+        case "OTHERLEFT" =>
+          game.removeOther(Parser.findRest(c, 0))
[…]

### 2014-05-05 src/lostvaults/client/PlayGameCommunication.scala

@@ -1,66 +1,65 @@
 package lostvaults.client
 
 object playGameCommunication {
-	var game : playGame = null
-	var gui = new GUI()
- 
-  def setGame(_game : playGame) {
+  var game: playGame = null
+  var gui = new GUI()
+
+  def setGame(_game: playGame) {
     game = _game
   }
-		
-  def sendMessage(msg : String){
-	  game.sendMessage(msg)
+
+  def sendMessage(msg: String) {
+    game.sendMessage(msg)
   }
-  
-  def updateDynamicInfo(msg: String){
-	  gui.updateDynamicInfo(msg)  
+
+  def updateDynamicInfo(msg: String) {
+    gui.updateDynamicInfo(msg)
   }
-  def setDungeonPlayers(playerList : String) {
-	gui.setDungeonPlayers(playerList)
+  def setDungeonPlayers(playerList: String) {
+    gui.setDungeonPlayers(playerList)
   }
-  def addDungeonPlayer(player : String) {
-	gui.addDungeonPlayer(player)
+  def addDungeonPlayer(player: String) {
+    gui.addDungeonPlayer(player)
   }
-  def removeDungeonPlayer(player : String) {
+  def removeDungeonPlayer(player: String) {
     gui.removeDungeonPlayer(player)
   }
 
-  
-  def setRoomPlayers(playerList : String) {
+  def setRoomPlayers(playerList: String) {
     gui.setRoomPlayers(playerList)
-  } 
-  def addRoomPlayer(player : String) {
+  }
+  def addRoomPlayer(player: String) {
     gui.addRoomPlayer(player)
   }
-  def removeRoomPlayer(player : String) {
+  def removeRoomPlayer(player: String) {
     gui.removeRoomPlayer(player)
   }
 
-  def setOthers(otherList : String) {
+  def setOthers(otherList: String) {
     gui.setOthers(otherList)
   }
-  def addOther(other : String) {
+  def addOther(other: String) {
     gui.addOther(other)
   }
-  def removeOther(other : String) {
+  def removeOther(other: String) {
     gui.removeOther(other)
   }
 
-  def setItems(itemList : String) {
+  def setItems(itemList: String) {
     gui.setItems(itemList)
   }
-  def addItem(item : String) {
+  def addItem(item: String) {
     gui.addItem(item)
   }
-  def removeItem(item : String) {
+  def removeItem(item: String) {
     gui.removeItem(item)
   }
 
-  def setExits(exits : String) {
[…]

### 2014-05-05 src/lostvaults/server/Player.scala

@@ -13,7 +13,8 @@ class Player extends Actor {
   var dungeon = self
   var whisperTo = ""
   var whisperMsg = ""
-
+  val helpList: List[String] = List("Say \n", "Whisper \n", "LogOut \n")
+  
   def receive = {
     case Received(msg) => {
       connection = sender
@@ -30,14 +31,17 @@ class Player extends Actor {
             connection ! Write(ByteString("LoginFail"))
             context stop self
           } else {
-            connection ! Write(ByteString("LoginOk"))
-            PMap ! PMapAddPlayer(name, self)
+            connection ! Write(ByteString("LOGINOK"))
+            PMap ! PMapAddPlayer(name,self)
             dungeon = Main.City.get
             dungeon ! GameAddPlayer(name)
             become(LoggedIn)
           }
         }
       }
+      
+      // Här finns Receive satsen för servern - här tar vi emot alla användar-meddelanden från GUI:t
+      
       def LoggedIn: Receive = {
         case Received(msg) => {
           val decodedMsg = msg.decodeString(java.nio.charset.Charset.defaultCharset().name())
@@ -54,6 +58,10 @@ class Player extends Actor {
             case "LogOut" => {
               connection ! Write(ByteString("Bye"))
               connection ! Close
+            }
+            case "Help" => {
+              connection ! Write(ByteString(helpList.mkString))
+
             }
             case _ => {
               connection ! Write(ByteString("System I have no idea what you're wanting to do."))

### 2014-05-05 src/lostvaults/client/GUI.java
Hejsan

@@ -182,7 +182,6 @@ public class GUI {
 	    window = _window;
 	   
 	    //Setting up the fields
-	    new BorderLayout();
 	    button = new JButton("OK");
 	    button.addActionListener(this);
 	    button.setBackground(mediumBackground);
@@ -217,17 +216,15 @@ public class GUI {
 	    IP.add(IPInput, BorderLayout.CENTER);
 	    IP.add(IPLabel, BorderLayout.WEST);
 
-	    JPanel northbox = new JPanel(new BorderLayout());
-	    JPanel southbox = new JPanel(new BorderLayout());
 
-	    northbox.add(userName, BorderLayout.NORTH);
-	    northbox.add(password, BorderLayout.CENTER);
-	    southbox.add(IP, BorderLayout.NORTH);
-	    southbox.add(button, BorderLayout.CENTER);
-	    add(northbox, BorderLayout.NORTH);
-	    add(southbox, BorderLayout.CENTER);
-	    
-	    setSize(600, 120);
+	    JPanel frame = new JPanel(new GridLayout(0, 1));
+	    frame.add(userName);
+	    frame.add(password);
+	    frame.add(IP);
+	    frame.add(button);
+	    add(frame);
+	    setPreferredSize(new Dimension(600, 200));
+	    pack();
 
 	    setLocationRelativeTo(null);
 	    setVisible(true);
@@ -235,13 +232,19 @@ public class GUI {
 
 	public void actionPerformed(ActionEvent e) {
 	    String user = userNameInput.getText();
-	    //String pwd = passwordInput.getText();
-	    //String ip = IPInput.getText();
-	    user = user.replace(" ", "");
-	    playGameCommunication.sendMessage("LOGIN " + user); /// Obs, ändra till caps
-	    window.setVisible(true);
-	    dispose();
-
+	    if(user.equals("")) {
+		userNameInput.setText("Enter username here");
+	    } else {
+		System.out.println(user);
+		System.out.println("Hello");
+		//String pwd = passwordInput.getText();
+		//String ip = IPInput.getText();
+		user = user.replace(" ", "");
+		game = user;
+		playGameCommunication.sendMessage("LOGIN " + user); /// Obs, ändra till caps
+		window.setVisible(true);
+		dispose();
+	    }
 	}
     }
 

### 2014-05-05 src/lostvaults/client/PlayGameCommunication.scala
Added a message in server

@@ -15,6 +15,9 @@ object playGameCommunication {
   def updateDynamicInfo(msg: String) {
     gui.updateDynamicInfo(msg)
   }
+
+
+
   def setDungeonPlayers(playerList: String) {
     gui.setDungeonPlayers(playerList)
   }

### 2014-05-05 src/lostvaults/server/Player.scala

@@ -70,9 +70,11 @@ class Player extends Actor {
         }
         case GamePlayerEnter(name) => {
           connection ! Write(ByteString("SYSTEM Player " + name + " has entered the dungeon"))
+	  connection ! Write(ByteString("DUNGEONJOIN " + name))
         }
         case GamePlayerLeft(name) => {
           connection ! Write(ByteString("SYSTEM Player " + name + " has left the dungeon"))
+	  connection ! Write(ByteString("DUNGEONLEFT " + name))
         }
         case GameSay(name, msg) => {
           connection ! Write(ByteString("SAY " + name + " " + msg))

### 2014-05-05 src/lostvaults/client/GUI.java
started implementing password and IP sending from GUI and onward

@@ -249,14 +249,21 @@ public class GUI {
 
 	public void actionPerformed(ActionEvent e) {
 	    String user = userNameInput.getText();
+	    String password = passwordInput.getText();
+	    String ip = ipInput.getText();
 	    if(user.equals("")) {
 		message.setText("You must enter a username\n");
+	    } else if (password.equals("")){
+	    message.setText("You must enter a password\n")
+	    }
 	    } else {
 		//String pwd = passwordInput.getText();
 		//String ip = IPInput.getText();
 		user = user.replace(" ", "");
 		name = user;
-		playGameCommunication.sendMessage("LOGIN " + user); /// Obs, ändra till caps
+		playGameCommunication.sendMessage("LOGIN " + user);
+		playGameCommunication.sendMessage("PASSWORD " + password); // Login + pass borde antagligen sickas tillsammans i ett gemensamt meddelande.
+		playGameCommunication.sendIP("IP " + ip);
 		window.setVisible(true);
 		dispose();
 	    }

### 2014-05-05 src/lostvaults/client/PlayGameCommunication.scala

@@ -11,6 +11,9 @@ object playGameCommunication {
   def sendMessage(msg: String) {
     game.sendMessage(msg)
   }
+  def sendIP(msg: String){
+    game.sendIP(msg)
+  }
 
   def updateDynamicInfo(msg: String) {
     gui.updateDynamicInfo(msg)

### 2014-05-05 src/lostvaults/client/TCPClient.scala

@@ -12,17 +12,18 @@ case object ShutDown extends MyMsg
 case object Ok extends MyMsg
 
 object TCPClient {
-  def props(listener: ActorRef): Props = Props(new TCPClient(listener))
+  def props(listener: ActorRef, requestedIP: InetSocketAddress): Props = Props(new TCPClient(listener, requestedIP))
 }
 
-class TCPClient(listener: ActorRef) extends Actor {
+class TCPClient(listener: ActorRef, requestedIP: InetSocketAddress) extends Actor {
   import Tcp._
   import context.system
   val manager = IO(Tcp)
   var connection: Option[ActorRef] = None
+  
 
   override def preStart() = {
-    manager ! Connect(new InetSocketAddress("localhost", 51234))
+    manager ! Connect(requestedIP) // ändra "localhost" till den IP:n man skriver in i GUI:t 
     // Ändra localhost i slutversionen till IP'n för Servern.
   }
 

### 2014-05-05 src/lostvaults/server/Player.scala

@@ -15,6 +15,9 @@ class Player extends Actor {
   var whisperMsg = ""
   val helpList: List[String] = List("Say \n", "Whisper \n", "LogOut \n")
   
+  "LOGIN Anna Häst"
+  
+  
   def receive = {
     case Received(msg) => {
       connection = sender

### 2014-05-05 src/lostvaults/client/PlayGame.scala
GL HF

@@ -27,38 +27,40 @@ class playGame extends Actor {
       println(c)
       val firstWord = Parser.findWord(c, 0)
       firstWord match {
-	case "DUNGEONLIST" => 
-	  game.setDungeonPlayers(Parser.findRest(c, 0))
-	case "DUNGEONJOIN" =>
-	  game.addDungeonPlayer(Parser.findRest(c, 0))
-	case "DUNGEONLEFT" =>
-	  game.removeDungeonPlayer(Parser.findRest(c, 0))
-	case "ROOMLIST" =>
-	  game.setRoomPlayers(Parser.findRest(c, 0))
-	case "ROOMJOIN" =>
-	  game.addRoomPlayer(Parser.findRest(c, 0))
-	case "ROOMLEFT" =>
-	  game.removeRoomPlayer(Parser.findRest(c, 0))
-	case "OTHERLIST" =>
-	  game.setOthers(Parser.findRest(c, 0))
-	case "OTHERJOIN" =>
-	  game.addOther(Parser.findRest(c, 0))
-	case "OTHERLEFT" =>
-	  game.removeOther(Parser.findRest(c, 0))
-	case "ITEMLIST" =>
-	  game.setItems(Parser.findRest(c, 0))
-	case "ITEMJOIN" =>
-	  game.addItem(Parser.findRest(c, 0))
-	case "ITEMLEFT" =>
-	  game.removeItem(Parser.findRest(c, 0))
-	case "ROOMEXITS" =>
-	  game.setExits(Parser.findRest(c, 0))
+        case "DUNGEONLIST" =>
+          game.setDungeonPlayers(Parser.findRest(c, 0))
+        case "DUNGEONJOIN" =>
+          game.addDungeonPlayer(Parser.findRest(c, 0))
+        case "DUNGEONLEFT" =>
+          game.removeDungeonPlayer(Parser.findRest(c, 0))
+        case "ROOMLIST" =>
+          game.setRoomPlayers(Parser.findRest(c, 0))
+        case "ROOMJOIN" =>
+          game.addRoomPlayer(Parser.findRest(c, 0))
+        case "ROOMLEFT" =>
+          game.removeRoomPlayer(Parser.findRest(c, 0))
+        case "OTHERLIST" =>
+          game.setOthers(Parser.findRest(c, 0))
+        case "OTHERJOIN" =>
+          game.addOther(Parser.findRest(c, 0))
+        case "OTHERLEFT" =>
[…]

### 2014-05-05 src/lostvaults/server/Player.scala

@@ -18,19 +18,19 @@ class Player extends Actor {
     case Received(msg) => {
       connection = sender
       val decodedMsg = msg.decodeString(java.nio.charset.Charset.defaultCharset().name())
-      if (Parser.findWord(decodedMsg, 0) == "Login") {
+      if (Parser.findWord(decodedMsg, 0) == "LOGIN") {
         name = Parser.findWord(decodedMsg, 1)
         PMap ! PMapIsOnline(name, decodedMsg)
       }
     }
     case PMapIsOnlineResponse(response, purpose) =>
       {
-        if (Parser.findWord(purpose, 0) == "Login") {
+        if (Parser.findWord(purpose, 0) == "LOGIN") {
           if (response) {
-            connection ! Write(ByteString("LoginFail"))
+            connection ! Write(ByteString("LOGINFAIL"))
             context stop self
           } else {
-            connection ! Write(ByteString("LoginOk"))
+            connection ! Write(ByteString("LOGINOK"))
             PMap ! PMapAddPlayer(name, self)
             dungeon = Main.City.get
             dungeon ! GameAddPlayer(name)
@@ -41,54 +41,54 @@ class Player extends Actor {
       def LoggedIn: Receive = {
         case Received(msg) => {
           val decodedMsg = msg.decodeString(java.nio.charset.Charset.defaultCharset().name())
-          val action = Parser.findWord(decodedMsg, 0)
+          val action = Parser.findWord(decodedMsg, 0).toUpperCase
           action match {
-            case "Say" => {
+            case "SAY" => {
               dungeon ! GameSay(name, Parser.findRest(decodedMsg, 0))
             }
-            case "Whisper" => {
+            case "WHISPER" => {
               whisperTo = Parser.findWord(decodedMsg, 1)
               whisperMsg = Parser.findRest(decodedMsg, 1)
               PMap ! PMapGetPlayer(whisperTo, decodedMsg)
             }
-            case "LogOut" => {
+            case "LOGOUT" => {
               connection ! Write(ByteString("Bye"))
               connection ! Close
             }
             case _ => {
-              connection ! Write(ByteString("System I have no idea what you're wanting to do."))
+              connection ! Write(ByteString("SYSTEM I have no idea what you're wanting to do."))
             }
           }
         }
         case GamePlayerEnter(name) => {
-          connection ! Write(ByteString("System Player " + name + " has entered the dungeon"))
+          connection ! Write(ByteString("SYSTEM Player " + name + " has entered the dungeon"))
         }
[…]

### 2014-05-05 src/lostvaults/server/Player.scala
fix merge error

@@ -32,11 +32,7 @@ class Player extends Actor {
             context stop self
           } else {
             connection ! Write(ByteString("LOGINOK"))
-<<<<<<< HEAD
             PMap ! PMapAddPlayer(name, self)
-=======
-            PMap ! PMapAddPlayer(name,self)
->>>>>>> fea8578946503f184b8822d76fdc51615d9b92aa
             dungeon = Main.City.get
             dungeon ! GameAddPlayer(name)
             become(LoggedIn)

### 2014-05-06 doc/ProposalSrc/lostvaults.tex
Latest Proposal

@@
 \usepackage{graphicx}
-\usepackage{appendix}
-\usepackage{longtable}
 \DeclareGraphicsExtensions{.png}
@@
 The game takes place in one of two locations, the city and the dungeon; the city being where the players may recoup from previous adventures, restock on supplies and 
-form parties to delve back into the dungeon. The second location is the dungeon, a procedurally generated set of rooms populated with monsters, traps and treasures.
+form parties to delve down into the dungeons. The second location is the dungeon itself, a procedurally generated set of rooms populated with monsters, traps and treasures.
 The dungeon is procedurally generated and instanced in such a way that each party of players has its own dungeon, uniquely generated when the party delves down into 
@@
 
-A quest can be finding an object and bringing it back to the surface, killing a number of monsters or collecting a set amount of gold. The party works together to accomplish 
-the goals, but at the same time only one of the party members reaps the rewards, making the party a tense and fragile alliance of rogues. Gold earned in the dungeon can be 
-spent in the city on equipment and consumables to increase the player’s chance of surviving in the dungeon and taking on more difficult and threatening monsters.
+As described in the game design portion of this document, there are two types of quests: group quests and player quests. Group quests are to everyone's benefit, and player 
+quests are individual quests of subterfuge. We aim to create an atmosphere where the players need to rely on each other to achieve the tougher group quests while at the same 
+time remaining weary about each other as any one of them could be a traitor, looking out only for themselves and thus creating an air of an uneasy alliance as you enter the dungeon.
 
@@
 combat, denying them the ability to escape the room. During player versus player combat, neither player may send a private message or perform a dungeon wide yell command, limiting their 
-ability to communicate to only the room they're occupying. Combat against an NPC does not have this limitation, and players may both escape at the cost of one additional food, and they 
+ability to communicate to only the room they are occupying. Combat against an NPC does not have this limitation, and players may both escape at the cost of one additional food, and they 
 may use yells to call in aid from their allies.
@@
 is alive to leave the dungeon after completion. The group quests are as follows.
-
-\textit{Kill a specified monster}. The group is tasked to kill a specific monster, appropriate to the strength of the group. The monster is placed in a random location and a path is 
-guaranteed from the start to the monster's room.\\
-\textit{Find an item}. A specific piece of treasure is to be located and taken out of the dungeon. Similarly to the previous quest, a room is created containing the item and a path is 
-guaranteed to it from the start.\\
-\textit{Kill X monsters}. A specified number of monsters are to be slain. The types of monsters do not matter, and every killed monster works towards this goal.\\
-\textit{Every ally must leave}. This quest works against traiterous players. Whenever a player gains the Kill a specified player or Kill all other players quests, the group gains this quest.
-In order for this quest to be completed, not only does everyone not tasked with a kill quest leave the dungeon but the player who does have that quest must not. That is to say, the 
+\begin{description}
+\item[Kill a specified monster] The group is tasked to kill a specific monster, appropriate to the strength of the group. The monster is placed in a random location and a path is 
+guaranteed from the start to the monster's room.
+\item[Find an item] A specific piece of treasure is to be located and taken out of the dungeon. Similarly to the previous quest, a room is created containing the item and a path is 
+guaranteed to it from the start.
+\item[Kill X monsters] A specified number of monsters are to be slain. The types of monsters do not matter, and every killed monster works towards this goal.
+\item[Every ally must survive] This quest works against traiterous players.
+Whenever a player gains the \textbf{Kill a specified player character} or \textbf{Be the only survivor} players quests, the group gains this quest.
+In order for this quest to be completed, not only does everyone not tasked with a kill quest leave the dungeon but the player who does have that quest must not. That is to say, an eventual  
 traitor has to bee rooted out of the group and killed in order for the group to accomplish this quest. This quest does not require a traitor be present, but if a traitor is present this 
 quest will always accompany it.
+\end{description}
 \subsubsection{Player Quests}
-Player quests are quests given to individual players and they alone stand to gain from it. It's in opposition to the best interest of the rest of the group and their rewards are 
+Player quests are quests given to individual players and they alone stand to gain from it. It is in opposition to the best interest of the rest of the group and their rewards are 
 greater than the others, providing an incentive to complete them. The player quests are as follows.
-
-\textit{Kill a specified player}. The player is tasked with killing one of the other players in his or her group and then manage to leave the dungeon alive. There is no requirement to leave 
+\begin{description}
+\item[Kill a specified player character] The player is tasked with killing one of the other players in his or her group and then manage to leave the dungeon alive. There is no requirement to leave 
 the dungeon immediately, however, but an enterprising player may continue to play as part of the group if possible, reaping the rewards from the group quests as well. However, the group 
-knows that someone has been tasked to kill someone else through the \textit{Every ally must leave} quest. The player does not have to be the one killing the target, as long as the target 
-does not exit the dungeon alive.\\
-\textit{Earn the most money}. Be the player who has earned the most gold during the adventure, either by making sure other players do not leave or by taking all treasure that they come across.\\
-\textit{Kill all other players}. The player is tasked with being the only one to leave the dungeon alive. Not only do they stand to gain the reward of all items found in the dungeon, they also gain 
+knows that someone has been tasked to kill someone else through the \textbf{Every ally must leave} quest. The player does not have to be the one killing the target, as long as the target 
+does not exit the dungeon alive.
+\item[Earn the most gold] Be the player who has earned the most gold during the adventure, either by making sure other players do not leave or by taking all treasure that they come across.
+\item[Be the only survivor] The player is tasked with being the only one to leave the dungeon alive. Not only do they stand to gain the reward of all items found in the dungeon, they also gain 
 a substantial reward for completing this quest, greater than any other quest available. Completion of this quest will be difficult and require more than brute strength on the part of the player. 
-Similarly to the \textit{Kill a specified player} quest, this will force a \textit{Every ally must leave} quest on the group.
+Similarly to the \textbf{Kill a specified player character} quest, this will force a \textbf{Every ally must survive} quest on the group.
+\end{description}
 \subsection{Items}
@@
 \newpage
-\part{Appendices}
-\begin{appendices}
-\section{Network Messages}\label{app:NetworkMessages}
-\begin{longtable}{|l|c|p{8 cm}|}
-\hline
-Message & Direction & Description\\
-\hline
-\endhead
-\textit{SAY [msg]} & Client $\rightarrow$ Server & Chat message sent from client to server.\\
-\hline
-\textit{SAY [name] [msg]} & Client $\leftarrow$ Server & The Chat message sent by [name] and relayed to the relevant clients.\\
-\hline
-\textit{WHISPER [to] [msg]} & Client $\rightarrow$ Server & A private message sent from a player to another player named [to].\\
-\hline
-\textit{WHISPER [from] [to] [msg]} & Client $\leftarrow$ Server & A private message sent from a player named [from], to another player named [to].\\
-\hline
-\textit{LOGIN [name]} & Client $\rightarrow$ Server & A request to sign onto the server using [name] as the player's username.\\
-\hline
-\textit{LOGOUT} & Client $\rightarrow$ Server & A Request to sign out of the server.\\
-\hline
-\textit{LOGINOK} & Client $\leftarrow$ Server & Response from server that a login request has been accepted.\\
-\hline
-\textit{LOGINFAIL} & Client $\leftarrow$ Server & Response from server that a login request has been denied.\\
-\hline
-\textit{BYE} & Client $\leftarrow$ Server & Connection Closed message sent from server to client.\\
-\hline
-\textit{SYSTEM} & Client $\leftarrow$ Server & System mesage sent from the server to the client.\\
-\hline
-\textit{INVENTORY} & Client $\rightarrow$ Server & Request from a client to list a player's current inventory.\\
-\hline
-\textit{INVENTORY [list]} & Client $\leftarrow$ Server & Response to a client's inventory request. [list] is a comma delimited list of item names.\\
-\hline
-\textit{ROOMENTER [name]} & Client $\leftarrow$ Server & Notification that a player named [name] has entered the room which the client receiving the message is in.\\
-\hline
-\textit{ROOMLEAVE [name]} & Client $\leftarrow$ Server & Notification that a player named [name] has left the room which the client receiving the message is in.\\
-\hline
-\textit{ROOMLIST [list]} & Client $\leftarrow$ Server & Notification that the list of players in the client's current room should be repopulated. [list] is a newline-delimited list of names.\\
-\hline
-\textit{NPCLIST [list]}  & Client $\leftarrow$ Server & Notification that the list of NPCs should be updated. [list] is a newline-delimited list of NPC names.\\
-\hline
-\textit{ROOMITEMS [list]} & Client $\leftarrow$ Server & Notification of all the items in the current room. [list] is a newline- delimited list of all the items in the room.\\
-\hline
-\textit{ROOMDESC [description} & Client $\leftarrow$ Server & Notification of the client's current room's description.\\
-\hline
-\textit{ROOMEXITS [list]} & Client $\leftarrow$ Server & Notification of all possible exits from the client's current room.\\
-\hline
-\textit{ROOMPLAYERS} & Client $\rightarrow$ Server & Request for a list of players in the client's current room.\\
-\hline
-\textit{DUNGEONPLAYERS} & Client $\rightarrow$ Server & Request for a list of players in the client's current dungeon.\\
-\hline
-\textit{ROOMNPCS} & Client $\rightarrow$ Server & Request for a list of NPCs in the client's current room.\\
-\hline
-\textit{DESCRIBE} & Client $\rightarrow$ Server & Request for a room description of the client's current room.\\
-\hline
-\textit{ITEMS} & Client $\rightarrow$ Server & Request for a list of items in the client's current room.\\
-\hline
-\textit{EXITS} & Client $\rightarrow$ Server & Request for a list of exits in the client's current room.\\
-\hline
-\textit{HELP} & Client $\rightarrow$ Server & Request for a list of available commands and their descriptions.\\
-\hline
-\textit{DUNGEONENTER [name]} & Client $\leftarrow$ Server & Notification that a player named [name] has entered the same dungeon the client is currently in.\\
-\hline
-\textit{DUNGEONLEAVE [name]} & Client $\leftarrow$ Server & Notification that a player named [name] has left the room which the client receiving the message is in.\\
-\hline
-\textit{DUNGEONLIST [list]} & Client $\leftarrow$ Server & Notification that the list of players in the client's current room should be repopulated. [list] is a newline-delimited list of names.\\
-\hline
-\end{longtable}
-\end{appendices}
-
 \end{document}

### 2014-05-06 src/lostvaults/server/Player.scala

@@ -1,4 +1,5 @@
 package lostvaults.server
+import scala.mutable 
 import akka.actor.Actor
 import akka.util.ByteString
 import akka.io.{ Tcp }
@@ -13,6 +14,9 @@ class Player extends Actor {
   var dungeon = self
   var whisperTo = ""
   var whisperMsg = ""
+  	var HP = 0
+    var Defense = 0
+    var Attack = 0 
 
   def receive = {
     case Received(msg) => {

### 2014-05-06 src/lostvaults/server/Consumable.scala
Items initial commit

@@ -1,0 +1,16 @@
+package lostvaults.server
+
+class Consumable(_name: String, _value: Int, _effect: Int) extends Item(_name: String, _value: Int) {
+  var effect = _effect // this value is negative if the potion takes life and positive if it gives life
+
+  
+  
+  // getters and setters
+  def getEffect = {
+    effect
+  }
+  def setEffect(_effect: Int) {
+    effect = _effect
+  }
+
+}

### 2014-05-06 src/lostvaults/server/EquipType.scala

@@ -1,0 +1,7 @@
+package lostvaults.server
+
+object EquipType extends Enumeration {
+  type EquipType = Value
+  val Weapon, Armor = Value
+}
+

### 2014-05-06 src/lostvaults/server/Equipment.scala

@@ -1,0 +1,19 @@
+package lostvaults.server
+import EquipType._
+
+class Equipment(_name: String, _value: Int, _equipType: EquipType, _effect: Int) extends Item(_name: String, _value: Int) {
+  val equipType = _equipType
+  var effect = _effect
+
+  //getters and setters
+  def getEquipType = {
+    equipType
+  }
+  def getEffect = {
+    effect
+  }
+  def setEffect(_effect: Int) {
+    effect = _effect
+  }
+
+}

### 2014-05-06 src/lostvaults/server/Item.scala

@@ -1,0 +1,18 @@
+package lostvaults.server
+
+class Item (_name : String, _value : Int) {
+	val name : String
+	var value = _value
+  	
+	  
+	// getters and setters
+	def getName = {
+	  name
+	} 	
+	def getValue = {
+	  value
+	}
+	def setValue (_value : Int) {
+	  value = _value
+	}
+}

### 2014-05-06 src/lostvaults/client/GUI.java
--

@@ -6,332 +6,331 @@ import java.awt.*;
 import java.awt.event.*;
 
 public class GUI {
+	String name;
 
+	int screenWidth;
+	int screenHeight;
 
-    String name;
+	JTextArea dynamicInfo = new JTextArea();
+	JTextField commandInputField = new JTextField();
 
-    int screenWidth;
-    int screenHeight;
+	JTextArea dungeonPlayers = new JTextArea();
+	JTextArea roomPlayers = new JTextArea();
+	JTextArea others = new JTextArea();
+	JTextArea items = new JTextArea();
+	JTextArea exits = new JTextArea();
+	JLabel stats = new JLabel();
+	JFrame window = new JFrame("The Lost Vaults");
 
-    JTextArea dynamicInfo = new JTextArea();
-    JTextField commandInputField = new JTextField();
-
-    JTextArea dungeonPlayers = new JTextArea();
-    JTextArea roomPlayers = new JTextArea();
-    JTextArea others = new JTextArea();
-    JTextArea items = new JTextArea();
-    JTextArea exits = new JTextArea();
-    JLabel stats = new JLabel();
-    JFrame window = new JFrame("The Lost Vaults");
-
-    
-    Color darkBackground = new Color(0x800000);
-    Color lightBackground = new Color(0xDAC8A3);
-    Color textColor = new Color(0x3D1515);
-    Color lightTextColor = new Color(0xDE9D5C);
-    Color mediumBackground = new Color(0xC2A366);
-    Color darkMediumBackground = new Color(0xB58C3C);
-
-    Font font = new Font("Serif", Font.BOLD + Font.ITALIC, 14);
-    Font bigFont = new Font("Serif", Font.BOLD + Font.ITALIC, 15);
-
-    public String getName() { return name; }
-
-    public GUI() {				
-	// Dimension screenSize = Toolkit.getDefaultToolkit().getScreenSize();
-	screenWidth = 1000; // screenSize.width;
-	screenHeight = 600; // screenSize.height;
-	window.setSize(screenWidth, screenHeight);
-	// window.setUndecorated(true); //true -> no exit button
-	window.setLayout(new BorderLayout());
-	window.setDefaultCloseOperation(JFrame.EXIT_ON_CLOSE);
-	
-	dynamicInfo.setEditable(false);
-	dynamicInfo.setBackground(lightBackground);
[…]

### 2014-05-06 src/lostvaults/server/Combat.scala

@@ -17,7 +17,6 @@ class Combat extends Actor with FSM[CombatState, CombatData] {
   startWith(Rest, RestData(List(), 0))
 
   when(Rest, stateTimeout = 10.milliseconds) {
-
     case Event(AddPlayer(name, speed), data: RestData) => {
       val NextList = data.PlayerList :+ Tuple2[String, Int](name, speed)
       goto(Rest) using RestData(NextList.sortWith((a, b) => a._2 < b._2), data.Duration)

### 2014-05-06 src/lostvaults/server/ConMan.scala

@@ -17,7 +17,7 @@ class ConMan extends Actor {
   val manager = IO(Tcp)
 
   override def preStart() {
-    manager ! Bind(self, new InetSocketAddress("localhost", 51234))
+    manager ! Bind(self, new InetSocketAddress("0.0.0.0", 51234))
   }
   
   def receive() = {
@@ -25,13 +25,11 @@ class ConMan extends Actor {
       println("Failed to bind to 0.0.0.0:51234")
     }
     case Bound(local) => {
-      printf("Hejsan")
       // Do interesting stuff
     }
     case c @ Connected(remote, local) => {
       val newplayer = context.actorOf(Props[Player])
       sender ! Register(newplayer)
-      println("New connection from: " + remote)
     }
   }
 }

### 2014-05-06 src/lostvaults/server/Dungeon.scala

@@ -28,43 +28,29 @@ class Dungeon extends Actor {
   def CityReceive: Receive = {
     case GameSay(name, msg) => {
       PSet foreach (c =>
-        PMap ! PMapGetPlayer(c, "Say " + name + " " + msg))
+        PMap ! PMapSendGameMessage(c, GameSay(name, msg)))
     }
+    
     case GameAddPlayer(name) => {
-      PSet foreach (c => PMap ! PMapGetPlayer(c, "AddPlayer " + name)) // Send "GamePlayerEnter" to all other players*/
+      PSet foreach (c => if (name != c) PMap ! PMapSendGameMessage(c, GamePlayerEnter(name)))
       PSet += name
-      PMap ! PMapGetPlayer(name, "MovePlayer " + name)
+      PMap ! PMapSendGameMessage(name, GameMoveToDungeon(self))
     }
+    
     case GameRemovePlayer(name) => {
       PSet -= name
-      PSet foreach (c => if (name != c) PMap ! PMapGetPlayer(c, "RemovePlayer " + name)) // Send "GamePlayerEnter" to all other players*/ 
+      PSet foreach (c => if (name != c) PMap ! PMapSendGameMessage(c, GamePlayerLeft(name))) // Send "GamePlayerLeft" to all other players*/ 
     }
-    case PMapGetPlayerResponse(player, purpose) => {
-      val action = Parser.findWord(purpose, 0)
-      action match {
-        case "Say" => {
-          val name = Parser.findWord(purpose, 1)
-          val msg = Parser.findRest(purpose, 1)
-          if (!player.isEmpty)
-            player.get ! GameSay(name, msg)
-        }
-        case "AddPlayer" => {
-          val name = Parser.findWord(purpose, 1)
-          if (!player.isEmpty)
-            player.get ! GamePlayerEnter(name)
-        }
-        case "RemovePlayer" => {
-          val name = Parser.findWord(purpose, 1)
-          if (!player.isEmpty)
-            player.get ! GamePlayerLeft(name)
-        }
-        case "MovePlayer" => {
-          val name = Parser.findWord(purpose, 1)
-          if (!player.isEmpty)
-            player.get ! GameMoveToDungeon(self)
-        }
-      }
+    
+    case GameNotifyDungeon(msg) => {
+      PSet foreach(c => ( PMap ! PMapSendGameMessage(c, GameSystem(msg))))
+    }
+    case GameNotifyRoom(msg) => {
[…]

### 2014-05-06 src/lostvaults/server/GameMsg.scala

@@ -56,8 +56,18 @@ case class GamePlayerEnter(name: String) extends GameMsg
  */
 case class GameMoveToDungeon(dungeon: ActorRef) extends GameMsg
 /**
- * Passed along to a player, this will send the message "System msg" to the 
+ * Passed along to a player, this will send the message "SYSTEM msg" to the 
  * remote connection.
  * @param msg The system message to be sent to the client. 
  */
 case class GameSystem(msg: String) extends GameMsg
+/**
+ * Passed along to a dungeon, this will send a system message to all players in the dungeon passed along to it.
+ * @param msg The notification to be sent. 
+ */
+case class GameNotifyDungeon(msg: String) extends GameMsg
+/**
+ * Passed along to a dungeon, this will send a system message to the room the sender is in. 
+ * @param msg The notification to be sent.
+ */
+case class GameNotifyRoom(msg: String) extends GameMsg

### 2014-05-06 src/lostvaults/server/Combat.scala
Combat

@@ -14,6 +14,8 @@ case class RestData(PlayerList: List[Tuple2[String, Int]], Duration: Int) extend
 case class ActionData(PlayerList: List[Tuple2[String, Int]], TurnList: List[String], Duration: Int) extends CombatData
 
 class Combat extends Actor with FSM[CombatState, CombatData] {
+  val PMap = Main.PMap.get
+
   startWith(Rest, RestData(List(), 0))
 
   when(Rest, stateTimeout = 10.milliseconds) {
@@ -25,22 +27,49 @@ class Combat extends Actor with FSM[CombatState, CombatData] {
 
     case Event(StateTimeout, data: RestData) => {
       val nextDuration = data.Duration + 1
-      val TurnList: List[String] = List()
-      data.PlayerList.foreach(c => if(nextDuration % c._2 == 0) TurnList :+ c._1)
-      goto(Rest) using RestData(data.PlayerList, nextDuration)
+      var turnList: List[String] = List()
+      data.PlayerList.foreach(c => if (nextDuration % c._2 == 0) c._1 :: turnList)
+      if (turnList isEmpty) {
+        goto(Rest) using RestData(data.PlayerList, nextDuration)
+      } else {
+        goto(Action) using ActionData(data.PlayerList, turnList, data.Duration)
+      }
     }
   }
-  
-  
+
+  onTransition {
+    case _ -> Action => {
+      var player = nextStateData.asInstanceOf[ActionData].TurnList.head
+      PMap ! PMapSendMessage(player, GameYourTurn)
+    }
+  }
+
   when(Action) {
     case Event(AttackPlayer(target), data: ActionData) => {
-    	val nextPlayer = data.TurnList.head
-    	val turnList = data.TurnList.tail
-    	//ask player for action and act
-    	if(turnList isEmpty)
-    		goto(Rest) using RestData(data.PlayerList, data.Duration)
-    	else    		
-    		goto(Action) using ActionData(data.PlayerList, turnList, data.Duration)
-      }
+      val nextPlayer = data.TurnList.head
+      val turnList = data.TurnList.tail
+      if (turnList isEmpty)
+        goto(Rest) using RestData(data.PlayerList, data.Duration)
+      else
+        goto(Action) using ActionData(data.PlayerList, turnList, data.Duration)
+    }
+    case Event(DrinkPotion, data: ActionData) => {
+      val turnList = data.TurnList.tail
+      if (turnList isEmpty)
[…]

### 2014-05-06 src/lostvaults/server/GameMsg.scala

@@ -61,3 +61,18 @@ case class GameMoveToDungeon(dungeon: ActorRef) extends GameMsg
  * @param msg The system message to be sent to the client. 
  */
 case class GameSystem(msg: String) extends GameMsg
+/**
+ * Passed along to a player when it is that player's turn in combat
+ */
+case object GameYourTurn extends GameMsg
+/**
+ * Passed along to a player, tells how much damage that player has suffered
+ * @param damage The amount of damage the player has suffered
+ * @param from Who has afflicted the damage on the player
+ */
+case class GameDamage(from: String, damage: Int) extends GameMsg
+/**
+ * Passed along to a combad, when a player has died
+ * @param player The player that is dead
+ */
+case class GameHasDied(player: String) extends GameMsg

### 2014-05-06 src/lostvaults/server/Item.scala

@@ -3,16 +3,4 @@ package lostvaults.server
 class Item (_name : String, _value : Int) {
 	val name : String
 	var value = _value
-  	
-	  
-	// getters and setters
-	def getName = {
-	  name
-	} 	
-	def getValue = {
-	  value
-	}
-	def setValue (_value : Int) {
-	  value = _value
-	}
 }

### 2014-05-06 src/lostvaults/server/ConMan.scala
Room, RoomRandom, Dungeon

@@ -25,7 +25,7 @@ class ConMan extends Actor {
       println("Failed to bind to 0.0.0.0:51234")
     }
     case Bound(local) => {
-      printf("Hejsan")
+      // printf("Hejsan")
       // Do interesting stuff
     }
     case c @ Connected(remote, local) => {

### 2014-05-06 src/lostvaults/server/Dungeon.scala

@@ -3,11 +3,14 @@ package lostvaults.server
 import akka.actor.Actor
 import scala.collection.mutable.Set
 import lostvaults.Parser
+import scala.util.Random
 /**
  * Special case message which tells a dungeon to act as the city process. Only sent
  * to a single dungeon actor instance at the start of the server's life.
  */
 case object DungeonMakeCity
+
+case object NewDungeon
 /**
  * Dungeon is an actor class in charge of carrying the Main logic of the game,
  *  either as a dungeon or as the special-case City actor. The dungeon allows for
@@ -21,10 +24,20 @@ class Dungeon extends Actor {
   val PMap = Main.PMap.get
   def receive() = {
     case DungeonMakeCity => {
+      val CityRoom = new Room()
+      // lägg till alla NPCs
       become(CityReceive)
+    }
+    case NewDungeon => {
+      val Rooms = new Array[Room](100)	// 10 x 10 Room array
+      RoomRandom.init(Rooms)
+      //become(DungeonReceive)
+
+      
     }
   }
 
+  
   def CityReceive: Receive = {
     case GameSay(name, msg) => {
       PSet foreach (c =>

### 2014-05-06 src/lostvaults/server/Room.scala

@@ -1,0 +1,91 @@
+package lostvaults.server
+
+
+
+class Room() {
+  var north: Boolean
+  var east: Boolean
+  var south: Boolean
+  var west: Boolean
+
+  var created = false
+  var connected = false
+  
+  def isCreated() = {
+    created = true
+  }
+  
+  def isConnected() = {
+    connected = true
+  }
+  
+  def northConnected = {
+    north = true
+  }
+  def southConnected = {
+    south = true
+  }  
+  def westConnected = {
+    west = true
+  } 
+  def eastConnected = {
+    east = true
+  }  
+  
+  
+  var playerList: List[String]
+  var itemList: List[Item]
+//  var NPCList: List[NPC]
+    
+  
+  def addPlayer(player: String) = {
+    player::playerList
+  }
+  
+  def removePlayer(player: String) = {
+    playerList = playerList.filterNot((c => c == player))
+  }
+  
+  def getPlayerList() : List[String] = {
+    return playerList
+  }
+  
+  def hasPlayer(player: String): Boolean = {
+    return playerList.contains(player)
+  }
+  
+  
+  def addItem(newItem : Item) = {
+    newItem::itemList
+  }
+  
+  def removeItem(item: Item) = {
+    itemList = itemList.filterNot((c => c == item))
+  }
+  
+  def getItemList() : List[Item] = {
+    return itemList
+  }
+  
+  def hasItem(item: Item) : Boolean = {
+    return itemList.contains(item)
+  }
+  
+  
+//  def addNPC(newNPC: NPC) = {
+//    newNPC::NPCList
+//  }
+//  
+//  def removeNPC(nPC: NPC) = {
+//    NPCList = NPCList.filterNot((c => c == nPC))
+//  }
+//  
+//  def getNPCList() : List[NPC] = {
+//    return NPCList
+//  }
+//  
+//  def hasNPC(nPC: NPC) : Boolean = {
+//    return NPCList.contains(nPC)
+//  }
+  
+}

### 2014-05-06 src/lostvaults/server/RoomRandom.scala

@@ -1,0 +1,51 @@
+package lostvaults.server
+
+import scala.util.Random
+
+object RoomRandom {
+
+  def init(Rooms: Array[Room]) = {
+    val Random = new Random()
+    var StartRoom = Random.nextInt(89)
+    if (StartRoom < 10) {
+      StartRoom += 10
+    }
+    if ((StartRoom % 10) == 0) {
+      StartRoom + 1
+    }
+    val StartString = StartRoom.toString
+    if (StartString.contains("9")) {
+      StartRoom - 1
+    }
+
+    Rooms(StartRoom).isConnected
+    Rooms(StartRoom).isCreated
+    Rooms(StartRoom).eastConnected
+    Rooms(StartRoom).northConnected
+    Rooms(StartRoom).westConnected
+    Rooms(StartRoom).southConnected
+
+    Rooms(StartRoom - 1).isConnected
+    Rooms(StartRoom - 1).isCreated
+    Rooms(StartRoom - 1).eastConnected
+
+    Rooms(StartRoom + 1).isConnected
+    Rooms(StartRoom + 1).isCreated
+    Rooms(StartRoom + 1).westConnected
+
+    Rooms(StartRoom + 10).isConnected
+    Rooms(StartRoom + 10).isCreated
+    Rooms(StartRoom + 10).southConnected
+
+    Rooms(StartRoom - 10).isConnected
+    Rooms(StartRoom - 10).isCreated
+    Rooms(StartRoom - 10).northConnected
+    
+    makeMagic
+  }
+  
+  def makeMagic() = {
+    
+  }
+
+}

### 2014-05-06 src/lostvaults/server/Dungeon.scala
Fixed small errors

@@ -3,7 +3,6 @@ package lostvaults.server
 import akka.actor.Actor
 import scala.collection.mutable.Set
 import lostvaults.Parser
-import scala.util.Random
 /**
  * Special case message which tells a dungeon to act as the city process. Only sent
  * to a single dungeon actor instance at the start of the server's life.

### 2014-05-06 src/lostvaults/server/Room.scala

@@ -11,12 +11,20 @@ class Room() {
   var created = false
   var connected = false
   
-  def isCreated() = {
+  def setCreated() = {
     created = true
   }
   
-  def isConnected() = {
+  def isCreated() : Boolean = {
+    return created
+  }
+  
+  def setConnected() = {
     connected = true
+  }
+  
+  def isConnected() : Boolean = {
+    return connected
   }
   
   def northConnected = {

### 2014-05-22 src/lostvaults/server/Dungeon.scala
massa roligheter

@@ -180,7 +180,7 @@ class Dungeon extends Actor {
         println("Adding " + attackee + " to combat")
         var npc = rooms(currentRoom).getNPCActorRef(attackee)
         if (npc != None) {
-          npc.get ! GamePlayerJoinBattle(activeCombat.get, attackee)
+          npc.get ! GamePlayerJoinBattle(activeCombat.get, attacker)
         }
       } else {
         PMap ! PMapSendGameMessage(attacker, GameAttackNotInRoom(attackee))

### 2014-05-22 src/lostvaults/server/Item.scala

@@ -108,4 +108,7 @@ class Item(ID: Int, Name: String, Attack: Int, Defense: Int, Speed: Int, ItemTyp
     itemType.compareToIgnoreCase("potion") == 0
   }
 
+  override def toString = {
+    name
+  }
 }

### 2014-05-22 src/lostvaults/server/ItemRepo.scala

@@ -9,7 +9,7 @@ import scala.util.Random
 object ItemRepo {
   import JdbcBackend.Database
   case class ItemData(id: Int, name: String, attack: Int, defense: Int, speed: Int, rating: Int, itemType: String)
-  implicit val getItemDataResult = GetResult(r => ItemData(r.nextInt, r.nextString, r.nextInt,  r.nextInt, r.nextInt, r.nextInt, r.nextString))
+  implicit val getItemDataResult = GetResult(r => ItemData(r.nextInt, r.nextString, r.nextInt, r.nextInt, r.nextInt, r.nextInt, r.nextString))
   val Rnd = new Random(System.currentTimeMillis)
   var itemArray: Array[ItemData] = Array()
   def clearArray() {
@@ -30,8 +30,8 @@ object ItemRepo {
       val r = (Rnd.nextFloat() * rndHigh - 1).asInstanceOf[Int]
       val itemData = pool(r)
       new Item(itemData.id, itemData.name, itemData.attack, itemData.defense, itemData.speed, itemData.itemType)
-    }
-    new Item(-4, "Invalid Item", 0, 0, 0, "Invalid")
+    } else 
+      new Item(-4, "Invalid Item", 0, 0, 0, "Invalid")
   }
 
   def getManyRandom(Amnt: Int, Type: String, Rating: Int): Array[Item] = {

### 2014-05-22 src/lostvaults/server/Room.scala

@@ -173,7 +173,7 @@ class Room() {
    * @return true if this room has this NPC, else false
    */
   def hasNPC(npc: String): Boolean = {
-    NPCList.exists(c => c._1 == npc)
+    NPCList.exists(c => c._1.equalsIgnoreCase(npc))
   }
   def getNPCActorRef(npc: String): Option[ActorRef] = {
     var NPCTupleOption = NPCList.find(c => c._1.equalsIgnoreCase(npc))
@@ -206,6 +206,10 @@ class Room() {
     if (!itemList.isEmpty) {
       ret += "On the floor you find: \n"
       itemList.foreach(item => ret += item.name + "\n")
+    }
+    if (!NPCList.isEmpty) {
+      ret += "You suddenly see: \n"
+        NPCList.foreach(npc => ret += npc._1 + "\n")
     }
     if (playerList.size > 1) {
       ret += "With you is: \n"

### 2014-05-22 src/lostvaults/server/RoomGenerator.scala

@@ -42,7 +42,7 @@ class RoomGenerator {
   def addItemsToRoom(X: Int, Y: Int) {
     if (X != startRoom._1 || Y != startRoom._2) {
       var howMany = rand(0, 3)
-      val range = ( ( ( ( (startRoom._1 - X).abs.asInstanceOf[Double] + (startRoom._2 - Y).abs.asInstanceOf[Double]) ) / 16.0).ceil * 10.0).asInstanceOf[Int]
+      val range = (((((startRoom._1 - X).abs.asInstanceOf[Double] + (startRoom._2 - Y).abs.asInstanceOf[Double])) / 16.0).ceil * 10.0).asInstanceOf[Int]
       var items = ItemRepo.getManyRandom(howMany, "NoTreasure", range)
       items foreach (i => rooms(coordToIndex(X, Y)).addItem(i))
       itemcnt += items.length
@@ -54,10 +54,15 @@ class RoomGenerator {
     }
   }
   def addNPCToRoom(system: ActorSystem, X: Int, Y: Int) {
-    if(X != startRoom._1 || Y != startRoom._2) {
-      var howMany = rand(0, 1)
-      val range = ( ( ( ( (startRoom._1 - X).abs.asInstanceOf[Double] + (startRoom._2 - Y).abs.asInstanceOf[Double]) ) / 16.0).ceil * 10.0).asInstanceOf[Int]
+    println("Hello1")
+    if (X != startRoom._1 || Y != startRoom._2) {
+      println("Hello2")
+      var howMany = 1 //rand(0, 1)
+      println("Hello3")
+      val range = (((((startRoom._1 - X).abs.asInstanceOf[Double] + (startRoom._2 - Y).abs.asInstanceOf[Double])) / 16.0).ceil * 10.0).asInstanceOf[Int]
+      println("Hello4")
       var npcs = NPCRepo.getManyRandom(howMany, system, range)
+      println("Hello5")
       npcs foreach (i => rooms(coordToIndex(X, Y)).addNPC(i))
     }
   }
@@ -240,8 +245,10 @@ class RoomGenerator {
             nextCoord = dir
           }
         } while (!success)
-        created.foreach(c => { rooms(coordToIndex(c)).created = true; rooms(coordToIndex(c)).connected = true; 
-        if (rand(0, 100) <= 50) addItemsToRoom(c._1, c._2) ; if (rand(0, 100) <= 50) addNPCToRoom(system, c._1, c._2)})
[…]

### 2014-05-22 src/lostvaults/server/ItemRepo.scala
merge

@@ -22,7 +22,7 @@ object ItemRepo {
     }
   }
   def getOneRandom(Type: String, Rating: Int): Item = {
-    var pool = Array[ItemData]()
+    var pool = List[ItemData]()
     itemArray foreach (item => if ((item.itemType.compareToIgnoreCase(Type) == 0 || Type.compareToIgnoreCase("Any") == 0 ||
       (Type.compareToIgnoreCase("NoTreasure") == 0 && item.itemType.compareToIgnoreCase("Treasure") != 0)) && item.rating <= Rating) pool = pool :+ item)
     val rndHigh = pool.length
@@ -30,13 +30,13 @@ object ItemRepo {
       val r = (Rnd.nextFloat() * rndHigh - 1).asInstanceOf[Int]
       val itemData = pool(r)
       new Item(itemData.id, itemData.name, itemData.attack, itemData.defense, itemData.speed, itemData.itemType)
-    }
-    new Item(-4, "Invalid Item", 0, 0, 0, "Invalid")
+    } else
+    	new Item(-4, "Invalid Item", 0, 0, 0, "Invalid")
   }
 
-  def getManyRandom(Amnt: Int, Type: String, Rating: Int): Array[Item] = {
-    var pool = Array[ItemData]()
-    var ret = Array[Item]()
+  def getManyRandom(Amnt: Int, Type: String, Rating: Int): List[Item] = {
+    var pool = List[ItemData]()
+    var ret = List[Item]()
     itemArray foreach (item => if ((item.itemType.compareToIgnoreCase(Type) == 0 || Type.compareToIgnoreCase("Any") == 0 ||
       (Type.compareToIgnoreCase("NoTreasure") == 0 && item.itemType.compareToIgnoreCase("Treasure") != 0)) && item.rating <= Rating) pool = pool :+ item)
     val rndHigh = pool.length

### 2014-05-23 src/lostvaults/server/Combat.scala
Now combat is working with NPC

@@ -48,31 +48,31 @@ case object Rest extends CombatState
  * The Action state: Can arrive to this state from Action, WaitForAck and Rest
  * This state waits for a message from the player who's turn it is
  * From this state you can go to Action, WaitForAck or Rest
- * Before going from this state to Action next player will be informed that it is her turn 
+ * Before going from this state to Action next player will be informed that it is her turn
  */
 case object Action extends CombatState
 /**
  * The WaitForAck state: Can arrive to this state from Action
- * This state wait for a message from the player who was attacked, acknowledging that the player 
+ * This state wait for a message from the player who was attacked, acknowledging that the player
  * has received damage and calculated it's new HP. If the player is alive a DamageAck will be received.
  * If the player is dead a RemovePlayer will be received.
- * From this state you can go to Action or Rest 
+ * From this state you can go to Action or Rest
  * Before going from this state to Action next player will be informed that it is her turn
  */
 case object WaitForAck extends CombatState
 /**
- * The data that the states keep track of. 
+ * The data that the states keep track of.
  */
 sealed trait CombatData
 /**
- * Data within Rest. 
+ * Data within Rest.
  * @param PlayerList A list with all players in combat, element in list looks like: Tuple2(name, speed)
  * @param Duration The game clock, increased by 1 with each turn
  * @param CombatsPerPlayer A list with all players in combat, and with each player a list of that player's enemies, element in list looks like: Tuple2(name, List(name of players))
  */
 case class RestData(PlayerList: List[Tuple3[String, Int, ActorRef]], Duration: Int, CombatsPerPlayer: List[Tuple2[String, List[String]]]) extends CombatData
 /**
- * Data within Action. 
+ * Data within Action.
  * @param PlayerList All players in combat, element in list looks like: Tuple2(name, speed)
  * @param TurnList The players who are currently up for their turn
  * @param Duration The game clock, increased by 1 with each turn
@@ -168,9 +168,12 @@ class Combat extends Actor with FSM[CombatState, CombatData] {
 
   when(Action) {
     case Event(AttackPlayer(name, target, strength), data: ActionData) => {
+      println("COMBAT: AttackPlayer received")
[…]

### 2014-05-23 src/lostvaults/server/GameMsg.scala

@@ -191,4 +191,10 @@ case class GameNotifyGUI(room: Int, msg: String) extends GameMsg
 case object GameHeal extends GameMsg
 
 case class GameHarm(amnt: Int) extends GameMsg
+/**
+ * Passed along to a Dungeon, when the NPC has died
+ * @param name The name of the NPC
+ * @param room The room the NPC is in
+ */
+case class GameRemoveNPCFromRoom(name: String, room: Int)
 

### 2014-05-23 src/lostvaults/server/NPC.scala

@@ -4,15 +4,16 @@ import akka.util.ByteString
 import akka.io.{ Tcp }
 import scala.util.Random
 object NPC {
-  def props(name: String, hp: Int, rating: Int): Props = Props(new NPC(name, hp, rating))
+  def props(name: String, hp: Int, rating: Int, dungeon: ActorRef, room: Int): Props = Props(new NPC(name, hp, rating, dungeon, room: Int))
 }
 
 
-class NPC(_name: String, _hp: Int, _rating: Int) extends Actor {
+class NPC(_name: String, _hp: Int, _rating: Int, _dungeon: ActorRef, _room: Int) extends Actor {
   var rand = new Random(System.currentTimeMillis())
   var name = _name
   val PMap = Main.PMap.get
-  var dungeon = self
+  var dungeon = _dungeon
+  var room = _room
   var hp = _hp
   var weapon = ItemRepo.getOneRandom("Weapon", _rating)
   var armor = ItemRepo.getOneRandom("Armor", _rating - 1)
@@ -20,7 +21,7 @@ class NPC(_name: String, _hp: Int, _rating: Int) extends Actor {
   var backPack: List[Item] = List()
   var target = ""
   var battle: Option[ActorRef] = None
-  var currentRoom = -1
+
 
   def getSpeed = {
     println("This NPC:s rating: " + _rating)
@@ -36,28 +37,31 @@ class NPC(_name: String, _hp: Int, _rating: Int) extends Actor {
 
   def receive = {
     case GamePlayerJoinBattle(_battle, enemy) => {
+      println("NPC: GamePlayerJoinBattle received")
       battle = Some(_battle)
       _battle ! AddPlayer(self, name, getSpeed, enemy)
       target = enemy
     }
     case GameYourTurn => {
+      println("NPC: GameYourTurn received")
       if (battle != None) {
         battle.get ! AttackPlayer(name, target, getAttack)
       }
     }
     case GameDamage(from, strength) => {
+      println("NPC: GameDamage received")
       var damage = strength - getDefense
       if (damage < 0) { damage = 0 }
       hp = hp - damage
       if (hp <= 0) {
-        dungeon ! GameRemovePlayer(name)
-        dungeon ! GameNotifyRoom(currentRoom, "NPC " + name + " has received " + damage + " damage from " + from + ". " + name + " has died.")
+        dungeon ! GameRemoveNPCFromRoom(name, room)
[…]

### 2014-05-23 src/lostvaults/server/NPCRepo.scala

@@ -20,31 +20,21 @@ object NPCRepo {
     }
   }
   populateArray
-    def rand(min: Int, max: Int) = {
+  def rand(min: Int, max: Int) = {
     (min + (random.nextFloat() * (max - min))).asInstanceOf[Int]
   }
-  def getRandomNPC(system: ActorSystem, rating: Int): (String, ActorRef) = {
-    println("GetRand HEllo1")
-
+  def getRandomNPC(system: ActorSystem, dungeon: ActorRef, rating: Int, room: Int): (String, ActorRef) = {
     val ratingList = npcList.filter(c => c.rating <= rating)
-    println("GetRand HEllo2")
     val n = random.nextInt(ratingList.length)
-    println("GetRand HEllo3")
     val newNPCData = ratingList.apply(n)
-    println("GetRand HEllo4")
     var hp = rand(newNPCData.minhp, newNPCData.maxhp)
-    println("GetRand HEllo5")
-    (newNPCData.name, system.actorOf(NPC.props(newNPCData.name, hp, newNPCData.rating)))
+    (newNPCData.name, system.actorOf(NPC.props(newNPCData.name, hp, newNPCData.rating, dungeon, room)))
   }
-  def getManyRandom(num: Int, system: ActorSystem, rating: Int): List[(String, ActorRef)] = {
-    println("GetMany Hello1")
+  def getManyRandom(num: Int, system: ActorSystem, dungeon: ActorRef, rating: Int, room: Int): List[(String, ActorRef)] = {
     var list: List[(String, ActorRef)] = List()
-    println("GetMany Hello2")
     for (x <- 0 until num) {
-      println("GetMany Hello3")
-      list = getRandomNPC(system, rating) :: list
+      list = getRandomNPC(system, dungeon, rating, room) :: list
     }
-    println("GetMany Hello4")
     list
   }
 }

### 2014-05-23 src/lostvaults/server/Player.scala

@@ -316,16 +316,18 @@ class Player extends Actor {
           pushToNetwork("SYSTEM " + _name + " is not in room, so you cannot attack her/him")
         }
         case GamePlayerJoinBattle(_battle, enemy) => {
+          println("PLAYER: GamePlayerJoinBattle received")
           battle = Some(_battle)
           _battle ! AddPlayer(self, name, getSpeed, enemy)
         }
         case GameYourTurn => {
-          println("It is " + name + "'s turn")
+          println("PLAYER: It is " + name + "'s turn")
+          println("PLAYER: Current State is " + state)
           state match {
             case PAttack => {
               if (battle != None) {
+                println("PLAYER: sending attack message to combat")
                 battle.get ! AttackPlayer(name, target, getAttack)
-                state
               }
             }
             case PDrinkPotion => {
@@ -335,7 +337,6 @@ class Player extends Actor {
             }
             case PDecide => {
               pushToNetwork("SYSTEM It's your turn")
-              state
             }
           }
         }
@@ -368,6 +369,7 @@ class Player extends Actor {
           sendStats
         }
         case GameDamage(from, strength) => {
+          println("PLAYER: GameDamage received")
           var damage = strength - getDefense
           if (damage < 0) { damage = 0 }
           hp = hp - damage

### 2014-05-23 doc/src/draft.tex
Preparing for final report, updated build.xml to reflect new doc directory structure, added draft.tex latex file for report draft.

\documentclass[a4paper]{article}
\usepackage[swedish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png}

\title{The Lost Vaults: Uneasy Alliance\\\small{Operativsystem och multicoreprogrammering (1DT089) våren 2013}\\\small{Slutrapport för grupp 4}}

\author{Felix Färjsjö\\(19911225-4678) \and Jimmy Holm\\(19870928-0138) \and Fredrik Larsson\\(19890422-0590) \and Anna Nilsson\\(19910804-0628) \and Philip Åkerfeldt\\(19920508-1335)}

\date{\today\\Version 1.0}

\begin{document}
\maketitle
\newpage
\tableofcontents
\listoffigures
\newpage
\section{Inledning}
Concurrency är en aspekt inom mjukvaruutveckling som ökar i betydelse då datorer förlitar sig mer och mer på parallell bearbetning och till följd av detta måste vårt sätt att skriva 
program justeras. Denna nya sort av arkitektur medför nya problem och om vi inte anpassar oss kommer denna utökning i kapacitet förbli outnyttjad. För att utforska dessa nya utmaningar 
och dess lösningar, valde vi att arbeta fram ett server-client system över en TCP/IP nätverksuppkoppling. Problemen vi försökte lösa var att upprätthålla en mottaglig miljö för multipla, 
simultana uppkopplingar och samtidigt ha flera aktiva samt oberoende sektioner av programlogik. Vi representerar detta problem genom ett multi-user dungeon eller MUD, 
en sorts online multiplayerspel, där målet var att säkerställa att servern upprätthåller ett stabilt verkställande oavsett antal uppkopplade användare.

Vi beslutade att kalla spelet Lost Vaults, ett semi-traditionellt MUD där användaren interagerar med andra spelare och tar del i uppdrag. Detta sker i grupper av flertal spelare som 
tillsammans arbetar mot ett gemensamt mål samtidigt som varje enskild gruppmedlem har en personlig agenda som endast gagnar den enskilda invididen. Möjligheten finns att utforska som 
enskild individ, men fokuset för spelet ligger i den dynamik som följer av interaktionen med andra spelare. Spelet utspelas på två olika platser, i City och i Dungeon; där City är 
staden där spelarna samlas efter tidigare utforskningar, kan fylla på förnödenheter samt forma grupper för att gå ner i Dungeons. Dungeons är en procedurellt genererad uppsättning 
rum fyllt med monster, fällor och skatter. Varje grupp spelare får alltså sin egen unikt genererade Dungeon när gruppen går ner i dessa magiska grottor under staden. Väl inne ges 
gruppen en eller flera uppdrag som bör fullbordas under upptäcksfärden.

Som beskrivet nedan i delen om speldesign, finns det två typer av uppdrag: grupp- och spelaruppdrag. Gruppuppdrag gagnar alla spelare i gruppen medan spelaruppdragen gynnar den enskilde. 
Vårt mål var att skapa en atmosfär där spelare behöver lita på varandra för att fullborda de svårare gruppuppdragen, fast samtidigt vara misstänksamma mot varandra då vem som helst kan 
förråda gruppen för att färdigställa sina personliga uppdrag.

Den slutgiltiga produkten för detta projekt är ett fullt funktionellt och interaktivt multiplayer online role playing game kallat Lost Vaults.

Relationen mellan konceptet concurrency och vårt projekt är förmågan att ha fler än en spelare aktiva i spelet samtidigt och se hur dessa interagerar med varandra, samt flertalet 
aktiva spelområden körandes samtidigt och oberoende av varandra.

\section{System architecture}
\subsection{Design}
Systemarkitekturen som återfinns i detta dokument är uppdelat i Client-side arkitektur och Server-side arkitektur. Applikation, skriven i Scala, körs i Java Virtual Machine och på 
grund av detta kan både klient och server köras på alla plattformar som stödjer Java VM 1.7.

****** figur 1****

\subsection{Client side}
Målet med designen för klienten till Lost Vaults var att ta fram något som kunde efterliknas med en indirekt terminal, där ingen logik används förutom att skicka förfrågningar och 
motta samt tolka svaren på förfrågningar. I slutänden hoppas vi kunna åstadkomma en client-side implementation som lätt kan utökas när serverns implementation av spelets logik ökar, 
alltså ett system som kan utkökas enkelt endast genom att addera nya förfrågningar och svar.

Som synes i Figur 1 är klientfönstret uppdelat i flera textfält som visar relevant information för spelaren. Huvudområdet är för vanliga server-svar och kommer innehålla beskrivningar 
av rummet, meddelanden i spelarchatten, meddelanden med systeminformation och liknande. Klientens högra sida är reserverat för ständig information som spelaren behöver ta del av snabbt. 
Den övre delen innehåller information om spelarens egen karaktär, där spelarens liv och stridsegenskaper samt hur mycket mat gruppen har listas.

Den nedre delen av fönstret innehåller kommandoraden, där spelaren skriver in kommandon i enlighet med ett strikt syntax. När klienten startas välkomnas spelaren 
av ett centrerat fönster för inloggning . Här kan spelaren skriva in sitt användarnamn och lösenord samt IP:n till den server som spelaren vill koppla upp sig mot.

Klientens GUI är implementerat i Javas Swing UI bibliotek och integrerat i Scala för att använda Akkas TCP funktionalitet.

**Figur 2**

\subsubsection{Class model}
Klienten är strukturerad i fyra olika distinkta klasser som beskrivs i Figur 2. Klasserna PlayGame och PlayGameCommunication arbetar 
tillsammans för att skapa en brygga mellan TCP lagret och GUI:t, där PlayGame accepterar meddelanden från TCPClient och skickar dem 
vidare till GUI via PlayGameCommunication. Samtidigt så skickas data från GUI över nätverket via metodanrop i PlayGameCommuncation till 
PlayGame för att sedan hamna hos TCPClient.

\subsection{Server side}
Systemarkitekturens serverdel är uppdelad i sektionerna Concurrency Model, Actor Model och Class Model. Den första delen beskriver vårt 
val av concurrencymodell, och anledningen till valet. Den andra delen beskriver funktionen hos de fem stora actor-typer i Lost Vaults servern och 
den tredje ger en ingående beskrivning hur klassförhållanden används av servern.

\subsubsection{Concurrency model}
Actor modellen har använts för projektet då vi under vår initiala diskussion gällande designen lyckades isolera beteenden i mindre och till stor del 
fristående sektioner. Dessa sektioner kunde enkelt skapas för att dela data enbart genom meddelandesändning som i sin tur leder till att problem 
såsom deadlock kunde undvikas.

För att implementera denna sortens system och bibehålla hög effektivitet valde vi Scala som programspråk till servern av den enkla anledningen att 
skalbarheten är ett av språkets fundamentala mål. Genom rekommendationer av skaparna bakom Scala och via språkets styrkor och enkelhet, beslöt vi 
att använda Akka som vårt aktörbibliotek. Detta för att kunna använda Akkas TCP-bibliotek för nätverkskommunikationen. Bibliotekets enkla integration 
ledde till vårt beslut att använda Scala och Akka som val av programspråk och aktörbibliotek även för klienten, som tidigare nämnts.

**Figur 3**

\subsubsection{Actor model}
Serverdelen är uppdelad i flera processer via Akkas aktörbibliotek för att upprätthålla Actor Concurrency Model i enlighet med Figur 3. Bara två typer av aktörer kommmunicerar 
direkt med nätverket via TCP/IP, Connection Manager-aktören och Player-aktörerna. Connection Manager- aktören har som syfte att hantera inkommande uppkopplingar samt ansvarar 
för att skapa Player-aktörer som nya högnivå aktörer innan de registreras som den nyetablerade uppkopplingens lyssnare. Som lyssnare kommer Player-aktören mottaga och skicka data 
över nätverket genom den etablerade uppkopplingen. Player-aktören styr över alla ting relaterat till klienten, som exempelvis spelarens attribut och för att verifiera 
inloggningsförsök via kommunikation med PlayerMap. Det är även via Player-aktören andra aktörer kan skicka meddelanden över nätverket om det skulle behövas.

PlayerMap-aktören och Groupmap-aktören fyller två specifika funktioner. PlayerMap mappar en sträng, namnet på den uppkopplade spelare, till aktören som kontrollerar 
spelaren med det specifika namnet. Genom denna aktör kan en annan aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - 
ett viktigt kommando som agerar på följande sätt är exempelvis “WHISPER”. PlayerMap möjliggör även ett snabbt och enkelt sätt för Player-aktören att försäkra 
sig om att det inte existerar flera spelare med samma namn på servern.

GroupMap-aktören fyller en liknande funktion som PlayerMap, men länkar istället namnen på spelarna med spelargrupper istället för spelaraktörer. 
En spelargrupp är en samling av en eller fler spelare som tillsammans kan gå ner i en Dungeon som är procedurellt genererad för just dem. Syftet med 
denna aktör är att underlätta skapandet och att ansluta sig till andra spelargrupper. Genom att använda GroupMap räcker det att ansluta sig till en 
spelare via dess namn för att inkluderas i denna spelares grupp, eller för att skapa en ny grupp med denna spelare.

Den fjärde sortens aktör som servern använder är Dungeon-aktören, den som utför spelets logik. 
Det existerar ett speciellt tillstånd av Dungeon-aktören, kallat City- aktören. City existerar ständigt 
under serverns livstid och hanterar spelets sociala aspekt, såsom chattande och skapandet av grupper. 
Det ordinära fallet som Dungeon-aktören ansvarar för är genererandet och hanterandet av den procedurella 
grottan av multipla, sammanlänkade rum i ett tvådimensionellt rutnät. Det är i dessa rum som spelare kommer kunna göra uppdrag, 
finna skatter etc. Dungeon-aktören ansvarar för koordinerandet av alla spelare som finns i grottan. 
Ett exempel på detta är kommandot “SAY”  som ska skickas till relevanta spelare.

Efter att City-aktören har skapat Dungeon-aktören ansvarar den för sin egen livslängd och avsutar sig själv endast när det inte längre finns några spelare i den.

**Figur 4**

\subsubsection{Class model}
Figur 4 visar relationen mellan de olika klasserna i implementation av servern och dess multiplicitet av relevanta förhållanden. 
De är uppdelade i tre kategorier; Utility Layer, Network Communicators och Game Logic. 
Utility Layer tillhandahåller understödjande funktionalitet till de andra klasserna och exakt en av varje klass ska existera vid en given punkt. 
Network Communicators är de som relaterar tillbaka till nätverket genom Akkas TCP bibliotek. Connection manager klassen, ConMan, hanteras som en singleton och endast en 
instans av denna ska existera vid en given tidpunkt. Player-klassen har emellertid en instans för varje öppen uppkoppling.

Game Logic delen innehåller alla interna klasser och där också Dungeon-klassen. Dungeon-klassen är bryggan mellan Network 
Communicators och Game Logic och det är endast via en Dungeon-klass som en Player kan utföra någon handling förutom WHISPER kommandot, 
då detta meddelande är över hela servern. Dungeon-klassen håller koll på utforskade och outforskade rum, uppdrag, grupper, object och NPCs. 
Dungeon håller även koll på de Players som för tillfället är uppkopplade och associerade med en given Dungeon.

\section{Utvecklingsverktyg}

I detta projekt användes flera olika verktyg för att underlätta utvecklingen. Då vi använt Scala som vårt val av programspråk skrevs i princip all vår kod i Eclipse. 
Detta då vi anser att det i särklass är det enklaste sättet att utveckla kod till Java eller Scala. Även fast all kod är skriven i Eclipse använder vi Ant Build System 
för automatiserad kompilering samt byggandet av vår klient och server, klar att köras i Java Virtual Machine.

För hanteringen av versionskontroll har vi använt det tillförlitliga och välkända verktyget Git. Vi satte upp ett nytt git repository på Github.com specifikt för detta 
projekt och valet av Git gjordes på grund av dess styrkor samt att vi är vana användare av det.

Testandet av vår kod görs med ScalaTest ramverket samt ett Ant Build skript som ger oss möjligheten till automatiskt byggande och körning av tester.

Sammansättningen av dokumentationen utförs med Scaladoc på grund av dess likhet med JavaDoc, ett verktyg vi är vana med att använda, och Ant har reviderats för att automatiskt 
bygga vår dokumentation.

\section{Implementation}

\subsection{Programspråk}
Java var det språket vi valde att använda vid skapandet av det grafiska gränssnittet som spelaren agerar mot. Vårt val grundade sig i biblioteket Swing som Java tillhandahåller. 
Med hjälp att detta bibliotek var skapandet av det grafiska gränssnittet en relativt enkel process. Likt många andra av Javas bibliotek var dokumentationen välskriven och enkel 
att använda vilket underlättade processen. En annan aspekt som fick oss att välja Java för just denna del var att vi ville kunna kommunicera med resterande kod, skriven i Scala, 
på ett enkelt sätt och detta kunde uppnås utan problem då Scala är byggt utifrån Javas Virtuella Maskin.

Anledningen till att vi skrev inte skrev hela projektet i Java var på grund av den bristande skalbarheten som språket besitter. Scala däremot erbjöd båda en liknande syntax som 
Java och hade samtidigt bättre skalbarhet. Detta innebar att övergången mellan att skriva Java och Scala var en någorlunda mjuk sådan, koden var ganska lättigenkännlig och systemet 
kunde utvecklas med skalbarhet i åtanke. Några nackdelar med Scala som vi finner nämnvärda är exempelvis att det, trots likheter med Java, tog en viss tid att sätta sig in i det nya 
språket vilket kan ha motarbetat utvecklingen mot om vi hade valt ett annat språk som vi var mer bekanta med. Det är viktigt att inte glömma att de nackdelar vi funnit under 
projektets gång skuggas av fördelarna vi funnit med språket.

\subsection{Algoritmer}

\subsection{Datastrukturer}

\subsection{Concurrency}
Flera spelare samtidigt

\section{Slutsatser}
Något vi gjorde bra var att vi gjorde klart det essentiella för huvudmålet med projektet, att uppnå concurrency på något sätt. 
Då den delen av projektet var klart kunde vi utöka produkten med funktioner för att göra spelet roligare och mer interaktivt. 
Implementation av föremål och monster att slåss mot i grottan. 
Något vi lärt oss är att skriva nätverkskod. Vi har även fått kunskap i ett nytt programspråk.
Det vi tycker har varit svårt var bland annat att integrationstesta våra aktörer. Svårigheterna uppstod på grund av bristande 
information att ta del av om hur vi skulle gå till väga för att göra detta. En annan sak som också varit relativt svår var att 
begränsa oss när det gällde den utsträckning för vilket spelet skulle utvecklas. Att begränsa utvecklingen till en rimlig nivå för spelet 
och samtidigt ha det tillräckligt intressant för den som spelar.

\section{Appendix}

Scala 2.10.4, Akka 2.3.2, SLF4J 1.7.7, Slick 2.0.2, SQLite JDBC 3.7.2

https://github.com/senilica/LostVaults/

Vilka versioner av till exempel Erlang, Java, Python etc har använts?
Hur kan koden laddas ner? Finns koden tillgänglig på till exempel GitHub eller Bitbucket eller som Tar arkiv?  Beskriv projektets katalogstruktur.
Vilket stöd för automatiserad testning finns och hur används det, till exempel JUnit (Java), EUnint (Erlang) eller PyUnit (Python)?
%Vilket stöd för automatiserad generering av dokumentation finns och hur används det, till exempel Doxygen (C, C++, C\#, Fortran, Java, Objective\­C, PHP, Python), EDoc (Erlang), Pydoc (Python), Javadoc (Java)?
Hur kompileras systemet?
Hur startas systemet? tryck på play

\end{document}

### 2014-05-23 doc/src/proposal.tex
Preparing for final report, updated build.xml to reflect new doc directory structure, added draft.tex latex file for report draft.

--- 2014-05-06 doc/ProposalSrc/lostvaults.tex
@@
 Concurrency is becoming a more and more important facet of software development as computers rely more heavily on parallel processing and because of this the way we write programs has to change. 
-This new kind of architecture brings with it a new type of problems, and without adapting we will not be able to make use of the increase in processing power. 
+This new kind of architecture brings with it a new type of problems and without adapting we will not be able to make use of the increase in processing power. 
 As a way for us to explore these challenges and their solutions, we opted to work on a server-client system over a TCP/IP network connection.
@@
 
-As described in the game design portion of this document, there are two types of quests: group quests and player quests. Group quests are to everyone's benefit, and player 
+As described in the game design portion of this document, there are two types of quests: group quests and player quests. Group quests are to everyone's benefit and player 
 quests are individual quests of subterfuge. We aim to create an atmosphere where the players need to rely on each other to achieve the tougher group quests while at the same 
@@
 
-The dungeon's room are created procedurally on demand. That is to say, a new room is only created when a player tries to enter a room that does not yet exist. There are exceptions to 
-this, as will be described in the quest section of this document.
+The dungeon's room are created procedurally at the creation of the dungeon. Each cell in a two-dimensional grid is assigned a room, and random routes connecting them to a starting room are placed 
+down to ensure each room is potentially reachable, provided players have enough food.
 \subsubsection{Rooms}
@@
 the dungeon immediately, however, but an enterprising player may continue to play as part of the group if possible, reaping the rewards from the group quests as well. However, the group 
-knows that someone has been tasked to kill someone else through the \textbf{Every ally must leave} quest. The player does not have to be the one killing the target, as long as the target 
+knows that someone has been tasked to kill someone else through the \textbf{Every ally must survive} quest. The player does not have to be the one killing the target, as long as the target 
 does not exit the dungeon alive.

### 2014-05-23 doc/html/index.js

@@ -1,0 +1,1 @@
+Index.PACKAGES = {"lostvaults.util" : [{"object" : "lostvaults\/util\/ItemAdder$.html", "name" : "lostvaults.util.ItemAdder"}], "akka.pattern" : [], "akka" : [], "lostvaults" : [{"object" : "lostvaults\/Parser$.html", "name" : "lostvaults.Parser"}], "lostvaults.tests" : [{"class" : "lostvaults\/tests\/CombatTest.html", "name" : "lostvaults.tests.CombatTest"}, {"class" : "lostvaults\/tests\/GroupMapTest.html", "name" : "lostvaults.tests.GroupMapTest"}, {"class" : "lostvaults\/tests\/ParserTest.html", "name" : "lostvaults.tests.ParserTest"}, {"class" : "lostvaults\/tests\/PlayerMapTest.html", "name" : "lostvaults.tests.PlayerMapTest"}, {"class" : "lostvaults\/tests\/RoomDescGenTest.html", "name" : "lostvaults.tests.RoomDescGenTest"}, {"class" : "lostvaults\/tests\/RoomGenTest.html", "name" : "lostvaults.tests.RoomGenTest"}, {"class" : "lostvaults\/tests\/RoomTest.html", "name" : "lostvaults.tests.RoomTest"}, {"object" : "lostvaults\/tests\/TestHelpFunctions$.html", "name" : "lostvaults.tests.TestHelpFunctions"}], "lostvaults.client" : [{"object" : "lostvaults\/client\/ConnClosed$.html", "name" : "lostvaults.client.ConnClosed"}, {"case class" : "lostvaults\/client\/ConnectTo.html", "name" : "lostvaults.client.ConnectTo"}, {"class" : "lostvaults\/client\/GUI.html", "name" : "lostvaults.client.GUI"}, {"class" : "lostvaults\/client\/Logger.html", "name" : "lostvaults.client.Logger"}, {"object" : "lostvaults\/client\/Main$.html", "name" : "lostvaults.client.Main"}, {"trait" : "lostvaults\/client\/MyMsg.html", "name" : "lostvaults.client.MyMsg"}, {"object" : "lostvaults\/client\/Ok$.html", "name" : "lostvaults.client.Ok"}, {"object" : "lostvaults\/client\/playGame$.html", "class" : "lostvaults\/client\/playGame.html", "name" : "lostvaults.client.playGame"}, {"object" : "lostvaults\/client\/playGameCommunication$.ht
[…]

### 2014-05-23 src/lostvaults/server/CheatActor.scala
Directory Structure updated, ant archive added.

@@ -101,7 +101,7 @@ class CheatActor extends Actor {
               implicit session =>
                 val sql = "SELECT * FROM ITEMS WHERE name LIKE '%" + name + "%'"
                 println("Listing all items containing \"" + name + "\":")
-                Q.queryNA[ItemData](sql) foreach (i => println("ID: " + i.id + "\tName: " + i.name + (if(i.name.length < 15)"\t" else if(i.name.length < 20)"\t\t"else"\t") + "Atk: " + i.attack + "\tDef: " + i.attack + "\tSpd: " + i.attack))
+                Q.queryNA[ItemData](sql) foreach (i => println("ID: " + i.id + "\tName: " + i.name + (if(i.name.length < 15)"\t" else if(i.name.length < 20)"\t\t"else"\t") + "Atk: " + i.attack + "\tDef: " + i.defense+ "\tSpd: " + i.speed))
                 println("Finished.")
             }
           } else if (Parser.findWord(m, 1).compareTo("npc") == 0) { // Find npcs

### 2014-05-23 src/lostvaults/client/GUI.java
Cursor fix in GUI, Combat fix in Server

@@ -278,6 +278,7 @@ public class GUI {
 
 			setLocationRelativeTo(null);
 			setVisible(true);
+			userNameInput.requestFocus();
 		}
 
 		/*******************************************
@@ -322,6 +323,7 @@ public class GUI {
 								+ name);
 				playGameCommunication.sendIP(ip);
 				window.setVisible(true);
+				commandInputField.requestFocus();
 				dispose();
 			}
 		}

### 2014-05-23 src/lostvaults/server/Dungeon.scala

@@ -123,6 +123,7 @@ class Dungeon extends Actor {
         rooms(nextRoom).addPlayer(name)
         PMap ! PMapSendGameMessage(name, GameDungeonMove(nextRoom, false))
         PMap ! PMapSendGameMessage(name, GameMessage("ROOMEXITS " + rooms(nextRoom).getExitsString))
+        PMap ! PMapSendGameMessage(name, GameMessage("NPCLIST " + rooms(nextRoom).getNPCString))
         PMap ! PMapSendGameMessage(name, GameSystem(rooms(nextRoom).getDescription(name)))
         rooms(nextRoom).getPlayerList.foreach(c => if (c != name) { PMap ! PMapSendGameMessage(c, GameMessage("ROOMJOIN " + name)) })
         PMap ! PMapSendGameMessage(name, GameMessage("ROOMLIST " + rooms(nextRoom).getPlayerList.foldRight("")((pName, s) => if (pName != name) { pName + "\n" + s } else { "" + s })))
@@ -150,8 +151,9 @@ class Dungeon extends Actor {
         context stop self
       }
     }
-    case GameRemoveNPCFromRoom(name, room) => {
-      rooms(room).removeNPC(name)
+    case GameRemoveNPCFromRoom(npc, room) => {
+      rooms(room).removeNPC(npc)
+      rooms(room).playerList foreach(c => PMap ! PMapSendGameMessage(c, GameMessage("NPCLEFT " + npc)))
     }
 
     case GameAttackPlayer(attacker, attackee) => {

### 2014-05-23 src/lostvaults/server/Room.scala

@@ -159,12 +159,8 @@ class Room() {
     NPCList = NPCList.filterNot((c => c._1 == npc))
   }
 
-  /**
-   * This method returns the list of NPCs in the room.
-   * @return the NPC's in this room
-   */
-  def getNPCList(): List[(String, ActorRef)] = {
-    NPCList
+  def getNPCString = {
+    NPCList.foldRight("")((npc, list) => npc._1 + "\n" + list)
   }
 
   /**
@@ -209,7 +205,7 @@ class Room() {
     }
     if (!NPCList.isEmpty) {
       ret += "You suddenly see: \n"
-        NPCList.foreach(npc => ret += npc._1 + "\n")
+      NPCList.foreach(npc => ret += npc._1 + "\n")
     }
     if (playerList.size > 1) {
       ret += "With you is: \n"

### 2014-05-23 src/lostvaults/server/RoomGenerator.scala

@@ -10,6 +10,8 @@ class RoomGenerator {
   val Width = 10
   val Height = 10
   var rooms = new Array[Room](Width * Height)
+  val MAXDEPTH = 10
+  var startRoom: (Int, Int) = (rand(1, Width - 1), rand(1, Height - 1))
   def coordToIndex(x: Int, y: Int): Int = {
     if (x < 0 || y < 0 || x >= Width || y >= Height)
       0
@@ -31,8 +33,7 @@ class RoomGenerator {
   def rand(min: Int, max: Int) = {
     (min + (Rnd.nextFloat() * (max - min))).asInstanceOf[Int]
   }
-  val MAXDEPTH = 10
-  var startRoom: (Int, Int) = (rand(1, Width - 1), rand(1, Height - 1))
+
   def findEmptyRoom(depth: Int): (Int, Int) = {
     val x = rand(0, Width)
     val y = rand(0, Height)
@@ -42,13 +43,18 @@ class RoomGenerator {
   def addItemsToRoom(X: Int, Y: Int) {
     if (X != startRoom._1 || Y != startRoom._2) {
       var howMany = rand(0, 3)
-      val range = (((((startRoom._1 - X).abs.asInstanceOf[Double] + (startRoom._2 - Y).abs.asInstanceOf[Double])) / 16.0).ceil * 10.0).asInstanceOf[Int]
+      var range = (((((startRoom._1 - X).abs.asInstanceOf[Double] + (startRoom._2 - Y).abs.asInstanceOf[Double])) / 16.0) * 10.0).ceil.asInstanceOf[Int] - 1
+      if(range == 0) range = 1
+      println(startRoom._1 + " - " + X + " + " + startRoom._2 + " - " + Y + " / 16 *  10 = " + range)
+      println("ROOMGENERATOR-addItemsToRoom: This is the range: " + range)
       var items = ItemRepo.getManyRandom(howMany, "NoTreasure", range)
       items foreach (i => rooms(coordToIndex(X, Y)).addItem(i))
       itemcnt += items.length
       howMany = rand(0, 3)
       items = ItemRepo.getManyRandom(howMany, "Treasure", range)
       items foreach (i => rooms(coordToIndex(X, Y)).addItem(i))
+      items foreach (i => print(i.name))
+      println("\nROOMGENERATOR-addItemsToRoom: This is the range: " + range)
       itemcnt += items.length
       itemrooms += 1
     }
[…]

### 2014-05-23 src/lostvaults/server/Dungeon.scala
Allowed partial-matching of item/NPC names.

@@ -31,6 +31,32 @@ class Dungeon extends Actor {
     (index % gen.Width, index / gen.Width)
   }
 
+  def compareStrings(str1: String, str2: String) = {
+    var matches = 0
+    var leng = 0
+    if (str1.length > str2.length) {
+      leng = str1.length
+      for (i <- 0 until str2.length) {
+        if (str1(i).toString().compareToIgnoreCase(str2(i).toString()) == 0 || (str1(str1.length-1-i).toString().compareToIgnoreCase(str2(str2.length-1-i).toString()) == 0)) {
+          matches += 1
+        }
+      }
+    } else {
+      leng = str2.length
+      for (i <- 0 until str1.length) {
+        if (str1(i).toString().compareToIgnoreCase(str2(i).toString()) == 0 || (str1(str1.length-1-i).toString().compareToIgnoreCase(str2(str2.length-1-i).toString()) == 0)) {
+          matches += 1
+        }
+      }
+      if (matches == 0) // Check the reverse as well.
+        for(i <- str2.length until 0 by -1)
+          if (str1(i).toString().compareToIgnoreCase(str2(i).toString()) == 0) {
+          matches += 1
+        }
+    }
+    matches.asInstanceOf[Float] / leng.asInstanceOf[Float]
+  }
+
   def findRoom(name: String): Int = {
     if (PSet.find(n => n.compareToIgnoreCase(name) == 0) == None)
       -1
@@ -155,39 +181,65 @@ class Dungeon extends Actor {
     }
 
     case GameAttackPlayer(attacker, attackee) => {
-      println("PSet: " + PSet + " attackee: " + attackee)
-      var currentRoom = findRoom(attacker)
-      if (rooms(currentRoom).hasPlayer(attackee)) {
-        println(attacker + " attacks player " + attackee)
-        if (activeCombat == None) {
-          println("New combat actor created.")
-          activeCombat = Some(context.actorOf(Props[Combat]))
-          activeCombat.get ! self
+      var nameMatches: List[(Float, String)] = List()
+      var ind = ""
+      PSet foreach (name => {
+        if (name.compareToIgnoreCase(attacker) != 0) {
+          nameMatches = (compareStrings(attackee, name), name) :: nameMatches
         }
-        println("Adding " + attacker + " to combat")
-        PMap ! PMapSendGameMessage(attacker, GamePlayerJoinBattle(activeCombat.get, attackee))
-        PMap ! PMapSendGameMessage(attacker, GameMessage("You have attacked " + attackee))
[…]

### 2014-05-23 src/lostvaults/server/Dungeon.scala
Fix npc list.

@@ -192,7 +192,7 @@ class Dungeon extends Actor {
         println(compareStrings(attackee, name))
       })
       if (nameMatches isEmpty) { // Not a player, check NPCs.
-        val npcs = rooms(findRoom(attacker)).getNPCList
+        val npcs = rooms(findRoom(attacker)).NPCList
         npcs foreach (name => {
           nameMatches = (compareStrings(attackee, name._1), name._1) :: nameMatches
           println(compareStrings(attackee, name._1))

### 2014-05-26 doc/src/draft.tex
Inledning read and change stuff :)

@@
 \section{Inledning}
-Concurrency är en aspekt inom mjukvaruutveckling som ökar i betydelse då datorer förlitar sig mer och mer på parallell bearbetning och till följd av detta måste vårt sätt att skriva 
-program justeras. Denna nya sort av arkitektur medför nya problem och om vi inte anpassar oss kommer denna utökning i kapacitet förbli outnyttjad. För att utforska dessa nya utmaningar 
-och dess lösningar, valde vi att arbeta fram ett server-client system över en TCP/IP nätverksuppkoppling. Problemen vi försökte lösa var att upprätthålla en mottaglig miljö för multipla, 
-simultana uppkopplingar och samtidigt ha flera aktiva samt oberoende sektioner av programlogik. Vi representerar detta problem genom ett multi-user dungeon eller MUD, 
-en sorts online multiplayerspel, där målet var att säkerställa att servern upprätthåller ett stabilt verkställande oavsett antal uppkopplade användare.
+Att spela spel över internet är en del av vår kultur som antagligen aldrig kommer försvinna. Det är ett sätt att umgås och samarbeta, ofta med människor man aldrig har mött. 
+På många platser i världen är gigantiska servrar igång dygnet runt för att hantera förfrågningar från miljontals användare, och tusentals programmerare gör sitt bästa för 
+att ge människor en så bra användarupplevelse som möjligt. 
+För att detta ska vara möjligt krävs mycket av serverprogrammen. 
+Servrarna ska kunna hantera många förfrågningar med låg fördröjning, samtidigt som de måste koordinera händelser så att det som en användare gör också ska påverka dem i anslutning till den. 
+Serverprogrammen ska också gärna vara finkornigt modulariserade för att möjliggöra parallellutveklingen av serverprogrammen på ett fungerande sätt.
 
-Vi beslutade att kalla spelet Lost Vaults, ett semi-traditionellt MUD där användaren interagerar med andra spelare och tar del i uppdrag. Detta sker i grupper av flertal spelare som 
-tillsammans arbetar mot ett gemensamt mål samtidigt som varje enskild gruppmedlem har en personlig agenda som endast gagnar den enskilda invididen. Möjligheten finns att utforska som 
-enskild individ, men fokuset för spelet ligger i den dynamik som följer av interaktionen med andra spelare. Spelet utspelas på två olika platser, i City och i Dungeon; där City är 
-staden där spelarna samlas efter tidigare utforskningar, kan fylla på förnödenheter samt forma grupper för att gå ner i Dungeons. Dungeons är en procedurellt genererad uppsättning 
-rum fyllt med monster, fällor och skatter. Varje grupp spelare får alltså sin egen unikt genererade Dungeon när gruppen går ner i dessa magiska grottor under staden. Väl inne ges 
-gruppen en eller flera uppdrag som bör fullbordas under upptäcksfärden.
+Vi kände att komplexiteten av att göra ett multiplayer onlinespel var något som utmanade och intresserade oss, då det gav upphov till intressanta problem som kunde lösas med hjälp av concurrency. 
+Vi har skapat ett serverbaserat spel, som kommunicerar med användaren via en TCP/IP uppkoppling till användarens klient-program. Servern består av flera självständiga aktörer som interagerar
+genom att skicka meddelanden fram och tillbaka. Detta ger oss ett bekvämt sätt att skriva fungerande spellogik, utan att behöva bry oss om att låsa delad data.
 
-Som beskrivet nedan i delen om speldesign, finns det två typer av uppdrag: grupp- och spelaruppdrag. Gruppuppdrag gagnar alla spelare i gruppen medan spelaruppdragen gynnar den enskilde. 
-Vårt mål var att skapa en atmosfär där spelare behöver lita på varandra för att fullborda de svårare gruppuppdragen, fast samtidigt vara misstänksamma mot varandra då vem som helst kan 
-förråda gruppen för att färdigställa sina personliga uppdrag.
-
-Den slutgiltiga produkten för detta projekt är ett fullt funktionellt och interaktivt multiplayer online role playing game kallat Lost Vaults.
+Spelet kallas \textit{The Lost Vaults - Uneasy Alliance} och är ett semi-traditionellt MUD där användaren interagerar med andra spelare och tar del i uppdrag. 
+Detta sker i grupper av flertal spelare som tillsammans arbetar mot ett gemensamt mål samtidigt som varje enskild gruppmedlem har en personlig agenda som endast 
+gagnar den enskilda invididen. Möjligheten finns att utforska som enskild individ, men fokuset för spelet ligger i den dynamik som följer av 
+interaktionen med andra spelare. Spelet utspelas på två olika platser, i City och i Dungeon; där City är staden där spelarna samlas efter tidigare utforskningar, 
+kan fylla på förnödenheter samt forma grupper för att gå ner i Dungeons. Dungeons är en procedurellt genererad uppsättning rum fyllt med monster, fällor och skatter. 
+Varje grupp spelare får alltså sin egen unikt genererade Dungeon när gruppen går ner i dessa magiska grottor under staden. Väl inne ges 
+gruppen en eller flera uppdrag som bör fullbordas innan de kommer upp till ytan igen.
 

### 2014-05-26 doc/src/draft.tex
Added some more text for the final draf in the section 'Systemarkitektur'

--- 2014-05-23 doc/src/draft.tex
@@
 
-\section{System architecture}
+\section{Systemarkitektur}
 \subsection{Design}
-Systemarkitekturen som återfinns i detta dokument är uppdelat i Client-side arkitektur och Server-side arkitektur. Applikation, skriven i Scala, körs i Java Virtual Machine och på 
-grund av detta kan både klient och server köras på alla plattformar som stödjer Java VM 1.7.
+Systemarkitekturen som beskrivs i detta dokument är uppdelat i två delar vilka beskriver akritekturen för klienten samt servern.
+Med tanke på att både klienten och servern är skrivna i Scala och körs via Java Virtual Maschine både servern och klienten kan köras på alla plattformar som stödjer Java VM 1.7.
 
-****** figur 1****
+****** figur 1 ****
 
-\subsection{Client side}
-Målet med designen för klienten till Lost Vaults var att ta fram något som kunde efterliknas med en indirekt terminal, där ingen logik används förutom att skicka förfrågningar och 
-motta samt tolka svaren på förfrågningar. I slutänden hoppas vi kunna åstadkomma en client-side implementation som lätt kan utökas när serverns implementation av spelets logik ökar, 
-alltså ett system som kan utkökas enkelt endast genom att addera nya förfrågningar och svar.
+\subsection{Klient}
+Designen för klienten till Lost Vaults är utvecklad för att efterlikna en indirekt terminal, där ingen logik används förutom att skicka förfrågningar och 
+ta emot samt tolka svaren på förfrågningar.
+Konceptet för en indirekt terminal valdes för att kunna åstadkomma en implementation hos klienten som lätt kan utökas när serverns implementation av spelets logik ökar.
+Detta betyder med andra ord ett system som kan utkökas enkelt endast genom att addera nya förfrågningar och svar.
 
-Som synes i Figur 1 är klientfönstret uppdelat i flera textfält som visar relevant information för spelaren. Huvudområdet är för vanliga server-svar och kommer innehålla beskrivningar 
+Som Figur 1 illustrerar är klientfönstret uppdelat i flera textfält som visar relevant information för spelaren. Huvudområdet är för vanliga server-svar och kommer innehålla beskrivningar 
 av rummet, meddelanden i spelarchatten, meddelanden med systeminformation och liknande. Klientens högra sida är reserverat för ständig information som spelaren behöver ta del av snabbt. 
@@
 Den nedre delen av fönstret innehåller kommandoraden, där spelaren skriver in kommandon i enlighet med ett strikt syntax. När klienten startas välkomnas spelaren 
-av ett centrerat fönster för inloggning . Här kan spelaren skriva in sitt användarnamn och lösenord samt IP:n till den server som spelaren vill koppla upp sig mot.
+av ett centrerat fönster för inloggning. Här kan spelaren skriva in sitt användarnamn och lösenord samt IP:n tillhörande den server som spelaren vill koppla upp sig mot.
 
@@
 
-\subsection{Server side}
-Systemarkitekturens serverdel är uppdelad i sektionerna Concurrency Model, Actor Model och Class Model. Den första delen beskriver vårt 
-val av concurrencymodell, och anledningen till valet. Den andra delen beskriver funktionen hos de fem stora actor-typer i Lost Vaults servern och 
-den tredje ger en ingående beskrivning hur klassförhållanden används av servern.
+\subsection{Server}
+Systemarkitekturens serverdel är uppdelad i sektionerna Concurrency-modell, Actor-modell och Class-modell. Den första delen beskriver vårt 
+val av concurrencymodell samt anledningen till det specifika valet. Den andra delen, Actor-modell, beskriver funktionen hos de fem stora actor-typer i Lost Vaults servern och 
+den tredje, klass-modell, ger en ingående beskrivning hur klassförhållanden används i servern.
 
@@
 
-För att implementera denna sortens system och bibehålla hög effektivitet valde vi Scala som programspråk till servern av den enkla anledningen att 
-skalbarheten är ett av språkets fundamentala mål. Genom rekommendationer av skaparna bakom Scala och via språkets styrkor och enkelhet, beslöt vi 
+För att implementera denna sortens system och bibehålla hög effektivitet valde vi Scala som programspråk till servern och detta passade otroligt bra då skalbarhet är ett av språkets fundamentala mål.
+Genom rekommendationer av skaparna bakom Scala och via språkets styrkor och enkelhet, beslöt vi oss för
 att använda Akka som vårt aktörbibliotek. Detta för att kunna använda Akkas TCP-bibliotek för nätverkskommunikationen. Bibliotekets enkla integration 
-ledde till vårt beslut att använda Scala och Akka som val av programspråk och aktörbibliotek även för klienten, som tidigare nämnts.
+var en av punkterna som ledde till vårt beslut att använda Scala och Akka som val av programspråk och aktörbibliotek även för klienten.
 
@@
 \subsubsection{Actor model}
-Serverdelen är uppdelad i flera processer via Akkas aktörbibliotek för att upprätthålla Actor Concurrency Model i enlighet med Figur 3. Bara två typer av aktörer kommmunicerar 
-direkt med nätverket via TCP/IP, Connection Manager-aktören och Player-aktörerna. Connection Manager- aktören har som syfte att hantera inkommande uppkopplingar samt ansvarar 
+Serverdelen är uppdelad i flera processer via Akkas aktörbibliotek för att upprätthålla Actor Concurrency-modellen i enlighet med Figur 3. Endast två typer av aktörer kommmunicerar 
+direkt med nätverket via TCP/IP, Connection Manager-aktören och Player-aktörerna. Connection Manager-aktören har som syfte att hantera inkommande uppkopplingar samt ansvarar 
 för att skapa Player-aktörer som nya högnivå aktörer innan de registreras som den nyetablerade uppkopplingens lyssnare. Som lyssnare kommer Player-aktören mottaga och skicka data 
@@
 GroupMap-aktören fyller en liknande funktion som PlayerMap, men länkar istället namnen på spelarna med spelargrupper istället för spelaraktörer. 
-En spelargrupp är en samling av en eller fler spelare som tillsammans kan gå ner i en Dungeon som är procedurellt genererad för just dem. Syftet med 
+En spelargrupp är en samling av en eller fler spelare som tillsammans kan gå ner i en Dungeon, som är procedurellt genererad för just dem. Syftet med 
 denna aktör är att underlätta skapandet och att ansluta sig till andra spelargrupper. Genom att använda GroupMap räcker det att ansluta sig till en 
@@
 
-Den fjärde sortens aktör som servern använder är Dungeon-aktören, den som utför spelets logik. 
+Den fjärde sortens aktör som servern använder är Dungeon-aktören och det denna som utför spelets logik. 
 Det existerar ett speciellt tillstånd av Dungeon-aktören, kallat City- aktören. City existerar ständigt 
 under serverns livstid och hanterar spelets sociala aspekt, såsom chattande och skapandet av grupper. 
-Det ordinära fallet som Dungeon-aktören ansvarar för är genererandet och hanterandet av den procedurella 
-grottan av multipla, sammanlänkade rum i ett tvådimensionellt rutnät. Det är i dessa rum som spelare kommer kunna göra uppdrag, 
-finna skatter etc. Dungeon-aktören ansvarar för koordinerandet av alla spelare som finns i grottan. 
+Det som Dungeon-aktören ansvarar för är genererandet och hanterandet av den procedurellt skapade 
+grotta som består av multipla och sammanlänkade rum i ett tvådimensionellt rutnät. Det är i dessa rum som spelare kommer kunna göra uppdrag, 
+finna skatter, slåss mot monster eller spelare etc. Dungeon-aktören ansvarar även för koordinationen av alla spelare som finns i grottan. 
 Ett exempel på detta är kommandot “SAY”  som ska skickas till relevanta spelare.
 
-Efter att City-aktören har skapat Dungeon-aktören ansvarar den för sin egen livslängd och avsutar sig själv endast när det inte längre finns några spelare i den.
+Efter att City-aktören har skapat Dungeon-aktören ansvarar den för sin egen livslängd och avslutar sig själv endast när det inte längre finns några spelare i den.
 
@@
 Detta då vi anser att det i särklass är det enklaste sättet att utveckla kod till Java eller Scala. Även fast all kod är skriven i Eclipse använder vi Ant Build System 
-för automatiserad kompilering samt byggandet av vår klient och server, klar att köras i Java Virtual Machine.
+för automatiserad kompilering samt vid byggandet av vår klient och server; som efter kompilering är klar att köras i Java Virtual Machine.
 
@@
 Sammansättningen av dokumentationen utförs med Scaladoc på grund av dess likhet med JavaDoc, ett verktyg vi är vana med att använda, och Ant har reviderats för att automatiskt 
-bygga vår dokumentation.
+bygga dokumentationen.
 

### 2014-05-26 doc/src/draft.tex
Skrev på programmeringsspråk och slutsats

@@
 \subsubsection{Class model}
-Klienten är strukturerad i fyra olika distinkta klasser som beskrivs i Figur 2. Klasserna PlayGame och PlayGameCommunication arbetar 
+Klienten är strukturerad i fyra distinkta klasser som beskrivs i Figur 2. Klasserna PlayGame och PlayGameCommunication arbetar 
 tillsammans för att skapa en brygga mellan TCP lagret och GUI:t, där PlayGame accepterar meddelanden från TCPClient och skickar dem 
@@
 \subsection{Server}
-Systemarkitekturens serverdel är uppdelad i sektionerna Concurrency-modell, Actor-modell och Class-modell. Den första delen beskriver vårt 
+Systemarkitekturens serverdel är uppdelad i sektionerna  Actor-modell och Class-modell. Den första delen beskriver vårt 
 val av concurrencymodell samt anledningen till det specifika valet. Den andra delen, Actor-modell, beskriver funktionen hos de fem stora actor-typer i Lost Vaults servern och 
 den tredje, klass-modell, ger en ingående beskrivning hur klassförhållanden används i servern.
-
-\subsubsection{Concurrency model}
-Actor modellen har använts för projektet då vi under vår initiala diskussion gällande designen lyckades isolera beteenden i mindre och till stor del 
-fristående sektioner. Dessa sektioner kunde enkelt skapas för att dela data enbart genom meddelandesändning som i sin tur leder till att problem 
-såsom deadlock kunde undvikas.
-
-För att implementera denna sortens system och bibehålla hög effektivitet valde vi Scala som programspråk till servern och detta passade otroligt bra då skalbarhet är ett av språkets fundamentala mål.
-Genom rekommendationer av skaparna bakom Scala och via språkets styrkor och enkelhet, beslöt vi oss för
-att använda Akka som vårt aktörbibliotek. Detta för att kunna använda Akkas TCP-bibliotek för nätverkskommunikationen. Bibliotekets enkla integration 
-var en av punkterna som ledde till vårt beslut att använda Scala och Akka som val av programspråk och aktörbibliotek även för klienten.
 
@@
 \subsection{Programspråk}
+För att möjliggöra massiv concurrency med många individuella aktörer har vi gjort vårt projekt i Scala.
+Scala är bra för skalbarhet, vilket innebär att vårt program kommer fungera bra oavsätt om det är tio användare online eller om det är tio tusen.
+En annan anledning till att vi valde Scala är att Scala är ett objektorienterat språk, vilket passade nära med det tänket vi hade när vi skapade programmet.
+Vi fokuserade på att skapa objekt som interagereade på rätt sätt med varandra, snarare än att skriva kod som ska exekveras i en särskild ordning.
+
+Scala bygger på Java, och erbjuder därför liknande syntax.
+Detta innebar att övergången mellan att skriva Java och Scala var en någorlunda mjuk sådan, koden var ganska lättigenkännlig samtidigt som vi fick fördelarna med att kunna utveckla skalbart.
+Några nackdelar med Scala som vi finner nämnvärda är exempelvis att det, trots likheter med Java, tog en viss tid att sätta sig in i det nya
+språket vilket kan ha motarbetat utvecklingen gämfört med om vi hade valt ett annat språk som vi var mer bekanta med.
+
+Genom rekommendationer av skaparna bakom Scala och via språkets styrkor och enkelhet, beslöt vi oss för 
+att använda Akka som vårt aktörbibliotek.
+Detta för att kunna använda Akkas TCP-bibliotek för nätverkskommunikationen.
+Bibliotekets enkla integration var en av punkterna som ledde till vårt beslut att använda Scala och Akka som val av programspråk och aktörbibliotek.
+
 Java var det språket vi valde att använda vid skapandet av det grafiska gränssnittet som spelaren agerar mot. Vårt val grundade sig i biblioteket Swing som Java tillhandahåller. 
@@
 på ett enkelt sätt och detta kunde uppnås utan problem då Scala är byggt utifrån Javas Virtuella Maskin.
-
-Anledningen till att vi skrev inte skrev hela projektet i Java var på grund av den bristande skalbarheten som språket besitter. Scala däremot erbjöd båda en liknande syntax som 
-Java och hade samtidigt bättre skalbarhet. Detta innebar att övergången mellan att skriva Java och Scala var en någorlunda mjuk sådan, koden var ganska lättigenkännlig och systemet 
-kunde utvecklas med skalbarhet i åtanke. Några nackdelar med Scala som vi finner nämnvärda är exempelvis att det, trots likheter med Java, tog en viss tid att sätta sig in i det nya 
-språket vilket kan ha motarbetat utvecklingen mot om vi hade valt ett annat språk som vi var mer bekanta med. Det är viktigt att inte glömma att de nackdelar vi funnit under 
-projektets gång skuggas av fördelarna vi funnit med språket.
 
@@
 Flera spelare samtidigt
+Skicka meddelanden - jobbigt när man bara vill ta reda på ett värde - skicka meddelanden fram och tillbaka. Men ingen risk för deadlock då all kommunikation sker via meddelanden. 
+Meddelanden är ej synkrona, vilket märks då en spelare ibland kan bli slagen efter att den har dött (det ser uut så i prompten eftersom meddelandena kommer så, men det är inte sant)
+För att skapa en slags synkronisering har vi använt FSM, vilket kräver att man är i en särskild state för att kunna ta emot ett särskilt meddelanden.
 
 \section{Slutsatser}
+Vårt slutresultat är ett textbaserat multiplayer dungeon spel.
+I spelets startrum kan man chatta med de andra spelarna som är online genom whisper (personligt meddelande) eller say (till alla spelare i rummet).
+Där kan man också forma en grupp så att man tillsammans med andra spelare kan gå ner i en dungeon och börja spela.
+Väl nere i en dungeon kan man chatta som vanligt, men man kan också plocka upp saker som man hittar i grottan, börja slåss mot en spelare eller NPC som är i rummet och man kan gå till andra rum.
+När detta sker uppdateras klienten på korrekt sätt, så att spelaren får information om vad som händer i grottan.
+Vi har också skapat en \textit{god mode} som gör att man i terminalen kan ge spelare speciella items, samt hela den så att den får fullt hp.
+Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla salarna.
+
 Något vi gjorde bra var att vi gjorde klart det essentiella för huvudmålet med projektet, att uppnå concurrency på något sätt.
+Spelet hanterar många individuella aktörer, och klarar av att hantera massiva uppkopplingar mot dess server.
 Då den delen av projektet var klart kunde vi utöka produkten med funktioner för att göra spelet roligare och mer interaktivt. 
@@
 och samtidigt ha det tillräckligt intressant för den som spelar.
+
+En stor sak som vi inte han med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa stek skulle vara, nu när det grundläggande fungerar som det ska.
 

### 2014-05-26 doc/src/draft.tex
Current Version + figures

--- 2014-05-26 doc/src/draft.tex
@@
 \usepackage[T1]{fontenc}
+\usepackage{algpseudocode}
+\usepackage{algorithm}
 \usepackage{lmodern}
@@
 
+%Döp om pseudokod.
+\floatname{algorithm}{Algoritm}
+\renewcommand{\algorithmicindent}{4 pt}
 \begin{document}
@@
 
-****** figur 1 ****
+\begin{figure}[hbt]
+\centering
+\includegraphics[width=1.0\textwidth]{client}
+\caption{\label{fig:Client}Klientens användargränssnitt.}
+\end{figure}
 
@@
 
-**Figur 2**
+\begin{figure}[hbt]
+\centering
+\includegraphics[width=1.0\textwidth]{clientuml1}
+\caption{\label{fig:ClientArch}Klientens klassmodell.}
+\end{figure}
 
-\subsubsection{Class model}
+\subsubsection{Klassmodell}
 Klienten är strukturerad i fyra olika distinkta klasser som beskrivs i Figur 2. Klasserna PlayGame och PlayGameCommunication arbetar 
@@
 
-\subsubsection{Concurrency model}
+\subsubsection{Concurrencymodell}
 Actor modellen har använts för projektet då vi under vår initiala diskussion gällande designen lyckades isolera beteenden i mindre och till stor del 
@@
 
-**Figur 3**
+\begin{figure}[hbt]
+\centering
+\includegraphics[width=1.0\textwidth]{serverActorModel2-1}
+\caption{\label{fig:ConManPlayer}Figur över förhållandet mellan ConMan och Player.}
+\end{figure}
+\subsection{Server-side}
 
-\subsubsection{Actor model}
+\subsubsection{Aktörmodell}
 Serverdelen är uppdelad i flera processer via Akkas aktörbibliotek för att upprätthålla Actor Concurrency-modellen i enlighet med Figur 3. Endast två typer av aktörer kommmunicerar 
@@
 sig om att det inte existerar flera spelare med samma namn på servern.
+
+\begin{figure}[hbt]
+\centering
+\includegraphics[width=1.0\textwidth]{serverActorModel2-2}
+\caption{\label{fig:ServerActorModel}Modell över de olika aktörernas sammanhang.}
+\end{figure}
 
@@
 
-Efter att City-aktören har skapat Dungeon-aktören ansvarar den för sin egen livslängd och avslutar sig själv endast när det inte längre finns några spelare i den.
+Efter att City-aktören har skapat Dungeon-aktören ansvarar den nya aktören för sin egen livslängd och avsutar sig själv endast när det inte längre finns några spelare i den.
 
-**Figur 4**
+\begin{figure}[hbt]
+\centering
+\includegraphics[width=1.0\textwidth]{serverActorModel2-2}
+\caption{\label{fig:ServerKlassModell}Modell över serverns klassstruktur}
+\end{figure}
 
-\subsubsection{Class model}
-Figur 4 visar relationen mellan de olika klasserna i implementation av servern och dess multiplicitet av relevanta förhållanden. 
-De är uppdelade i tre kategorier; Utility Layer, Network Communicators och Game Logic. 
-Utility Layer tillhandahåller understödjande funktionalitet till de andra klasserna och exakt en av varje klass ska existera vid en given punkt. 
-Network Communicators är de som relaterar tillbaka till nätverket genom Akkas TCP bibliotek. Connection manager klassen, ConMan, hanteras som en singleton och endast en 
-instans av denna ska existera vid en given tidpunkt. Player-klassen har emellertid en instans för varje öppen uppkoppling.
+\subsubsection{Klassmodell}
+Figur \ref{fig:ServerKlassModell} visar de olika klasserna i serverimplementationen.
+De är uppdelade i fyra lager; Verktygslagret, Anslutningslagret, Spelarlagret och Dungeonlagret. Indelningen i dessa lager följer till stor del
+den indelning som gjorts i vilka klasser är sina egna aktörer. Undantaget till detta är verktygslagret, där klasserna PlayerMap, GroupMap och CheatActor är sina egna aktörer.
+Med undantag av RoomGenerator och RoomDescGenerator är alla klasser i Verktygslagret Singletons. Lagret tillhandahåller  understödjande funktionalitet till de andra klasserna.
+Anslutningslagret är ingångspunkten till servern över nätverket genom Akkas TCP bibliotek. Vår anslutningshanterare, ConMan, agerar som en singleton och endast en 
+instans av denna ska existera vid en given tidpunkt. ConMan är den klass som lystnar efter och godtar anslutningar från klienter, samt skapar nya Player-instanser vid nyupprättad anslutning.
 
-Game Logic delen innehåller alla interna klasser och där också Dungeon-klassen. Dungeon-klassen är bryggan mellan Network 
-Communicators och Game Logic och det är endast via en Dungeon-klass som en Player kan utföra någon handling förutom WHISPER kommandot, 
-då detta meddelande är över hela servern. Dungeon-klassen håller koll på utforskade och outforskade rum, uppdrag, grupper, object och NPCs. 
-Dungeon håller även koll på de Players som för tillfället är uppkopplade och associerade med en given Dungeon.
+Dungeonlagret innehåller de klasser som är viktiga för spelets logiska funktioner. Lagret innehåller dungeonklassen, som ansvarar över en mängd slumpmässigt genererade rum, som i sin tur
+ansvarar för aktiva strider samt icke-spelar karaktärer och objekt.
 
@@
 \subsection{Algoritmer}
+För att spelarna alltid skall få  nya och intressanta upplevelser bestämde vi oss för att skriva en algoritm för slumpmässig generering av rum som spelarna kan utforska. Vi
+bestämde oss för att nyttja ett rutnät där varje cell representerar ett rum. Spelare kan ta sig från rum till rum via utgångar placerade på några av eller alla rummens fyra väggar.
+Vår algoritm skall även säkerställa att inga rum skapas som inte går att nå från ingången. Nedan beskrivs med pseudokod den algoritm vi bestämde oss för att använda.
+\begin{algorithm}
+\caption{Procedurell Rumsgenerering.}
+\label{alg:RoomGen}
+\begin{algorithmic}[1]
+\Function{generateRooms}{Bredd, Höjd}
+\State  $Rooms$ = Array[Bredd * Höjd]
+\State  $StartRoom$ = slumpmässig cell i $Rooms$
+\State  $CreatedRooms$ = $0$
+\State  $GoalRooms$ = önskat antal skapade rum
+\Repeat
+\State $ToConnect$ = List()
+\State $NextRoom$  =  Slumpat rum $x$ ur $Rooms$ där $x.created = false$
+\State $NextRoom.created$ = $true$
+\State $ToConnect.Insert NextRoom$
+\While{$NextRoom.connected \neq true$}
+\State Välj en slumpmässig riktning, viktad mot $StartRoom$
+\State $NextRoom$ = den cell i $Rooms$ som är ett steg i vald riktning
+\If {$NextRoom.created = true$ och $NextRoom.connected \neq true$}
+\If {Andra riktningar har inte prövats}
+\State Välj ny riktning och börja om från $13$
+\ElsIf{Alla riktningar har misslyckats}
+\State Gå tillbaka ett rum ur $ToConnect$ och börja om från $12$
+\If{Alla möjliga riktningar prövats i alla rum ur $ToConnect$}
+\State Börja om från $7$
+\EndIf
+\EndIf
+\ElsIf{$NextRoom.created = false$}
+\State Lägg $NextRoom$ först i $ToConnect$
+\EndIf
+\EndWhile
+\While{$|ToConnect|$}
+\State Anslut $NextRoom$ med $ToConnect$
+\State Sätt $NextRoom.connected = true$
+\State Plocka ut $head$ från $ToConnect$ och tilldela den till $NextRoom$
+\State Öka $CreatedRooms$ med $1$
+\EndWhile
+\Until{$CreatedRooms \geq GoalRooms$}
+\EndFunction
+\end{algorithmic}
+
+\end{algorithm}
 

### 2014-05-26 doc/src/draft.tex

--- 2014-05-26 doc/src/draft.tex
@@
 Med tanke på att både klienten och servern är skrivna i Scala och körs via Java Virtual Maschine både servern och klienten kan köras på alla plattformar som stödjer Java VM 1.7.
-
-****** figur 1 ****
+\begin{figure}[hbt]
+\centering
+\includegraphics[width=1.0\textwidth]{client}
+\caption{\label{fig:Client}Klientens användargränssnitt.}
+\end{figure}
 
@@
 
-**Figur 2**
+\begin{figure}[hbt]
+\centering
+\includegraphics[width=1.0\textwidth]{clientuml1}
+\caption{\label{fig:ClientArch}Klientens klassmodell.}
+\end{figure}
 
-\subsubsection{Class model}
-Klienten är strukturerad i fyra distinkta klasser som beskrivs i Figur 2. Klasserna PlayGame och PlayGameCommunication arbetar 
+\subsubsection{Klassmodell}
+Klienten är strukturerad i fyra distinkta klasser som beskrivs i Figur \ref{fig:ClientArch}. Klasserna PlayGame och PlayGameCommunication arbetar 
 tillsammans för att skapa en brygga mellan TCP lagret och GUI:t, där PlayGame accepterar meddelanden från TCPClient och skickar dem 
@@
 \subsection{Server}
-Systemarkitekturens serverdel är uppdelad i sektionerna  Actor-modell och Class-modell. Den första delen beskriver vårt 
+Systemarkitekturens serverdel är uppdelad i sektionerna Concurrency-modell, Actor-modell och Class-modell. Den första delen beskriver vårt 
 val av concurrencymodell samt anledningen till det specifika valet. Den andra delen, Actor-modell, beskriver funktionen hos de fem stora actor-typer i Lost Vaults servern och 
@@
 
-**Figur 3**
+\begin{figure}[hbt]
+\centering
+\includegraphics[width=1.0\textwidth]{serverActorModel2-1}
+\caption{\label{fig:ConManPlayer}Figur över förhållandet mellan ConMan och Player.}
+\end{figure}
+\subsection{Server-side}
 
-\subsubsection{Actor model}
-Serverdelen är uppdelad i flera processer via Akkas aktörbibliotek för att upprätthålla Actor Concurrency-modellen i enlighet med Figur 3. Endast två typer av aktörer kommmunicerar 
-direkt med nätverket via TCP/IP, Connection Manager-aktören och Player-aktörerna. Connection Manager-aktören har som syfte att hantera inkommande uppkopplingar samt ansvarar 
-för att skapa Player-aktörer som nya högnivå aktörer innan de registreras som den nyetablerade uppkopplingens lyssnare. Som lyssnare kommer Player-aktören mottaga och skicka data 
-över nätverket genom den etablerade uppkopplingen. Player-aktören styr över alla ting relaterat till klienten, som exempelvis spelarens attribut och för att verifiera 
-inloggningsförsök via kommunikation med PlayerMap. Det är även via Player-aktören andra aktörer kan skicka meddelanden över nätverket om det skulle behövas.
+\subsubsection{Aktörmodell}
+Serverdelen är uppdelad i flera processer via Akkas aktörbibliotek för att upprätthålla Actor Concurrency-modellen i enlighet med Figur \ref{fig:ConManPlayer} och Figur \ref{fig:ServerActorModel}. 
+Endast två typer av aktörer kommmunicerar direkt med nätverket via TCP/IP, ConManaktören och Playeraktörerna. ConManaktören har som syfte att hantera inkommande anslutningar samt ansvarar 
+för att skapa Playeraktörer som nya högnivå aktörer innan de registreras som den nyetablerade anslutningens lyssnare. Som lyssnare kommer Playeraktören ta emot och skicka data 
+över nätverket. Playeraktören styr över alla attribut relaterade till sin klient, som exempelvis spelarens attribut och för att verifiera 
+inloggningsförsök via kommunikation med PlayerMap och en databas innehållande inloggningsinformation. Det är även via Playeraktören andra aktörer kan skicka meddelanden över nätverket vid behov.
 
-PlayerMap-aktören och Groupmap-aktören fyller två specifika funktioner. PlayerMap mappar en sträng, namnet på den uppkopplade spelare, till aktören som kontrollerar 
-spelaren med det specifika namnet. Genom denna aktör kan en annan aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - 
-ett viktigt kommando som agerar på följande sätt är exempelvis “WHISPER”. PlayerMap möjliggör även ett snabbt och enkelt sätt för Player-aktören att försäkra 
+PlayerMapaktören och GroupMapaktören fyller två specifika och snarlika funktioner. PlayerMap mappar en sträng, namnet på en uppkopplad spelare, till den aktör som kontrollerar 
+spelaren med det eftersökta namnet. Genom denna aktör kan en annan aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - 
+ett viktigt kommando som agerar på följande sätt är exempelvis “WHISPER”. PlayerMap möjliggör även ett snabbt och enkelt sätt för Playeraktören att försäkra 
 sig om att det inte existerar flera spelare med samma namn på servern.
 
-GroupMap-aktören fyller en liknande funktion som PlayerMap, men länkar istället namnen på spelarna med spelargrupper istället för spelaraktörer. 
+\begin{figure}[hbt]
+\centering
+\includegraphics[width=1.0\textwidth]{serverActorModel2-2}
+\caption{\label{fig:ServerActorModel}Modell över de olika aktörernas sammanhang.}
+\end{figure}
+
+GroupMapaktören fyller en liknande funktion som PlayerMap, men länkar istället namnen på spelarna med spelargrupper istället för spelaraktörer. 
 En spelargrupp är en samling av en eller fler spelare som tillsammans kan gå ner i en Dungeon, som är procedurellt genererad för just dem. Syftet med 
-denna aktör är att underlätta skapandet och att ansluta sig till andra spelargrupper. Genom att använda GroupMap räcker det att ansluta sig till en 
+denna aktör är att underlätta skapandet av spelargrupper samt anslutning till redan existerande spelargrupper. Genom att använda GroupMap räcker det att ansluta sig till en 
 spelare via dess namn för att inkluderas i denna spelares grupp, eller för att skapa en ny grupp med denna spelare.
 
-Den fjärde sortens aktör som servern använder är Dungeon-aktören och det denna som utför spelets logik. 
-Det existerar ett speciellt tillstånd av Dungeon-aktören, kallat City- aktören. City existerar ständigt 
+De två resterande lagren av aktörer som servern använder är Dungeonlagret och Stridslagret, och det är dessa som utför spelets logik. 
+Det existerar ett speciellt tillstånd av Dungeonaktören, kallat Cityaktören. City existerar ständigt 
 under serverns livstid och hanterar spelets sociala aspekt, såsom chattande och skapandet av grupper. 
-Det som Dungeon-aktören ansvarar för är genererandet och hanterandet av den procedurellt skapade 
+Det som Dungeonaktören ansvarar för är genererandet och hanterandet av den procedurellt skapade 
 grotta som består av multipla och sammanlänkade rum i ett tvådimensionellt rutnät. Det är i dessa rum som spelare kommer kunna göra uppdrag, 
-finna skatter, slåss mot monster eller spelare etc. Dungeon-aktören ansvarar även för koordinationen av alla spelare som finns i grottan. 
+finna skatter, slåss mot monster eller spelare etc. Dungeonaktören ansvarar även för koordinationen av alla spelare som finns i grottan. 
 Ett exempel på detta är kommandot “SAY”  som ska skickas till relevanta spelare. 
+Strider koordineras av sin egna aktör, en finit tillståndsmaskin kallad Combat, som sköter turordning av spelare och monster vid strid. Varje rum i en Dungeon kan innehålla en
+referens till en Combat, vilket leder till att det som max kan vara upp till en combat aktiv per rum. Combataktören skapas då spelare går i strid mot monster eller andra spelare
+och terminerar när det inte längre finns någon som anfaller någon annan.
 
-Efter att City-aktören har skapat Dungeon-aktören ansvarar den för sin egen livslängd och avslutar sig själv endast när det inte längre finns några spelare i den.
+Efter att Cityaktören har skapat en Dungeonaktör ansvarar den nya aktören för sin egen livslängd och avsutar sig själv endast när det inte längre finns några spelare i den.
 
-**Figur 4**
+\begin{figure}[hbt]
+\centering
+\includegraphics[width=1.0\textwidth]{serverUml2}
+\caption{\label{fig:ServerKlassModell}Modell över serverns klassstruktur}
+\end{figure}
 
-\subsubsection{Class model}
-Figur 4 visar relationen mellan de olika klasserna i implementation av servern och dess multiplicitet av relevanta förhållanden. 
-De är uppdelade i tre kategorier; Utility Layer, Network Communicators och Game Logic. 
-Utility Layer tillhandahåller understödjande funktionalitet till de andra klasserna och exakt en av varje klass ska existera vid en given punkt. 
-Network Communicators är de som relaterar tillbaka till nätverket genom Akkas TCP bibliotek. Connection manager klassen, ConMan, hanteras som en singleton och endast en 
-instans av denna ska existera vid en given tidpunkt. Player-klassen har emellertid en instans för varje öppen uppkoppling.
+\subsubsection{Klassmodell}
+Figur \ref{fig:ServerKlassModell} visar de olika klasserna i serverimplementationen.
+De är uppdelade i fyra lager; Verktygslagret, Anslutningslagret, Spelarlagret och Dungeonlagret. Indelningen i dessa lager följer till stor del
+den indelning som gjorts i vilka klasser är sina egna aktörer. Undantagen till detta är verktygslagret, där klasserna PlayerMap, GroupMap och CheatActor är sina egna aktörer samt 
+Combat klassen som i denna figur flyttats från sitt egna lager (se figur \ref{fig:ServerActorModel}) för att visa dess täta koppling med Room klassen.
 
-Game Logic delen innehåller alla interna klasser och där också Dungeon-klassen. Dungeon-klassen är bryggan mellan Network 
-Communicators och Game Logic och det är endast via en Dungeon-klass som en Player kan utföra någon handling förutom WHISPER kommandot, 
-då detta meddelande är över hela servern. Dungeon-klassen håller koll på utforskade och outforskade rum, uppdrag, grupper, object och NPCs. 
-Dungeon håller även koll på de Players som för tillfället är uppkopplade och associerade med en given Dungeon.
+Bortsett från RoomGenerator och RoomDescGenerator är alla klasser i Verktygslagret Singletons. Lagret tillhandahåller  understödjande funktionalitet till de andra klasserna.
+Anslutningslagret är ingångspunkten till servern över nätverket genom Akkas TCP bibliotek. Vår anslutningshanterare, ConMan, agerar som en singleton och endast en 
+instans av denna ska existera vid en given tidpunkt. ConMan är den klass som lystnar efter och godtar anslutningar från klienter, samt skapar nya Player-instanser vid nyupprättad anslutning.
+
+Dungeonlagret innehåller de klasser som är viktiga för spelets logiska funktioner. Lagret innehåller dungeonklassen, som ansvarar över en mängd slumpmässigt genererade rum, som i sin tur
+ansvarar för aktiva strider samt icke-spelarkaraktärer och objekt. Tidigare design visar att Item klassen används som superklass till olika typer av objekt. Vi valde dock att platta till 
+vår klasshierarki och förenkla designen genom att låta alla typer av objekt vara instanser av Item klassen med olika attribut. På samma sätt valde vi att göra oss av med distinktionen mellan
+goda och onda icke-spelarkaraktärer, och har istället valt att implementera enbart monster.
 

### 2014-05-26 doc/src/draft.tex
Latest Draft

@@
 \maketitle
+\thispagestyle{empty}
 \newpage
+\setcounter{page}{1}
+\pagenumbering{Roman}
 \tableofcontents
@@
 \newpage
+\setcounter{page}{1}
+\pagenumbering{arabic}
 \section{Inledning}
@@
 \subsection{Server}
-Systemarkitekturens serverdel är uppdelad i sektionerna Concurrency-modell, Actor-modell och Class-modell. Den första delen beskriver vårt 
-val av concurrencymodell samt anledningen till det specifika valet. Den andra delen, Actor-modell, beskriver funktionen hos de fem stora actor-typer i Lost Vaults servern och 
-den tredje, klass-modell, ger en ingående beskrivning hur klassförhållanden används i servern.
+Systemarkitekturens serverdel är uppdelad i sektionerna Aktörmodell och Klassmodell. Den första delen beskriver funktionen hos de olika aktörlagren i Lost Vaults servern och 
+den andra ger en  beskrivning av serverns klassförhållanden.
 

### 2014-05-27 doc/src/draft.tex
Written report and added RoomDesc

@@
 Servrarna ska kunna hantera många förfrågningar med låg fördröjning, samtidigt som de måste koordinera händelser så att det som en användare gör också ska påverka dem i anslutning till den. 
-Serverprogrammen ska också gärna vara finkornigt modulariserade för att möjliggöra parallellutveklingen av serverprogrammen på ett fungerande sätt.
+Serverprogrammen ska också gärna vara finkornigt modulariserade för att möjliggöra parallellutveklingen av programmen på ett fungerande sätt.
 
@@
 gagnar den enskilda invididen. Möjligheten finns att utforska som enskild individ, men fokuset för spelet ligger i den dynamik som följer av 
-interaktionen med andra spelare. Spelet utspelas på två olika platser, i City och i Dungeon; där City är staden där spelarna samlas efter tidigare utforskningar, 
-kan fylla på förnödenheter samt forma grupper för att gå ner i Dungeons. Dungeons är en procedurellt genererad uppsättning rum fyllt med monster, fällor och skatter. 
-Varje grupp spelare får alltså sin egen unikt genererade Dungeon när gruppen går ner i dessa magiska grottor under staden. Väl inne ges 
-gruppen en eller flera uppdrag som bör fullbordas innan de kommer upp till ytan igen.
+interaktionen med andra spelare.
+Spelet utspelas på två olika platser, i City och i Dungeon.
+City är staden där spelarna samlas innan kommande exkursion, där kan de fylla på förnödenheter samt forma grupper för att gå ner i Dungeons.
+En dungeon är en den värld som spelet utspelar sig i; en uppsättning rum fyllt med monster, fällor och skatter.
+Varje grupp spelare får sin egen unikt genererade Dungeon när de går ner i dessa magiska grottor under staden.
+Väl inne ges gruppen en eller flera uppdrag som bör fullbordas innan de kommer upp till ytan igen.
 
-Relationen mellan konceptet concurrency och vårt projekt är förmågan att ha fler än en spelare aktiva i spelet samtidigt och se hur dessa interagerar med varandra, samt flertalet 
-aktiva spelområden körandes samtidigt och oberoende av varandra.
+Relationen mellan konceptet concurrency och vårt projekt är förmågan att ha fler än en spelare aktiva i spelet samtidigt, samt flertalet aktiva spelområden körandes samtidigt och oberoende av varandra.
 
@@
 Systemarkitekturen som beskrivs i detta dokument är uppdelat i två delar vilka beskriver akritekturen för klienten samt servern.
-Med tanke på att både klienten och servern är skrivna i Scala och körs via Java Virtual Maschine både servern och klienten kan köras på alla plattformar som stödjer Java VM 1.7.
+På grund av att både klienten och servern är skrivna i Scala och körs via Java Virtual Maschine kan både servern och klienten köras på alla plattformar som stödjer Java VM 1.7.
 \begin{figure}[hbt]
@@
 
-Som Figur 1 illustrerar är klientfönstret uppdelat i flera textfält som visar relevant information för spelaren. Huvudområdet är för vanliga server-svar och kommer innehålla beskrivningar 
-av rummet, meddelanden i spelarchatten, meddelanden med systeminformation och liknande. Klientens högra sida är reserverat för ständig information som spelaren behöver ta del av snabbt. 
+Som Figur 1 illustrerar är klientfönstret uppdelat i flera textfält som visar relevant information för spelaren.
+Det vänstra området är huvudområdet och används till spelets dynamiska informaton.
+Där får spelaren beskrivningar av rummen den besöker, meddelanden från andra spelare, meddelanden om vad som händer i spelet och liknande.
+Klientens högra sida innehåller statisk information som det kan vara bra för spelaren att snabbt kunna kolla upp.
 Den övre delen innehåller information om spelarens egen karaktär, där spelarens liv och stridsegenskaper samt hur mycket mat gruppen har listas.
+Den undre håller reda på vilka spelare som är i spelarens dungeon, vilka spelare som är i rummet spelaren är i, samt vad rummet har för föremål, monster och utgångar.
 
-Den nedre delen av fönstret innehåller kommandoraden, där spelaren skriver in kommandon i enlighet med ett strikt syntax. När klienten startas välkomnas spelaren 
-av ett centrerat fönster för inloggning. Här kan spelaren skriva in sitt användarnamn och lösenord samt IP:n tillhörande den server som spelaren vill koppla upp sig mot.
+Den nedre delen av fönstret innehåller kommandoraden, där spelaren skriver in kommandon i enlighet med ett strikt syntax.
+
+När klienten startas välkomnas spelaren av ett centrerat fönster för inloggning.
+Här kan spelaren skriva in sitt användarnamn och lösenord samt IP:n tillhörande den server som spelaren vill koppla upp sig mot.
+Lösenordet krypteras enligt SHA-256 innan det skickas över nätverket och sparas i vår player-map, som håller koll på användarinformationen.
 
@@
 bestämde oss för att nyttja ett rutnät där varje cell representerar ett rum. Spelare kan ta sig från rum till rum via utgångar placerade på några av eller alla rummens fyra väggar.
-Vår algoritm skall även säkerställa att inga rum skapas som inte går att nå från ingången. Nedan beskrivs med pseudokod den algoritm vi bestämde oss för att använda.
+Vår algoritm skall även säkerställa att inga rum skapas som inte går att nå från ingången.
+Nedan beskrivs med pseudokod den algoritm vi bestämde oss för att använda.
+I kort fungerar algoritmen så att först slumpas koordinaterna till ett rum som blir startrummet.
+Därefter slumpas koordinaterna till ett annat rum varefter programmet går i slumpad riktning från det nya rummet till angränsande rum, samtidigt som nya rum skapas i varje ny besökt koordinatruta, tills det nya rummet har fått en anknytning till startrummet.
 \begin{algorithm}

### 2014-05-27 src/lostvaults/server/Dungeon.scala

@@ -70,9 +70,6 @@ class Dungeon extends Actor {
 
   def receive() = {
     case DungeonMakeCity => {
-      //val CityRoom = new Room()
-      //lägg till alla NPCs
-      //rooms = new Array[Room](1)
       become(CityReceive)
     }
     case NewDungeon => {
@@ -215,12 +212,12 @@ class Dungeon extends Actor {
               rooms(currentRoom).activeCombat = Some(context.actorOf(Props[Combat]))
               rooms(currentRoom).activeCombat.get ! self
             }
-            println("Adding " + attacker + " to combat")
-            PMap ! PMapSendGameMessage(attacker, GamePlayerJoinBattle(rooms(currentRoom).activeCombat.get, attackee))
-            PMap ! PMapSendGameMessage(attacker, GameMessage("You have attacked " + attackee))
             println("Adding " + attackee + " to combat")
             PMap ! PMapSendGameMessage(attackee, GamePlayerJoinBattle(rooms(currentRoom).activeCombat.get, attacker))
             PMap ! PMapSendGameMessage(attackee, GameMessage("You have been attacked by " + attacker))
+            println("Adding " + attacker + " to combat")
+            PMap ! PMapSendGameMessage(attacker, GamePlayerJoinBattle(rooms(currentRoom).activeCombat.get, attackee))
+            PMap ! PMapSendGameMessage(attacker, GameMessage("You have attacked " + attackee))
           } else if (rooms(currentRoom).hasNPC(attackee)) {
             println(attacker + " attacks player " + attackee)
             if (rooms(currentRoom).activeCombat == None) {
@@ -228,15 +225,14 @@ class Dungeon extends Actor {
               rooms(currentRoom).activeCombat = Some(context.actorOf(Props[Combat]))
               rooms(currentRoom).activeCombat.get ! self
             }
-            println("Adding " + attacker + " to combat")
-            PMap ! PMapSendGameMessage(attacker, GamePlayerJoinBattle(rooms(currentRoom).activeCombat.get, attackee))
-
-            PMap ! PMapSendGameMessage(attacker, GameMessage("You have attacked " + attackee))
             println("Adding " + attackee + " to combat")
             var npc = rooms(currentRoom).getNPCActorRef(attackee)
             if (npc != None) {
               npc.get ! GamePlayerJoinBattle(rooms(currentRoom).activeCombat.get, attacker)
             }
+            println("Adding " + attacker + " to combat")
[…]

### 2014-05-27 src/lostvaults/server/RoomDescGen.scala

@@ -7,9 +7,12 @@ object RoomDescGen {
   //maybe change item listan till en itemlist istället för en stringlist
   def generateDescription(npc: List[String], items: List[String], exits: List[String]) = {
     if (npc.isEmpty && items.isEmpty) {
-      "The room you walk into is empty. "
+      var string = "\nThe room you walk into is empty. "
+      string += _GenerateExitDesc(exits)
+      string += _GenerateMystery
+      string
     } else {
-      var string = ""
+      var string = "\n"
       string += _GenerateStartingSentence
       string += _GenerateNPCDesc(npc)
       string += _GenerateItemDesc(items)
@@ -168,7 +171,7 @@ object RoomDescGen {
   }
   //Ranges for generateAdjective
   val COLOR = Tuple2(0, 12)
-  val ANYTHING = Tuple2(0, 22)
+  val ANYTHING = Tuple2(0, 16)
   val SIZE = Tuple2(13, 16)
   val SOUND = Tuple2(17, 22)
   def _GenerateAdjective(range: Tuple2[Int, Int]) = {

### 2014-05-27 src/lostvaults/server/RoomGenerator.scala

@@ -44,7 +44,7 @@ class RoomGenerator {
     if (X != startRoom._1 || Y != startRoom._2) {
       var howMany = rand(0, 3)
       var range = (((((startRoom._1 - X).abs.asInstanceOf[Double] + (startRoom._2 - Y).abs.asInstanceOf[Double])) / 16.0) * 10.0).ceil.asInstanceOf[Int] - 1
-      if(range == 0) range = 1
+      if (range == 0) range = 1
       println(startRoom._1 + " - " + X + " + " + startRoom._2 + " - " + Y + " / 16 *  10 = " + range)
       println("ROOMGENERATOR-addItemsToRoom: This is the range: " + range)
       var items = ItemRepo.getManyRandom(howMany, "NoTreasure", range)
@@ -61,7 +61,7 @@ class RoomGenerator {
   }
   def addNPCToRoom(system: ActorSystem, dungeon: ActorRef, X: Int, Y: Int) {
     if (X != startRoom._1 || Y != startRoom._2) {
-      var howMany = 1 //rand(0, 1)
+      var howMany = rand(0, 1)
       var range = (((((startRoom._1 - X).abs.asInstanceOf[Double] + (startRoom._2 - Y).abs.asInstanceOf[Double])) / 16.0) * 10.0).ceil.asInstanceOf[Int] - 1
       if (range == 0) range = 1
       println("ROOMGENERATOR-addNPCToRoom: This is the range: " + range)
@@ -108,7 +108,6 @@ class RoomGenerator {
       directions(5) = 1
       directions(6) = 1
       directions(7) = 1
-
     } else if (dirX == -1 && dirY == 0) {
       directions(0) = 0
       directions(1) = 2
@@ -253,7 +252,8 @@ class RoomGenerator {
         } while (!success)
         created.foreach(c => {
           rooms(coordToIndex(c)).created = true; rooms(coordToIndex(c)).connected = true;
-          if (rand(0, 100) <= 50) addItemsToRoom(c._1, c._2); if (rand(0, 100) <= 100) addNPCToRoom(system, dungeon, c._1, c._2)
+          if (rand(0, 100) <= 50) addItemsToRoom(c._1, c._2); if (rand(0, 100) <= 100) addNPCToRoom(system, dungeon, c._1, c._2);
+          rooms(coordToIndex(c)).createRoomDesc
         })
         var head = (0, 0)
         var lastCoord = (-1, -1)

### 2014-05-28 doc/src/draft.tex
rapport

@@
 Systemarkitekturen som beskrivs i detta dokument är uppdelat i två delar vilka beskriver akritekturen för klienten samt servern.
-På grund av att både klienten och servern är skrivna i Scala och körs via Java Virtual Maschine kan både servern och klienten köras på alla plattformar som stödjer Java VM 1.7.
+På grund av att både klienten och servern är skrivna i Scala och körs via Java Virtual Maschine kan de köras på alla plattformar som stödjer Java VM 1.7.
 \begin{figure}[hbt]
@@
 \subsection{Klient}
-Designen för klienten till Lost Vaults är utvecklad för att efterlikna en indirekt terminal, där ingen logik används förutom att skicka förfrågningar och 
-ta emot samt tolka svaren på förfrågningar.
-Konceptet för en indirekt terminal valdes för att kunna åstadkomma en implementation hos klienten som lätt kan utökas när serverns implementation av spelets logik ökar.
-Detta betyder med andra ord ett system som kan utkökas enkelt endast genom att addera nya förfrågningar och svar.
+Designen för klienten till Lost Vaults är utvecklad för att efterlikna en indirekt terminal, vars ända uppgift är att skicka samt ta emot och tolka svaren på förfrågningar.
+Konceptet med en indirekt terminal valdes för att fokus skulle ligga på spellogiken, och inte på GUI:t.
+Det textbaserade gränssnittet tillåter utökning av serversidan utan att kräva att användaren återinstallerar sin klient.
+Detta innebär att det är enkelt att åtgärda buggar och bygga ut spelet utan att söra användaren.
 
-Som Figur 1 illustrerar är klientfönstret uppdelat i flera textfält som visar relevant information för spelaren.
+Klientfönstret uppdelat i flera textfält som visar relevant information för spelaren, se fig.
+\ref{fig:Client}.
 Det vänstra området är huvudområdet och används till spelets dynamiska informaton.
@@
 Klientens högra sida innehåller statisk information som det kan vara bra för spelaren att snabbt kunna kolla upp.
-Den övre delen innehåller information om spelarens egen karaktär, där spelarens liv och stridsegenskaper samt hur mycket mat gruppen har listas.
+Den övre delen innehåller information om spelarens egen karaktär, där listas bl.a.
+spelarens liv, stridsegenskaper och hur mycket mat spelaren har.
 Den undre håller reda på vilka spelare som är i spelarens dungeon, vilka spelare som är i rummet spelaren är i, samt vad rummet har för föremål, monster och utgångar.
@@
 Här kan spelaren skriva in sitt användarnamn och lösenord samt IP:n tillhörande den server som spelaren vill koppla upp sig mot.
-Lösenordet krypteras enligt SHA-256 innan det skickas över nätverket och sparas i vår player-map, som håller koll på användarinformationen.
+Lösenordet krypteras enligt SHA-256 innan det skickas över nätverket och sparas i databasen, som håller koll på användarinformationen.
 
@@
 \subsubsection{Klassmodell}
-Klienten är strukturerad i fyra distinkta klasser som beskrivs i Figur \ref{fig:ClientArch}. Klasserna PlayGame och PlayGameCommunication arbetar 
-tillsammans för att skapa en brygga mellan TCP lagret och GUI:t, där PlayGame accepterar meddelanden från TCPClient och skickar dem 
-vidare till GUI via PlayGameCommunication. Samtidigt så skickas data från GUI över nätverket via metodanrop i PlayGameCommuncation till 
-PlayGame för att sedan hamna hos TCPClient.
+Klienten är strukturerad i fyra distinkta klasser, se fig.
+\ref{fig:ClientArch}.
+Klasserna PlayGame och PlayGameCommunication arbetar tillsammans för att skapa en brygga mellan TCP lagret och GUI:t.
+PlayGame accepterar meddelanden från TCPClient och skickar dem vidare till GUI via PlayGameCommunication.
+Samtidigt skickas data från GUI över nätverket via metodanrop i PlayGameCommuncation till PlayGame för att sedan hamna hos TCPClient.
 
 \subsection{Server}
-Systemarkitekturens serverdel är uppdelad i sektionerna Aktörmodell och Klassmodell. Den första delen beskriver funktionen hos de olika aktörlagren i Lost Vaults servern och 
-den andra ger en  beskrivning av serverns klassförhållanden.
+Systemarkitekturens serverdel är uppdelad i sektionerna Aktörmodell och Klassmodell.
+Den första delen beskriver funktionen hos de olika aktörlagren i Lost Vaults servern och den andra ger en  beskrivning av serverns klassförhållanden.
 
@@
 \end{figure}
-\subsection{Server-side}
 
 \subsubsection{Aktörmodell}
-Serverdelen är uppdelad i flera processer via Akkas aktörbibliotek för att upprätthålla Actor Concurrency-modellen i enlighet med Figur \ref{fig:ConManPlayer} och Figur \ref{fig:ServerActorModel}. 
-Endast två typer av aktörer kommmunicerar direkt med nätverket via TCP/IP, ConManaktören och Playeraktörerna. ConManaktören har som syfte att hantera inkommande anslutningar samt ansvarar 
-för att skapa Playeraktörer som nya högnivå aktörer innan de registreras som den nyetablerade anslutningens lyssnare. Som lyssnare kommer Playeraktören ta emot och skicka data 
-över nätverket. Playeraktören styr över alla attribut relaterade till sin klient, som exempelvis spelarens attribut och för att verifiera 
-inloggningsförsök via kommunikation med PlayerMap och en databas innehållande inloggningsinformation. Det är även via Playeraktören andra aktörer kan skicka meddelanden över nätverket vid behov.
+Serverdelen är uppdelad i flera processer via Akkas aktörbibliotek för att upprätthålla Actor Concurrency-modellen .
+Två typer av aktörer kommmunicerar direkt med nätverket via TCP/IP, ConManaktören och Playeraktörerna.
+ConManaktören har som syfte att hantera inkommande anslutningar för att sedan starta en ny Playeraktör för varje godkänd anslutning.
+Den nyetablerade anslutningen skickas till den nya Playeraktören, som sedan kommer hantera all kommunikation mellan spelet och den nyanslutna klienten, se fig.
+\ref{fig:ConManPlayer}.
 
-PlayerMapaktören och GroupMapaktören fyller två specifika och snarlika funktioner. PlayerMap mappar en sträng, namnet på en uppkopplad spelare, till den aktör som kontrollerar 
-spelaren med det eftersökta namnet. Genom denna aktör kan en annan aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - 
-ett viktigt kommando som agerar på följande sätt är exempelvis “WHISPER”. PlayerMap möjliggör även ett snabbt och enkelt sätt för Playeraktören att försäkra 
-sig om att det inte existerar flera spelare med samma namn på servern.
+PlayerMapaktören och GroupMapaktören fyller två specifika funktioner.
+PlayerMap mappar på en uppkopplad spelares användarnamn till spelarens Playeraktör.
+Genom PlayerMap kan en aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - ett viktigt kommando som agerar på följande sätt är exempelvis “WHISPER”.
+Det är även via PlayerMap som Playeraktören ser till att samma användarnamn inte används av flera uppkopplade spelare samtidigt.
 
@@
 
-GroupMapaktören fyller en liknande funktion som PlayerMap, men länkar istället namnen på spelarna med spelargrupper istället för spelaraktörer. 
-En spelargrupp är en samling av en eller fler spelare som tillsammans kan gå ner i en Dungeon, som är procedurellt genererad för just dem. Syftet med 
-denna aktör är att underlätta skapandet av spelargrupper samt anslutning till redan existerande spelargrupper. Genom att använda GroupMap räcker det att ansluta sig till en 
-spelare via dess namn för att inkluderas i denna spelares grupp, eller för att skapa en ny grupp med denna spelare.
+GroupMapaktörens uppgift är att länka samman namn på spelare, för att forma spelargrupper, se fig.
+\ref{fig:ServerActorModel}.
+En spelargrupp är en samling av en eller fler spelare som tillsammans kan gå ner i en Dungeon.
+Syftet med denna aktör är att underlätta skapandet av spelargrupper samt anslutning till redan existerande spelargrupper.
+Genom att använda GroupMap räcker det att ansluta sig till en spelare via dess namn för att inkluderas i denna spelares grupp.
 
 De två resterande lagren av aktörer som servern använder är Dungeonlagret och Stridslagret, och det är dessa som utför spelets logik.
-Det existerar ett speciellt tillstånd av Dungeonaktören, kallat Cityaktören. City existerar ständigt 
-under serverns livstid och hanterar spelets sociala aspekt, såsom chattande och skapandet av grupper. 
-Det som Dungeonaktören ansvarar för är genererandet och hanterandet av den procedurellt skapade 
-grotta som består av multipla och sammanlänkade rum i ett tvådimensionellt rutnät. Det är i dessa rum som spelare kommer kunna göra uppdrag, 
-finna skatter, slåss mot monster eller spelare etc. Dungeonaktören ansvarar även för koordinationen av alla spelare som finns i grottan. 
-Ett exempel på detta är kommandot “SAY”  som ska skickas till relevanta spelare. 
-Strider koordineras av sin egna aktör, en finit tillståndsmaskin kallad Combat, som sköter turordning av spelare och monster vid strid. Varje rum i en Dungeon kan innehålla en
-referens till en Combat, vilket leder till att det som max kan vara upp till en combat aktiv per rum. Combataktören skapas då spelare går i strid mot monster eller andra spelare
-och terminerar när det inte längre finns någon som anfaller någon annan.
+Det existerar ett speciellt tillstånd av Dungeonaktören, kallat Cityaktören.
+City är spelets uppsamlingsplats.
+Det är här spelaren bildar grupper med andra spelare, för att göra sig i ordning inför utforskandet av en Dungeon.
+Så i City kan spelaren chatta med andra spelare, köpa mat och bilda grupper.
+
+När en grupp bestämmer sig för att stiga in i en Dungeon skapas en ny slumpvis genererad grotta, som endast de kan komma åt.
+Grottan består av en array med rum med dörrar som spelaren kan förflytta sig emellan.
+Det är i dessa rum som spelare kommer kunna göra uppdrag, finna skatter, slåss mot monster eller andra spelare etc.
+Dungeonaktören koordinerar också kommunikation, och händelser som påverkar spelarna som befinner sig i grottan.
+Ett exempel på detta är kommandot “SAY”  som skickar ett meddelande till alla spelare som är i samma rum som spelaren.
+
+Strider koordineras av sin egen aktör, en finit tillståndsmaskin kallad Combat, som sköter turordning av spelare och monster vid strid.
+Varje rum i en Dungeon kan innehålla en referens till en Combat, vilket leder till att det kan vara max en aktiv Combat per rum.
+Combataktören skapas då spelare går i strid mot monster eller andra spelare och terminerar när det inte längre finns någon som anfaller någon annan.
 
@@
 \subsubsection{Klassmodell}
-Figur \ref{fig:ServerKlassModell} visar de olika klasserna i serverimplementationen.
-De är uppdelade i fyra lager; Verktygslagret, Anslutningslagret, Spelarlagret och Dungeonlagret. Indelningen i dessa lager följer till stor del
-den indelning som gjorts i vilka klasser är sina egna aktörer. Undantagen till detta är verktygslagret, där klasserna PlayerMap, GroupMap och CheatActor är sina egna aktörer samt 
-Combat klassen som i denna figur flyttats från sitt egna lager (se figur \ref{fig:ServerActorModel}) för att visa dess täta koppling med Room klassen.
+Klasserna i servermodellen är konceptuellt uppdelade i fyra lager: Anslutningslagret, Spelarlagret, Dungeonlagret och Verktygslagret, se fig \ref{fig:ServerKlassModell}.
 
-Bortsett från RoomGenerator och RoomDescGenerator är alla klasser i Verktygslagret Singletons. Lagret tillhandahåller  understödjande funktionalitet till de andra klasserna.
-Anslutningslagret är ingångspunkten till servern över nätverket genom Akkas TCP bibliotek. Vår anslutningshanterare, ConMan, agerar som en singleton och endast en 
-instans av denna ska existera vid en given tidpunkt. ConMan är den klass som lystnar efter och godtar anslutningar från klienter, samt skapar nya Player-instanser vid nyupprättad anslutning.
+Anslutningslagret är ingångspunkten till servern över nätverket genom Akkas TCP bibliotek.
+Vår anslutningshanterare, ConMan, agerar som en singleton och endast en instans av denna ska existera vid en given tidpunkt.
+ConMan är den klass som lyssnar efter och godtar anslutningar från klienter, samt skapar nya Player-instanser vid nyupprättad anslutning.
 
-Dungeonlagret innehåller de klasser som är viktiga för spelets logiska funktioner. Lagret innehåller dungeonklassen, som ansvarar över en mängd slumpmässigt genererade rum, som i sin tur
-ansvarar för aktiva strider samt icke-spelarkaraktärer och objekt. Tidigare design visar att Item klassen används som superklass till olika typer av objekt. Vi valde dock att platta till 
-vår klasshierarki och förenkla designen genom att låta alla typer av objekt vara instanser av Item klassen med olika attribut. På samma sätt valde vi att göra oss av med distinktionen mellan
-goda och onda icke-spelarkaraktärer, och har istället valt att implementera enbart monster.
+Dungeonlagret innehåller de klasser som är viktiga för spelets logiska funktioner.
+Lagret innehåller dungeonklassen, som ansvarar över en mängd slumpmässigt genererade rum.
+Rummen i sin tur ansvarar för aktiva strider samt icke-spelarkaraktärer och objekt.
+Tidigare design visar att Item klassen används som superklass till olika typer av objekt.
+Vi valde dock att platta till vår klasshierarki och förenkla designen genom att låta alla typer av objekt vara instanser av Item klassen med olika attribut.
+På samma sätt valde vi att göra oss av med distinktionen mellan goda och onda icke-spelarkaraktärer, och har istället valt att implementera enbart monster.
+
+Verktygslagret tillhandahåller understödjande funktionalitet till de andra klasserna. Bortsett från RoomGenerator är alla klasser i Verktygslagret Singletons.
 
@@
 
-I detta projekt användes flera olika verktyg för att underlätta utvecklingen. Då vi använt Scala som vårt val av programspråk skrevs i princip all vår kod i Eclipse. 
-Detta då vi anser att det i särklass är det enklaste sättet att utveckla kod till Java eller Scala. Även fast all kod är skriven i Eclipse använder vi Ant Build System 
-för automatiserad kompilering samt vid byggandet av vår klient och server; som efter kompilering är klar att köras i Java Virtual Machine.
+I detta projekt användes flera olika verktyg för att underlätta utvecklingen.
+Då vi använt Scala som vårt val av programspråk skrevs i princip all vår kod i Eclipse.
+Detta då vi anser att det i särklass är det enklaste sättet att utveckla kod till Java eller Scala.
+Trots att all kod är skriven i Eclipse använder vi Ant Build System
+för automatiserad kompilering av vår klient och server; som sedan är klar att köras i Java Virtual Machine.
 
-För hanteringen av versionskontroll har vi använt det tillförlitliga och välkända verktyget Git. Vi satte upp ett nytt git repository på Github.com specifikt för detta 
-projekt och valet av Git gjordes på grund av dess styrkor samt att vi är vana användare av det.
+För hanteringen av versionskontroll har vi använt det tillförlitliga och välkända verktyget Git.
+Vi satte upp ett nytt git repository på Github.com specifikt för detta projekt och valet av Git gjordes på grund av att vi har använt oss av det tidigare, och för att det har bra funktioner för versionshantering och för att sammanfoga parallellskriven kod.
 
-Testandet av vår kod görs med ScalaTest ramverket samt ett Ant Build skript som ger oss möjligheten till automatiskt byggande och körning av tester.
+Testandet av vår kod görs med ScalaTest-ramverket samt ett Ant Build-skript som ger oss möjligheten till automatiskt byggande och körning av tester.
 
-Sammansättningen av dokumentationen utförs med Scaladoc på grund av dess likhet med JavaDoc, ett verktyg vi är vana med att använda, och Ant har reviderats för att automatiskt 
-bygga dokumentationen.
+Sammansättningen av dokumentationen utförs med Scaladoc på grund av dess likhet med JavaDoc, ett verktyg vi är vana med att använda, och Ant har omarbetats för att automatiskt bygga dokumentationen.
 
@@
 Scala är bra för skalbarhet, vilket innebär att vårt program kommer fungera bra oavsätt om det är tio användare online eller om det är tio tusen.
-En annan anledning till att vi valde Scala är att Scala är ett objektorienterat språk, vilket passade nära med det tänket vi hade när vi skapade programmet.
+En annan anledning till att vi valde Scala är att Scala är ett objektorienterat språk, vilket passade ihop med det tänket vi hade när vi började planera programmet.
 Vi fokuserade på att skapa objekt som interagereade på rätt sätt med varandra, snarare än att skriva kod som ska exekveras i en särskild ordning.
@@
 
-Genom rekommendationer av skaparna bakom Scala och via språkets styrkor och enkelhet, beslöt vi oss för 
-att använda Akka som vårt aktörbibliotek.
+Genom rekommendationer av skaparna bakom Scala, beslöt vi oss för att använda Akka som vårt aktörbibliotek.
 Detta för att kunna använda Akkas TCP-bibliotek för nätverkskommunikationen.

### 2014-05-28 src/lostvaults/server/RoomDescGen.scala
Lite fix med roomDesc

@@ -118,10 +118,11 @@ object RoomDescGen {
     }
   }
   def _GenerateExitDesc(exits: List[String]) = {
+    println(exits)
     exits.length match {
       case 0 => "You see no doors in front of you. "
       case 1 => "You see a door to the " + exits.head + ". "
-      case 2 => "You see doors to the " + exits.head + " and the" + exits.tail.head + ". "
+      case 2 => "You see doors to the " + exits.head + " and the " + exits.tail.head + ". "
       case 3 => "You see doors to the " + exits.head + ", " + exits.tail.head + " and to the " + exits.tail.tail.head
       case _ => "You see doors to the " + exits.head + ", " + exits.tail.head + ", " + exits.tail.tail.head + " and to the " + exits.tail.tail.tail.head
     }
@@ -175,7 +176,7 @@ object RoomDescGen {
   val SIZE = Tuple2(13, 16)
   val SOUND = Tuple2(17, 22)
   def _GenerateAdjective(range: Tuple2[Int, Int]) = {
-    val num = rand.nextInt(range._2) + range._1
+    val num = rand.nextInt(range._2 - range._1) + range._1
     num match {
       case 0 => "lemony yellow"
       case 1 => "blue"

### 2014-05-28 src/lostvaults/server/RoomGenerator.scala

@@ -252,9 +252,7 @@ class RoomGenerator {
         } while (!success)
         created.foreach(c => {
           rooms(coordToIndex(c)).created = true; rooms(coordToIndex(c)).connected = true;
-          if (rand(0, 100) <= 50) addItemsToRoom(c._1, c._2); if (rand(0, 100) <= 100) addNPCToRoom(system, dungeon, c._1, c._2);
-          rooms(coordToIndex(c)).createRoomDesc
-        })
+          if (rand(0, 100) <= 50) addItemsToRoom(c._1, c._2); if (rand(0, 100) <= 100) addNPCToRoom(system, dungeon, c._1, c._2);})
         var head = (0, 0)
         var lastCoord = (-1, -1)
         while (!(created isEmpty)) {
@@ -273,6 +271,7 @@ class RoomGenerator {
       }
     } while (roomsCreated < 40)
     // Finally return the generated array of rooms.
+      rooms.foreach(c => if(c.created == true) {c.createRoomDesc})
     println("Created " + itemcnt + " items in " + itemrooms + " rooms.")
     rooms
   }

### 2014-05-29 doc/src/draft.tex
-

--- 2014-05-26 doc/src/draft.tex
@@
 \floatname{algorithm}{Algoritm}
-\renewcommand{\algorithmicindent}{4 pt}
+\renewcommand{\algorithmicindent}{8 pt}
 \begin{document}
@@
 \pagenumbering{Roman}
+
 \tableofcontents
@@
 bestämde oss för att nyttja ett rutnät där varje cell representerar ett rum. Spelare kan ta sig från rum till rum via utgångar placerade på några av eller alla rummens fyra väggar.
-Vår algoritm skall även säkerställa att inga rum skapas som inte går att nå från ingången. Nedan beskrivs med pseudokod den algoritm vi bestämde oss för att använda.
+Vår algoritm skall även säkerställa att inga rum skapas som inte går att nå från ingången. Algoritm \ref{alg:RoomGen} beskriver med pseudokod den algoritm vi bestämde oss för att använda.
 \begin{algorithm}
@@
 \end{algorithmic}
-
 \end{algorithm}
@@
 \subsection{Datastrukturer}
+Under projektets gång har vi använt oss av Scalas standarbibliotek för datastrukturer där vi behövt använda datasamlingar. 
+Förutom arräer och listor har vi använt oss av Hashmap för att kunna koppla spelarnamn med aktörer och spelargrupper, vilket ses i klasserna
+PlayerMap och GroupMap.
 
@@
 Vi har också skapat en \textit{god mode} som gör att man i terminalen kan ge spelare speciella items, samt hela den så att den får fullt hp.
-Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla salarna.
+Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla rum i en dungeon.
 
@@
 information att ta del av om hur vi skulle gå till väga för att göra detta. En annan sak som också varit relativt svår var att 
-begränsa oss när det gällde den utsträckning för vilket spelet skulle utvecklas. Att begränsa utvecklingen till en rimlig nivå för spelet 
-och samtidigt ha det tillräckligt intressant för den som spelar.
+begränsa oss när det gällde den utsträckning för vilket spelet skulle utvecklas. Att begränsa oss till en rimlig nivå för spelet 
+och samtidigt ha det tillräckligt intressant för den som spelar visade sig vara mer utmanande än vi först trott.
 
-En stor sak som vi inte han med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa stek skulle vara, nu när det grundläggande fungerar som det ska.
+En stor sak som vi inte hann med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa steg skulle vara, nu när det grundläggande fungerar som det ska.
 

### 2014-05-29 doc/src/draft.tex
Added som changes to the draft

@@
 \floatname{algorithm}{Algoritm}
-\renewcommand{\algorithmicindent}{8 pt}
+\renewcommand{\algorithmicindent}{4 pt}
 \begin{document}
@@
 \pagenumbering{Roman}
-
 \tableofcontents
@@
 
-Efter att Cityaktören har skapat en Dungeonaktör ansvarar den nya aktören för sin egen livslängd och avsutar sig själv endast när det inte längre finns några spelare i den.
+Efter att Cityaktören har skapat en Dungeonaktör ansvarar den nya aktören för sin egen livslängd och avslutar sig själv endast när det inte längre finns några spelare i den.
 
@@
 bestämde oss för att nyttja ett rutnät där varje cell representerar ett rum. Spelare kan ta sig från rum till rum via utgångar placerade på några av eller alla rummens fyra väggar.
-Vår algoritm skall även säkerställa att inga rum skapas som inte går att nå från ingången. Algoritm \ref{alg:RoomGen} beskriver med pseudokod den algoritm vi bestämde oss för att använda.
+Vår algoritm skall även säkerställa att inga rum skapas som inte går att nå från ingången. Nedan beskrivs med pseudokod den algoritm vi bestämde oss för att använda.
 \begin{algorithm}
@@
 \end{algorithmic}
+
 \end{algorithm}
@@
 \subsection{Datastrukturer}
-Under projektets gång har vi använt oss av Scalas standarbibliotek för datastrukturer där vi behövt använda datasamlingar. 
-Förutom arräer och listor har vi använt oss av Hashmap för att kunna koppla spelarnamn med aktörer och spelargrupper, vilket ses i klasserna
-PlayerMap och GroupMap.
 
@@
 Vi har också skapat en \textit{god mode} som gör att man i terminalen kan ge spelare speciella items, samt hela den så att den får fullt hp.
-Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla rum i en dungeon.
+Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla salarna.
 
@@
 information att ta del av om hur vi skulle gå till väga för att göra detta. En annan sak som också varit relativt svår var att 
-begränsa oss när det gällde den utsträckning för vilket spelet skulle utvecklas. Att begränsa oss till en rimlig nivå för spelet 
-och samtidigt ha det tillräckligt intressant för den som spelar visade sig vara mer utmanande än vi först trott.
+begränsa oss när det gällde den utsträckning för vilket spelet skulle utvecklas. Att begränsa utvecklingen till en rimlig nivå för spelet 
+och samtidigt ha det tillräckligt intressant för den som spelar.
 
-En stor sak som vi inte hann med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa steg skulle vara, nu när det grundläggande fungerar som det ska.
+En stor sak som vi inte han med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa steg skulle vara, nu när det grundläggande fungerar som det ska.
 

### 2014-05-29 doc/src/draft.tex

--- 2014-05-28 doc/src/draft.tex
@@
 
-En stor sak som vi inte han med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa stek skulle vara, nu när det grundläggande fungerar som det ska.
+En stor sak som vi inte han med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa steg skulle vara, nu när det grundläggande fungerar som det ska.
 

### 2014-05-29 doc/src/draft.tex
Uppdated 'Programspråk' under implementation.

@@
 
-Efter att Cityaktören har skapat en Dungeonaktör ansvarar den nya aktören för sin egen livslängd och avslutar sig själv endast när det inte längre finns några spelare i den.
+Efter att Cityaktören har skapat en Dungeonaktör ansvarar den nya aktören för sin egen livslängd och avsutar sig själv endast när det inte längre finns några spelare i den.
 
@@
 \subsection{Programspråk}
-För att möjliggöra massiv concurrency med många individuella aktörer har vi gjort vårt projekt i Scala.
+%För att möjliggöra massiv concurrency med många individuella aktörer har vi gjort vårt projekt i Scala.
 Scala är bra för skalbarhet, vilket innebär att vårt program kommer fungera bra oavsätt om det är tio användare online eller om det är tio tusen.
@@
 
-Scala bygger på Java, och erbjuder därför liknande syntax.
+%Scala bygger på Java, och erbjuder därför liknande syntax.
 Detta innebar att övergången mellan att skriva Java och Scala var en någorlunda mjuk sådan, koden var ganska lättigenkännlig samtidigt som vi fick fördelarna med att kunna utveckla skalbart.
 Några nackdelar med Scala som vi finner nämnvärda är exempelvis att det, trots likheter med Java, tog en viss tid att sätta sig in i det nya
-språket vilket kan ha motarbetat utvecklingen gämfört med om vi hade valt ett annat språk som vi var mer bekanta med.
+%språket vilket kan ha motarbetat utvecklingen gämfört med om vi hade valt ett annat språk som vi var mer bekanta med.
 
-Genom rekommendationer av skaparna bakom Scala, beslöt vi oss för att använda Akka som vårt aktörbibliotek.
+%Genom rekommendationer av skaparna bakom Scala, beslöt vi oss för att använda Akka som vårt aktörbibliotek.
 Detta för att kunna använda Akkas TCP-bibliotek för nätverkskommunikationen.
@@
 
-Java var det språket vi valde att använda vid skapandet av det grafiska gränssnittet som spelaren agerar mot. Vårt val grundade sig i biblioteket Swing som Java tillhandahåller. 
-Med hjälp att detta bibliotek var skapandet av det grafiska gränssnittet en relativt enkel process. Likt många andra av Javas bibliotek var dokumentationen välskriven och enkel 
-att använda vilket underlättade processen. En annan aspekt som fick oss att välja Java för just denna del var att vi ville kunna kommunicera med resterande kod, skriven i Scala, 
-på ett enkelt sätt och detta kunde uppnås utan problem då Scala är byggt utifrån Javas Virtuella Maskin.
+%Java var det språket vi valde att använda vid skapandet av det grafiska gränssnittet som spelaren agerar mot. Vårt val grundade sig i biblioteket Swing som Java tillhandahåller. 
+%Med hjälp att detta bibliotek var skapandet av det grafiska gränssnittet en relativt enkel process. Likt många andra av Javas bibliotek var dokumentationen välskriven och enkel 
+%att använda vilket underlättade processen. En annan aspekt som fick oss att välja Java för just denna del var att vi ville kunna kommunicera med resterande kod, skriven i Scala, 
+%på ett enkelt sätt och detta kunde uppnås utan problem då Scala är byggt utifrån Javas Virtuella Maskin. 
+Vid reflektion över vår systemdesign och speciellt det aktörsystem vi planerade för kom vi fram till att vi skulle behöva
+ett stort antal aktörer körandes även vid ett lågt antal spelare och därmed att skalbarhet var en viktig faktor vid vårt
+val av språk. Vi kom fram till att vi skulle använda antingen Scala eller Erlang och efter en kort diskussion valde vi Scala.
+
+Att vi valde Scala över Erlang var dels en önskan att lära oss ett nytt språk, dels att just skalbarhet är just grundtanken
+i Scala och dels dess integrationsmöjligheter med Java och de likheter som finns mellan språken. Att lära oss skriva Scala kod
+visade sig vara en utmaning men likheterna med Java underlättade processen och vi kom snabbt igång.
+
+Scala är ett multiparadigmsspråks och tillåter att program skrivs både funktionellt och objektorienterat/imperativt. Detta gav oss en stor
+fördel vid implementationen av vår design då vi kunde använda en klasshierarki för våra aktörer men samtidigt använda 
+funktionella lösningar där dessa underlättade utvecklingen.
+
+Dess närhet med Java var dock grund till en del av svårigheterna att vänja sig till Scala. Scala använder både egna standardbibliotek
+och Javas standardbibliotek men inte alltid helt konsekvent. Samtidigt är alla datasamlingsstrukturer i Scala \textit{oföränderliga} 
+som standard, då trådsäkerhet är fundamentalt till Scala, vilket krävde en viss vana för att användas på rätt sätt.
+
+Versionen av Scala vi valde att använda har valt att tillfrån gå sitt egna aktörsbibliotek och istället använda sig av ett externt
+bibliotek kallat Akka. Vårt projekt använder till följd även det Akkas bibliotek för implementationen av det aktörssystem som
+vår server använder. Akka som bibliotek var samtidigt både lättanvänt och svårt att sätta sig in i. Det behövdes en viss förståelse
+för hur biblioteksskaparna tänkt sig att det ska användas för att förstå den dokumentation som finns tillgänglig och det krävdes
+en del försöksprogram för att sätta sig in i just hur biblioteket fungerar. Akka tillhandahöll även en implementation av TCP/IP
+sockets vilket märkbart förenklade nätverksdelen av vår kod och med dess hjälp undkom vi vad kunde varit stor huvudbry då vi inte
+hade stor erfarenhet av nätverkskodning sen tidigare.
+
+Att Scala är byggt ovanpå Javas virtuella maskin innebar att vi lätt kunde använda Javas Swing bibliotek för att snabbt skapa
+ett grafiskt gränssnitt till den klient som kommunicerar mot vår server. Bortsett från gränssnittet använder även klienten i
+grunden Scala och Akkas TCP/IP bibliotek.
 
@@
 bestämde oss för att nyttja ett rutnät där varje cell representerar ett rum. Spelare kan ta sig från rum till rum via utgångar placerade på några av eller alla rummens fyra väggar.
-Vår algoritm skall även säkerställa att inga rum skapas som inte går att nå från ingången.
-Nedan beskrivs med pseudokod den algoritm vi bestämde oss för att använda.
+
+Vår algoritm skall även säkerställa att inga rum skapas som inte går att nå från ingången. Algoritm \ref{alg:RoomGen} beskriver med pseudokod den algoritm vi bestämde oss för att använda. 
 I kort fungerar algoritmen så att först slumpas koordinaterna till ett rum som blir startrummet. 
-Därefter slumpas koordinaterna till ett annat rum varefter programmet går i slumpad riktning från det nya rummet till angränsande rum, samtidigt som nya rum skapas i varje ny besökt koordinatruta, tills det nya rummet har fått en anknytning till startrummet.
+Därefter slumpas koordinaterna till ett annat rum varefter programmet går i slumpad riktning från det nya rummet 
+till angränsande rum, samtidigt som nya rum skapas i varje ny besökt koordinatruta, tills det nya rummet har fått 
+en anknytning till startrummet.
+
 \begin{algorithm}
@@
 information att ta del av om hur vi skulle gå till väga för att göra detta. En annan sak som också varit relativt svår var att 
-begränsa oss när det gällde den utsträckning för vilket spelet skulle utvecklas. Att begränsa utvecklingen till en rimlig nivå för spelet 
-och samtidigt ha det tillräckligt intressant för den som spelar.
+begränsa oss när det gällde den utsträckning för vilket spelet skulle utvecklas. Att begränsa oss till en rimlig nivå för spelet 
+och samtidigt ha det tillräckligt intressant för den som spelar visade sig vara mer utmanande än vi först trott.
 
-En stor sak som vi inte han med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa steg skulle vara, nu när det grundläggande fungerar som det ska.
+En stor sak som vi inte hann med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa steg skulle vara, nu när det grundläggande fungerar som det ska.
 

### 2014-05-29 doc/src/draft.tex
draft

--- 2014-05-29 doc/src/draft.tex
@@
 Vårt slutresultat är ett textbaserat multiplayer dungeon spel.
-I spelets startrum kan man chatta med de andra spelarna som är online genom whisper (personligt meddelande) eller say (till alla spelare i rummet).
+I spelets startrum kan man chatta med de andra spelarna som är online genom \textit{WHISPER} (personligt meddelande) eller \textit{SAY} (till alla spelare i rummet).
 Där kan man också forma en grupp så att man tillsammans med andra spelare kan gå ner i en dungeon och börja spela.
-Väl nere i en dungeon kan man chatta som vanligt, men man kan också plocka upp saker som man hittar i grottan, börja slåss mot en spelare eller NPC som är i rummet och man kan gå till andra rum.
+Väl nere i en dungeon kan man chatta som vanligt, men man kan också plocka upp saker man hittar, gå till andra rum och slåss mot andra spelare eller NPC som är i rummet.
 När detta sker uppdateras klienten på korrekt sätt, så att spelaren får information om vad som händer i grottan.
-Vi har också skapat en \textit{god mode} som gör att man i terminalen kan ge spelare speciella items, samt hela den så att den får fullt hp.
+
+Vi har också skapat ett administrationsverktyg som gör att man i terminalen kan ge spelare objekt, återställa hälsan så att spelaren får fullt HP\footnote{HP står för Health Points, vilket är hur mycket liv spelaren har vid givet tillfälle} och skada den genom att bestämma hur mycket HP som ska dras av (man kan inte döda en spelare).
 Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla salarna.
@@
 
-En stor sak som vi inte han med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa steg skulle vara, nu när det grundläggande fungerar som det ska.
+En stor sak som vi inte han med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa stek skulle vara, nu när det grundläggande fungerar som det ska.
 

### 2014-05-29 doc/src/draft.tex
Fixed draft

@@
 \section{Inledning}
-Att spela spel över internet är en del av vår kultur som antagligen aldrig kommer försvinna. Det är ett sätt att umgås och samarbeta, ofta med människor man aldrig har mött. 
+Att spela spel över internet har blivit en del av vår kultur som antagligen aldrig kommer försvinna. Det är ett sätt att umgås och samarbeta, ofta med människor man aldrig har mött. 
 På många platser i världen är gigantiska servrar igång dygnet runt för att hantera förfrågningar från miljontals användare, och tusentals programmerare gör sitt bästa för 
@@
 För att detta ska vara möjligt krävs mycket av serverprogrammen. 
-Servrarna ska kunna hantera många förfrågningar med låg fördröjning, samtidigt som de måste koordinera händelser så att det som en användare gör också ska påverka dem i anslutning till den. 
-Serverprogrammen ska också gärna vara finkornigt modulariserade för att möjliggöra parallellutveklingen av programmen på ett fungerande sätt.
+Servrarna ska kunna hantera massvis av förfrågningar med låg fördröjning, samtidigt som de måste koordinera händelser så att det som en användare gör också ska påverka dem i anslutning till den. 
+Serverprogrammen ska också vara finkornigt modulariserade för att möjliggöra parallellutveckling av programmen på ett fungerande sätt.
 
@@
 Spelet kallas \textit{The Lost Vaults - Uneasy Alliance} och är ett semi-traditionellt MUD där användaren interagerar med andra spelare och tar del i uppdrag. 
-Detta sker i grupper av flertal spelare som tillsammans arbetar mot ett gemensamt mål samtidigt som varje enskild gruppmedlem har en personlig agenda som endast 
+Detta sker i grupper av flertal spelare vilka tillsammans arbetar mot ett gemensamt mål. Samtidigt har varje enskild gruppmedlem en personlig agenda som endast 
 gagnar den enskilda invididen. Möjligheten finns att utforska som enskild individ, men fokuset för spelet ligger i den dynamik som följer av 
@@
 City är staden där spelarna samlas innan kommande exkursion, där kan de fylla på förnödenheter samt forma grupper för att gå ner i Dungeons.
-En dungeon är en den värld som spelet utspelar sig i; en uppsättning rum fyllt med monster, fällor och skatter.
+En dungeon är den värld som spelet utspelar sig i; en uppsättning rum fyllt med monster, fällor och skatter.
 Varje grupp spelare får sin egen unikt genererade Dungeon när de går ner i dessa magiska grottor under staden.
@@
 Vårt slutresultat är ett textbaserat multiplayer dungeon spel.
-I spelets startrum kan man chatta med de andra spelarna som är online genom \textit{WHISPER} (personligt meddelande) eller \textit{SAY} (till alla spelare i rummet).
+I spelets startrum kan man chatta med de andra spelarna som är online genom whisper (personligt meddelande) eller say (till alla spelare i rummet).
 Där kan man också forma en grupp så att man tillsammans med andra spelare kan gå ner i en dungeon och börja spela.
-Väl nere i en dungeon kan man chatta som vanligt, men man kan också plocka upp saker man hittar, gå till andra rum och slåss mot andra spelare eller NPC som är i rummet.
+Väl nere i en dungeon kan man chatta som vanligt, men man kan också plocka upp saker som man hittar i grottan, börja slåss mot en spelare eller NPC som är i rummet och man kan gå till andra rum.
 När detta sker uppdateras klienten på korrekt sätt, så att spelaren får information om vad som händer i grottan.
-
-Vi har också skapat ett administrationsverktyg som gör att man i terminalen kan ge spelare objekt, återställa hälsan så att spelaren får fullt HP\footnote{HP står för Health Points, vilket är hur mycket liv spelaren har vid givet tillfälle} och skada den genom att bestämma hur mycket HP som ska dras av (man kan inte döda en spelare).
+Vi har också skapat en \textit{god mode} som gör att man i terminalen kan ge spelare speciella items, samt hela den så att den får fullt hp.
 Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla salarna.

### 2014-05-29 doc/src/draft.tex
-

--- 2014-05-29 doc/src/draft.tex
@@
 \subsection{Programspråk}
-För att möjliggöra massiv concurrency med många individuella aktörer har vi gjort vårt projekt i Scala.
-Scala är bra för skalbarhet, vilket innebär att vårt program kommer fungera bra oavsätt om det är tio användare online eller om det är tio tusen.
-En annan anledning till att vi valde Scala är att Scala är ett objektorienterat språk, vilket passade ihop med det tänket vi hade när vi började planera programmet.
-Vi fokuserade på att skapa objekt som interagereade på rätt sätt med varandra, snarare än att skriva kod som ska exekveras i en särskild ordning.
+Vid reflektion över vår systemdesign och speciellt det aktörsystem vi planerade för kom vi fram till att vi skulle behöva
+ett stort antal aktörer körandes även vid ett lågt antal spelare och därmed att skalbarhet var en viktig faktor vid vårt
+val av språk. Vi kom fram till att vi skulle använda antingen Scala eller Erlang och efter en kort diskussion valde vi Scala.
 
-Scala bygger på Java, och erbjuder därför liknande syntax.
-Detta innebar att övergången mellan att skriva Java och Scala var en någorlunda mjuk sådan, koden var ganska lättigenkännlig samtidigt som vi fick fördelarna med att kunna utveckla skalbart.
-Några nackdelar med Scala som vi finner nämnvärda är exempelvis att det, trots likheter med Java, tog en viss tid att sätta sig in i det nya
-språket vilket kan ha motarbetat utvecklingen gämfört med om vi hade valt ett annat språk som vi var mer bekanta med.
+Att vi valde Scala över Erlang var dels en önskan att lära oss ett nytt språk, dels att just skalbarhet är just grundtanken
+i Scala och dels dess integrationsmöjligheter med Java och de likheter som finns mellan språken. Att lära oss skriva Scala kod
+visade sig vara en utmaning men likheterna med Java underlättade processen och vi kom snabbt igång.
 
-Genom rekommendationer av skaparna bakom Scala, beslöt vi oss för att använda Akka som vårt aktörbibliotek.
-Detta för att kunna använda Akkas TCP-bibliotek för nätverkskommunikationen.
-Bibliotekets enkla integration var en av punkterna som ledde till vårt beslut att använda Scala och Akka som val av programspråk och aktörbibliotek.
+Scala är ett multiparadigmsspråks och tillåter att program skrivs både funktionellt och objektorienterat/imperativt. Detta gav oss en stor
+fördel vid implementationen av vår design då vi kunde använda en klasshierarki för våra aktörer men samtidigt använda 
+funktionella lösningar där dessa underlättade utvecklingen.
 
-Java var det språket vi valde att använda vid skapandet av det grafiska gränssnittet som spelaren agerar mot. Vårt val grundade sig i biblioteket Swing som Java tillhandahåller. 
-Med hjälp att detta bibliotek var skapandet av det grafiska gränssnittet en relativt enkel process. Likt många andra av Javas bibliotek var dokumentationen välskriven och enkel 
-att använda vilket underlättade processen. En annan aspekt som fick oss att välja Java för just denna del var att vi ville kunna kommunicera med resterande kod, skriven i Scala, 
-på ett enkelt sätt och detta kunde uppnås utan problem då Scala är byggt utifrån Javas Virtuella Maskin.
+Dess närhet med Java var dock grund till en del av svårigheterna att vänja sig till Scala. Scala använder både egna standardbibliotek
+och Javas standardbibliotek men inte alltid helt konsekvent. Samtidigt är alla datasamlingsstrukturer i Scala \textit{oföränderliga} 
+som standard, då trådsäkerhet är fundamentalt till Scala, vilket krävde en viss vana för att användas på rätt sätt.
+
+Versionen av Scala vi valde att använda har valt att tillfrån gå sitt egna aktörsbibliotek och istället använda sig av ett externt
+bibliotek kallat Akka. Vårt projekt använder till följd även det Akkas bibliotek för implementationen av det aktörssystem som
+vår server använder. Akka som bibliotek var samtidigt både lättanvänt och svårt att sätta sig in i. Det behövdes en viss förståelse
+för hur biblioteksskaparna tänkt sig att det ska användas för att förstå den dokumentation som finns tillgänglig och det krävdes
+en del försöksprogram för att sätta sig in i just hur biblioteket fungerar. Akka tillhandahöll även en implementation av TCP/IP
+sockets vilket märkbart förenklade nätverksdelen av vår kod och med dess hjälp undkom vi vad kunde varit stor huvudbry då vi inte
+hade stor erfarenhet av nätverkskodning sen tidigare.
+
+Att Scala är byggt ovanpå Javas virtuella maskin innebar att vi lätt kunde använda Javas Swing bibliotek för att snabbt skapa
+ett grafiskt gränssnitt till den klient som kommunicerar mot vår server. Bortsett från gränssnittet använder även klienten i
+grunden Scala och Akkas TCP/IP bibliotek.
 
@@
 Vårt slutresultat är ett textbaserat multiplayer dungeon spel.
-I spelets startrum kan man chatta med de andra spelarna som är online genom \textit{WHISPER} (personligt meddelande) eller \textit{SAY} (till alla spelare i rummet).
+I spelets startrum kan man chatta med de andra spelarna som är online genom whisper (personligt meddelande) eller say (till alla spelare i rummet).
 Där kan man också forma en grupp så att man tillsammans med andra spelare kan gå ner i en dungeon och börja spela.
-Väl nere i en dungeon kan man chatta som vanligt, men man kan också plocka upp saker man hittar, gå till andra rum och slåss mot andra spelare eller NPC som är i rummet.
+Väl nere i en dungeon kan man chatta som vanligt, men man kan också plocka upp saker som man hittar i grottan, börja slåss mot en spelare eller NPC som är i rummet och man kan gå till andra rum.
 När detta sker uppdateras klienten på korrekt sätt, så att spelaren får information om vad som händer i grottan.
-
-Vi har också skapat ett administrationsverktyg som gör att man i terminalen kan ge spelare objekt, återställa hälsan så att spelaren får fullt HP\footnote{HP står för Health Points, vilket är hur mycket liv spelaren har vid givet tillfälle} och skada den genom att bestämma hur mycket HP som ska dras av (man kan inte döda en spelare).
-Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla salarna.
+Vi har också skapat en \textit{god mode} som gör att man i terminalen kan ge spelare speciella items, samt hela den så att den får fullt hp.
+Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla rum i en dungeon.
 

### 2014-05-29 doc/src/draft.tex
Added some things to the server part of the draft

--- 2014-05-29 doc/src/draft.tex
@@
 \subsubsection{Aktörmodell}
-Serverdelen är uppdelad i flera processer via Akkas aktörbibliotek för att upprätthålla Actor Concurrency-modellen .
+Serverdelen är uppdelad i flera aktörer via Akkas aktörbibliotek för att upprätthålla Actor Concurrency-modellen. 
 Två typer av aktörer kommmunicerar direkt med nätverket via TCP/IP, ConManaktören och Playeraktörerna.
@@
 PlayerMap mappar på en uppkopplad spelares användarnamn till spelarens Playeraktör.
-Genom PlayerMap kan en aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - ett viktigt kommando som agerar på följande sätt är exempelvis “WHISPER”.
+Genom PlayerMap kan en aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - ett viktigt kommando som agerar på följande sätt är exempelvis \textit{WHISPER}.
 Det är även via PlayerMap som Playeraktören ser till att samma användarnamn inte används av flera uppkopplade spelare samtidigt.
+
+Det finns även en aktör som kallas CheatActor som agerar som ett administrationsverkyg.
+Den har befogenheter som överstiger alla andra aktörer som agerar på spelet och detta med anledning till att värden för servern ska kunna administrera i spelet utan att vara i spelet.
+Aktören kan leta reda på spelaraktörer via PlayerMapAktören och därefter utföra ett antal operationer som påverkar spelaren i fråga.
+Dessa operationer består av: att skada spelare, att läka spelare, att leta efter föremål och NPCs, prata med spelare, skapa spelare och NPCs samt operationen som endast påverkar servern själv vilket är operationen för omstart av servern.
 
@@
 Dungeonaktören koordinerar också kommunikation, och händelser som påverkar spelarna som befinner sig i grottan.
-Ett exempel på detta är kommandot “SAY”  som skickar ett meddelande till alla spelare som är i samma rum som spelaren.
+Ett exempel på detta är kommandot \textit{SAY} som skickar ett meddelande till alla spelare som är i samma rum som spelaren.
 

### 2014-05-29 doc/src/draft.tex

--- 2014-05-29 doc/src/draft.tex
@@
 \subsection{Concurrency}
-Flera spelare samtidigt
-Skicka meddelanden - jobbigt när man bara vill ta reda på ett värde - skicka meddelanden fram och tillbaka. Men ingen risk för deadlock då all kommunikation sker via meddelanden. 
-Meddelanden är ej synkrona, vilket märks då en spelare ibland kan bli slagen efter att den har dött (det ser uut så i prompten eftersom meddelandena kommer så, men det är inte sant)
-För att skapa en slags synkronisering har vi använt FSM, vilket kräver att man är i en särskild state för att kunna ta emot ett särskilt meddelanden.
+Som nämnts tidigare valde vi att använda Aktörsmodellen som vår concurrencymodell därför att vi vid designen såg hur de olika
+delarna av servern kunde delas in i till stor del självständiga moduler där minne inte behövde delas. Detta underlättade
+skapandet av deadlock-säker kod men vår ovana i hur Akka biblioteket fungerade gav oss vissa svårigheter i synkronisering av
+meddelanden som skickades mellan aktörerna. Det var inte förrän sent under projektetsgång vi lyckades få Futures, ett sätt att 
+vänta på resultat från en annan aktör, att fungera på rätt sätt och i det stadiet hade vi redan skapat andra, dock ej optimala,
+lösningar på synkroniseringsproblemen. Akkas meddelandeskickning är icke garanterad, vilket innebär att meddelanden kan
+tappas, speciellt på väg från klient till server över nätverk, vilket vi inte på ett okomplicerat sätt kunde ta hänsyn till utan
+synkronisering och meddelande time-out hantering som vi inte implementerat. Dessutom är inte heller ordningsföljden av meddelanden
+garanterade, så utan någon form av tidsstämpling finns inget okomplicerat sätt att sortera meddelanden som inkommer till aktörer.
+
+Implementationen är även svårtestad, integrationstester av aktörerna krävde mer specialkunskap om Akkas bibliotek än vi
+hann skaffa oss och vi fick istället nöja oss med enhetstester av de aktörer där detta är aktuellt.
+
+Som alternativ till komplicerad synkronisering vid strider mellan spelare och monster eller enbart strid mellan spelare valde vi att
+skapa en speciell typ av aktör som använder en finit tillståndsmaskin.
+
+Vår implementation av servern skapar ett stort antal aktörer även för få klienter. Dels skapas alltid ett flertal aktörer som
+agerar som verktyg för systemet, exempelvis för att hantera inkommande anslutningar eller binda samman spelarnamn och spelaraktörer.
+Det skapas även två nya aktörer för varje nyinkommen anslutning, en aktör för varje nyskapad dungeon, en aktör för varje nystartad strid
+och en aktör för varje levande monsterkaraktär.
+Tack vare Akka och Scalas skalbarhet har vi dock inte sett något problem i detta.
 
@@
 Vårt slutresultat är ett textbaserat multiplayer dungeon spel.
-I spelets startrum kan man chatta med de andra spelarna som är online genom whisper (personligt meddelande) eller say (till alla spelare i rummet).
+I spelets startrum kan man chatta med de andra spelarna som är online genom \textit{WHISPER} (personligt meddelande) eller \textit{SAY} (till alla spelare i rummet).
 Där kan man också forma en grupp så att man tillsammans med andra spelare kan gå ner i en dungeon och börja spela.
-Väl nere i en dungeon kan man chatta som vanligt, men man kan också plocka upp saker som man hittar i grottan, börja slåss mot en spelare eller NPC som är i rummet och man kan gå till andra rum.
+Väl nere i en dungeon kan man chatta som vanligt, men man kan också plocka upp saker man hittar, gå till andra rum och slåss mot andra spelare eller NPC som är i rummet.
 När detta sker uppdateras klienten på korrekt sätt, så att spelaren får information om vad som händer i grottan.
-Vi har också skapat en \textit{god mode} som gör att man i terminalen kan ge spelare speciella items, samt hela den så att den får fullt hp.
-Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla rum i en dungeon.
+
+Vi har också skapat ett administrationsverktyg som gör att man i terminalen kan ge spelare objekt, återställa hälsan så att spelaren får fullt HP\footnote{HP står för Health Points, vilket är hur mycket liv spelaren har vid givet tillfälle} och skada den genom att bestämma hur mycket HP som ska dras av (man kan inte döda en spelare).
+Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla salarna.
 
@@
 \section{Appendix}
+\subsection{Använda externa bibliotek}
+För licensinformation angående följande bibliotek, se .license filer i projektets rotmapp.
+\begin{description}
+\item[Scala 2.10.4] \hfill \\ Copyright © 2002-2014 EPFL, Copyright (c) 2011-2014 Typesafe, Inc.\hfill \\http://scala-lang.org/
+\item[Akka 2.3.2] \hfill \\ Copyright © 2009-2014 Typesafe Inc.\hfill \\ http://akka.io/
+\item[SLF4J 1.7.7] \hfill \\ Copyright © 2004-2013 QOS.ch\hfill \\ http://www.slf4j.org/
+\item[Slick 2.0.2] \hfill \\ Copyright © 2011-2014 Typesafe, Inc.\hfill \\ http://slick.typesafe.com
+\item[SQLite JDBC 3.7.2] \hfill \\ Copyright © Taro L. Saito\hfill \\ http://bitbucket.org/xerial/sqlite-jdbc
+\end{description}
 
-Scala 2.10.4, Akka 2.3.2, SLF4J 1.7.7, Slick 2.0.2, SQLite JDBC 3.7.2
+\subsection{Tillgänglighet}
+Projektet finns tillgängligt för nedladdning på https://github.com/senilica/LostVaults/
 
-https://github.com/senilica/LostVaults/
+\subsection{Kompilering}
+Kompilering av systemet sker med hjälp av ANT, Apache's byggsystem, och är automatiserat. Byggskriptet använder följande byggmål:
+\begin{description}
+\item[build\_server] \hfill \\ Kompilerar alla serverns scalafiler.
+\item[build\_client] \hfill \\ Kompilerar alla klientens scalafiler.
+\item[build\_tools] \hfill \\ Kompilerar alla databasverktygens scalafiler samt skapar körbara \textbf{.jar} arkiv i rotmappen.
+\item[server] \hfill \\ Kompilerar alla serverns scalafiler och skapar ett körbart \textbf{server.jar} arkiv i rotmappen.
+\item[client] \hfill \\ Kompilerar alla klientens scala- och javafiler och skapar ett körbart \textbf{client.jar} arkiv i rotmappen.
+\item[clean] \hfill \\ Återställer kompilartoromgivningen och tvingar ny kompilering av all källkod.
+\item[doc] \hfill \\ Skapar html-baserad Scaladoc dokumentation av projektet.
+\item[run\_tests] \hfill \\ Kompilerar alla testens scalafiler och kör automatiska enhetstester genom Scalatest.
+\item[archive] \hfill \\ Återställer kompilatoromgivningen samt skapar .tar.gz arkiv som följer projektanvisningarnas namn och katalogstruktur.
+\item[run\_server] \hfill \\ Kompilerar alla serverns scalafiler, skapar samt kör ett körbart \textbf{server.jar} arkiv i rotmappen.
+\item[run\_server] \hfill \\ Kompilerar alla klientens scala- och javafiler, skapar samt kör ett körbart \textbf{client.jar} arkiv i rotmappen.
+\end{description}
 
-Vilka versioner av till exempel Erlang, Java, Python etc har använts?
-Hur kan koden laddas ner? Finns koden tillgänglig på till exempel GitHub eller Bitbucket eller som Tar arkiv?  Beskriv projektets katalogstruktur.
-Vilket stöd för automatiserad testning finns och hur används det, till exempel JUnit (Java), EUnint (Erlang) eller PyUnit (Python)?
-%Vilket stöd för automatiserad generering av dokumentation finns och hur används det, till exempel Doxygen (C, C++, C\#, Fortran, Java, Objective\­C, PHP, Python), EDoc (Erlang), Pydoc (Python), Javadoc (Java)?
-Hur kompileras systemet?
-Hur startas systemet? tryck på play
+\subsection{Körning}
+Körning av systemet kräver kompilering och körning av serverns och klientens java arkiv, och kan göras antingen via byggsystemet
+eller från terminal via \textit{java -jar server.jar} respektive  \textit{java -jar client.jar}.
 

### 2014-05-29 doc/src/draft.tex
Helloo cooling people ^^

--- 2014-05-29 doc/src/draft.tex
@@
 \subsubsection{Aktörmodell}
-Serverdelen är uppdelad i flera aktörer via Akkas aktörbibliotek för att upprätthålla Actor Concurrency-modellen. 
+Serverdelen är uppdelad i flera processer via Akkas aktörbibliotek för att upprätthålla Actor Concurrency-modellen .
 Två typer av aktörer kommmunicerar direkt med nätverket via TCP/IP, ConManaktören och Playeraktörerna.
@@
 PlayerMap mappar på en uppkopplad spelares användarnamn till spelarens Playeraktör.
-Genom PlayerMap kan en aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - ett viktigt kommando som agerar på följande sätt är exempelvis \textit{WHISPER}.
+Genom PlayerMap kan en aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - ett viktigt kommando som agerar på följande sätt är exempelvis “WHISPER”.
 Det är även via PlayerMap som Playeraktören ser till att samma användarnamn inte används av flera uppkopplade spelare samtidigt.
-
-Det finns även en aktör som kallas CheatActor som agerar som ett administrationsverkyg.
-Den har befogenheter som överstiger alla andra aktörer som agerar på spelet och detta med anledning till att värden för servern ska kunna administrera i spelet utan att vara i spelet.
-Aktören kan leta reda på spelaraktörer via PlayerMapAktören och därefter utföra ett antal operationer som påverkar spelaren i fråga.
-Dessa operationer består av: att skada spelare, att läka spelare, att leta efter föremål och NPCs, prata med spelare, skapa spelare och NPCs samt operationen som endast påverkar servern själv vilket är operationen för omstart av servern.
 
@@
 Dungeonaktören koordinerar också kommunikation, och händelser som påverkar spelarna som befinner sig i grottan.
-Ett exempel på detta är kommandot \textit{SAY} som skickar ett meddelande till alla spelare som är i samma rum som spelaren.
+Ett exempel på detta är kommandot “SAY”  som skickar ett meddelande till alla spelare som är i samma rum som spelaren.
 
@@
 
-En stor sak som vi inte han med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa steg skulle vara, nu när det grundläggande fungerar som det ska.
+En stor sak som vi inte hann med under projektets gång är att implementera uppdrag.
+Utan uppdrag missar spelet sitt djup, och lyckas inte fånga spelaren.
+Dessutom ska spelet ha fällor i vissa rum, för att göra färden genom grottorna farligare.
+
+Vi har arbetat med automatiserad testing medan vi har byggt upp vårt spel.
+Men på grund av aktöruppbyggnaden av vårt program har det vara svårt att göra annat än enhetstester, och dessa har endast gett ytlig testning av spelet, då mängder av olika händelseförlopp kan inträffa.
+Så för att uppväga våra brister i automatiserade tester har vi helt enkelt testkört spelet många gånger.
 

### 2014-05-29 doc/src/draft.tex

--- 2014-05-29 doc/src/draft.tex
@@
 
-En stor sak som vi inte hann med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa steg skulle vara, nu när det grundläggande fungerar som det ska.
+En stor sak som vi inte hann med under projektets gång är att implementera uppdrag.
+Utan uppdrag missar spelet sitt djup, och lyckas inte fånga spelaren.
+Dessutom ska spelet ha fällor i vissa rum, för att göra färden genom grottorna farligare.
+
+Vi har arbetat med automatiserad testing medan vi har byggt upp vårt spel.
+Men på grund av aktöruppbyggnaden av vårt program har det vara svårt att göra annat än enhetstester, och dessa har endast gett ytlig testning av spelet, då mängder av olika händelseförlopp kan inträffa.
+Så för att uppväga våra brister i automatiserade tester har vi helt enkelt testkört spelet många gånger.
 

### 2014-05-29 doc/src/draft.tex
Moved some chunks of text in the server part of the draft

--- 2014-05-29 doc/src/draft.tex
@@
 PlayerMap mappar på en uppkopplad spelares användarnamn till spelarens Playeraktör.
-Genom PlayerMap kan en aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - ett viktigt kommando som agerar på följande sätt är exempelvis “WHISPER”.
+Genom PlayerMap kan en aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - ett viktigt kommando som agerar på följande sätt är exempelvis \textit{WHISPER}.
 Det är även via PlayerMap som Playeraktören ser till att samma användarnamn inte används av flera uppkopplade spelare samtidigt.
@@
 
+Det finns även en aktör som kallas CheatActor som agerar som ett administrationsverkyg.
+Den har befogenheter som överstiger alla andra aktörer som agerar på spelet och detta med anledning till att värden för servern ska kunna administrera i spelet utan att vara i spelet.
+Aktören kan leta reda på spelaraktörer via PlayerMapAktören och därefter utföra ett antal operationer som påverkar spelaren i fråga.
+Dessa operationer består av: att skada spelare, att läka spelare, att leta efter föremål och NPCs, prata med spelare, skapa spelare och NPCs samt operationen som endast påverkar servern själv vilket är operationen för omstart av servern.
+
 De två resterande lagren av aktörer som servern använder är Dungeonlagret och Stridslagret, och det är dessa som utför spelets logik.
@@
 
-En stor sak som vi inte hann med under projektets gång är att implementera uppdrag.
-Utan uppdrag missar spelet sitt djup, och lyckas inte fånga spelaren.
-Dessutom ska spelet ha fällor i vissa rum, för att göra färden genom grottorna farligare.
-
-Vi har arbetat med automatiserad testing medan vi har byggt upp vårt spel.
-Men på grund av aktöruppbyggnaden av vårt program har det vara svårt att göra annat än enhetstester, och dessa har endast gett ytlig testning av spelet, då mängder av olika händelseförlopp kan inträffa.
-Så för att uppväga våra brister i automatiserade tester har vi helt enkelt testkört spelet många gånger.
+En stor sak som vi inte han med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa steg skulle vara, nu när det grundläggande fungerar som det ska.
 

### 2014-05-29 doc/src/draft.tex
Hello

@@
 \section{Appendix}
+\subsection{Använda externa bibliotek}
+För licensinformation angående följande bibliotek, se .license filer i projektets rotmapp.
+\begin{description}
+\item[Scala 2.10.4] \hfill \\ Copyright © 2002-2014 EPFL, Copyright (c) 2011-2014 Typesafe, Inc.\hfill \\http://scala-lang.org/
+\item[Akka 2.3.2] \hfill \\ Copyright © 2009-2014 Typesafe Inc.\hfill \\ http://akka.io/
+\item[SLF4J 1.7.7] \hfill \\ Copyright © 2004-2013 QOS.ch\hfill \\ http://www.slf4j.org/
+\item[Slick 2.0.2] \hfill \\ Copyright © 2011-2014 Typesafe, Inc.\hfill \\ http://slick.typesafe.com
+\item[SQLite JDBC 3.7.2] \hfill \\ Copyright © Taro L. Saito\hfill \\ http://bitbucket.org/xerial/sqlite-jdbc
+\end{description}
 
-Scala 2.10.4, Akka 2.3.2, SLF4J 1.7.7, Slick 2.0.2, SQLite JDBC 3.7.2
+\subsection{Tillgänglighet}
+Projektet finns tillgängligt för nedladdning på https://github.com/senilica/LostVaults/
 
-https://github.com/senilica/LostVaults/
+\subsection{Kompilering}
+Kompilering av systemet sker med hjälp av ANT, Apache's byggsystem, och är automatiserat. Byggskriptet använder följande byggmål:
+\begin{description}
+\item[build\_server] \hfill \\ Kompilerar alla serverns scalafiler.
+\item[build\_client] \hfill \\ Kompilerar alla klientens scalafiler.
+\item[build\_tools] \hfill \\ Kompilerar alla databasverktygens scalafiler samt skapar körbara \textbf{.jar} arkiv i rotmappen.
+\item[server] \hfill \\ Kompilerar alla serverns scalafiler och skapar ett körbart \textbf{server.jar} arkiv i rotmappen.
+\item[client] \hfill \\ Kompilerar alla klientens scala- och javafiler och skapar ett körbart \textbf{client.jar} arkiv i rotmappen.
+\item[clean] \hfill \\ Återställer kompilartoromgivningen och tvingar ny kompilering av all källkod.
+\item[doc] \hfill \\ Skapar html-baserad Scaladoc dokumentation av projektet.
+\item[run\_tests] \hfill \\ Kompilerar alla testens scalafiler och kör automatiska enhetstester genom Scalatest.
+\item[archive] \hfill \\ Återställer kompilatoromgivningen samt skapar .tar.gz arkiv som följer projektanvisningarnas namn och katalogstruktur.
+\item[run\_server] \hfill \\ Kompilerar alla serverns scalafiler, skapar samt kör ett körbart \textbf{server.jar} arkiv i rotmappen.
+\item[run\_client] \hfill \\ Kompilerar alla klientens scala- och javafiler, skapar samt kör ett körbart \textbf{client.jar} arkiv i rotmappen.
+\end{description}
 
-Vilka versioner av till exempel Erlang, Java, Python etc har använts?
-Hur kan koden laddas ner? Finns koden tillgänglig på till exempel GitHub eller Bitbucket eller som Tar arkiv?  Beskriv projektets katalogstruktur.
-Vilket stöd för automatiserad testning finns och hur används det, till exempel JUnit (Java), EUnint (Erlang) eller PyUnit (Python)?
-%Vilket stöd för automatiserad generering av dokumentation finns och hur används det, till exempel Doxygen (C, C++, C\#, Fortran, Java, Objective\­C, PHP, Python), EDoc (Erlang), Pydoc (Python), Javadoc (Java)?
-Hur kompileras systemet?
-Hur startas systemet? tryck på play
+\subsection{Körning}
+Körning av systemet kräver kompilering och körning av serverns och klientens java arkiv, och kan göras antingen via byggsystemet
+eller från terminal via \textit{java -jar server.jar} respektive  \textit{java -jar client.jar}.
 

### 2014-05-29 doc/src/draft.tex
Cool stuff

@@
 Aktören kan leta reda på spelaraktörer via PlayerMapAktören och därefter utföra ett antal operationer som påverkar spelaren i fråga.
-Dessa operationer består av: att skada spelare, att läka spelare, att leta efter föremål och NPCs, prata med spelare, skapa spelare och NPCs samt operationen som endast påverkar servern själv vilket är operationen för omstart av servern.
+Dessa operationer består av: att skada spelare, att läka spelare, att leta efter föremål och NPCs, ge en spelare ett föremål, sätta en NPC i en spelares rum, prata med spelare, skapa spelare och NPCs samt operationen som endast påverkar servern själv vilket är operationen för omstart av servern.
 
@@
 När en grupp bestämmer sig för att stiga in i en Dungeon skapas en ny slumpvis genererad grotta, som endast de kan komma åt.
-Grottan består av en array med rum med dörrar som spelaren kan förflytta sig emellan.
+Grottan består av en array av rum med dörrar som spelaren kan förflytta sig emellan.
 Det är i dessa rum som spelare kommer kunna göra uppdrag, finna skatter, slåss mot monster eller andra spelare etc.

### 2014-05-29 src/lostvaults/client/GUI.java
item msg

@@ -403,7 +403,7 @@ public class GUI {
 
 	public void removeItem(String item) {
 		String i = items.getText();
-		i = i.replace(item + "\n", "");
+		i = i.replaceFirst(item + "\n", "");
 		items.setText(i);
 	}
 

### 2014-05-29 src/lostvaults/server/Dungeon.scala

@@ -129,6 +129,15 @@ class Dungeon extends Actor {
         PMap ! PMapSendGameMessage(name, GameSystem(rooms(nextRoom).getDescription(name)))
         rooms(nextRoom).getPlayerList.foreach(c => if (c != name) { PMap ! PMapSendGameMessage(c, GameMessage("ROOMJOIN " + name)) })
         PMap ! PMapSendGameMessage(name, GameMessage("ROOMLIST " + rooms(nextRoom).getPlayerList.foldRight("")((pName, s) => if (pName != name) { pName + "\n" + s } else { "" + s })))
+        if(rooms(nextRoom).getItemList.isEmpty) {
+            PMap ! PMapSendGameMessage(name, GameMessage("ITEMLIST  "))
+        } else {
+          var retString = ""
+          rooms(nextRoom).getItemList.foreach(c => (retString += c.name + "\n"))
+          println(retString)
+          println(";;;;;;;;;;;;;;;;;;;;;")
+          PMap ! PMapSendGameMessage(name, GameMessage("ITEMLIST " + retString))
+        }
       } else {
         println("Cannot move player.")
         PMap ! PMapSendGameMessage(name, GameSystem("You cannot move in that direction."))
@@ -220,6 +229,7 @@ class Dungeon extends Actor {
         }
         PMap ! PMapSendGameMessage(name, GameUpdateItem(pItem))
         var msg = "ITEMLEFT " + pItem.name
+        println(msg+"--------------------------------")
         rooms(index).getPlayerList().foreach(n => (PMap ! PMapSendGameMessage(n, GameMessage(msg))))
       } else {
         PMap ! PMapSendGameMessage(name, GameMessage("No such item in the room."))

### 2014-05-29 src/lostvaults/server/Player.scala

@@ -364,7 +364,7 @@ class Player extends Actor {
           } else if (item.isPotion) {
             potions = potions + 1
           }
-          pushToNetwork("SYTEM You picked up " + item.name)
+          pushToNetwork("SYSTEM You picked up " + item.name)
         }
         case GameDamage(from, strength) => {
           var damage = strength - getDefense

### 2014-05-29 doc/src/draft.tex
Fixed draft

@@
 \subsection{Programspråk}
-För att möjliggöra massiv concurrency med många individuella aktörer har vi gjort vårt projekt i Scala.
-Scala är bra för skalbarhet, vilket innebär att vårt program kommer fungera bra oavsätt om det är tio användare online eller om det är tio tusen.
-En annan anledning till att vi valde Scala är att Scala är ett objektorienterat språk, vilket passade ihop med det tänket vi hade när vi började planera programmet.
-Vi fokuserade på att skapa objekt som interagereade på rätt sätt med varandra, snarare än att skriva kod som ska exekveras i en särskild ordning.
+Vid reflektion över vår systemdesign och speciellt det aktörsystem vi planerade för kom vi fram till att vi skulle behöva
+ett stort antal aktörer körandes även vid ett lågt antal spelare och därmed att skalbarhet var en viktig faktor vid vårt
+val av språk. Vi kom fram till att vi skulle använda antingen Scala eller Erlang och efter en kort diskussion valde vi Scala.
 
-Scala bygger på Java, och erbjuder därför liknande syntax.
-Detta innebar att övergången mellan att skriva Java och Scala var en någorlunda mjuk sådan, koden var ganska lättigenkännlig samtidigt som vi fick fördelarna med att kunna utveckla skalbart.
-Några nackdelar med Scala som vi finner nämnvärda är exempelvis att det, trots likheter med Java, tog en viss tid att sätta sig in i det nya
-språket vilket kan ha motarbetat utvecklingen gämfört med om vi hade valt ett annat språk som vi var mer bekanta med.
+Att vi valde Scala över Erlang var dels en önskan att lära oss ett nytt språk, dels att just skalbarhet är just grundtanken
+i Scala och dels dess integrationsmöjligheter med Java och de likheter som finns mellan språken. Att lära oss skriva Scala kod
+visade sig vara en utmaning men likheterna med Java underlättade processen och vi kom snabbt igång.
 
-Genom rekommendationer av skaparna bakom Scala, beslöt vi oss för att använda Akka som vårt aktörbibliotek.
-Detta för att kunna använda Akkas TCP-bibliotek för nätverkskommunikationen.
-Bibliotekets enkla integration var en av punkterna som ledde till vårt beslut att använda Scala och Akka som val av programspråk och aktörbibliotek.
+Scala är ett multiparadigmsspråks och tillåter att program skrivs både funktionellt och objektorienterat/imperativt. Detta gav oss en stor
+fördel vid implementationen av vår design då vi kunde använda en klasshierarki för våra aktörer men samtidigt använda 
+funktionella lösningar där dessa underlättade utvecklingen.
 
-Java var det språket vi valde att använda vid skapandet av det grafiska gränssnittet som spelaren agerar mot. Vårt val grundade sig i biblioteket Swing som Java tillhandahåller. 
-Med hjälp att detta bibliotek var skapandet av det grafiska gränssnittet en relativt enkel process. Likt många andra av Javas bibliotek var dokumentationen välskriven och enkel 
-att använda vilket underlättade processen. En annan aspekt som fick oss att välja Java för just denna del var att vi ville kunna kommunicera med resterande kod, skriven i Scala, 
-på ett enkelt sätt och detta kunde uppnås utan problem då Scala är byggt utifrån Javas Virtuella Maskin.
+Dess närhet med Java var dock grund till en del av svårigheterna att vänja sig till Scala. Scala använder både egna standardbibliotek
+och Javas standardbibliotek men inte alltid helt konsekvent. Samtidigt är alla datasamlingsstrukturer i Scala \textit{oföränderliga} 
+som standard, då trådsäkerhet är fundamentalt till Scala, vilket krävde en viss vana för att användas på rätt sätt.
 
+Versionen av Scala vi valde att använda har valt att tillfrån gå sitt egna aktörsbibliotek och istället använda sig av ett externt
+bibliotek kallat Akka. Vårt projekt använder till följd även det Akkas bibliotek för implementationen av det aktörssystem som
+vår server använder. Akka som bibliotek var samtidigt både lättanvänt och svårt att sätta sig in i. Det behövdes en viss förståelse
+för hur biblioteksskaparna tänkt sig att det ska användas för att förstå den dokumentation som finns tillgänglig och det krävdes
+en del försöksprogram för att sätta sig in i just hur biblioteket fungerar. Akka tillhandahöll även en implementation av TCP/IP
+sockets vilket märkbart förenklade nätverksdelen av vår kod och med dess hjälp undkom vi vad kunde varit stor huvudbry då vi inte
+hade stor erfarenhet av nätverkskodning sen tidigare.
+
+Att Scala är byggt ovanpå Javas virtuella maskin innebar att vi lätt kunde använda Javas Swing bibliotek för att snabbt skapa
+ett grafiskt gränssnitt till den klient som kommunicerar mot vår server. Bortsett från gränssnittet använder även klienten i
+grunden Scala och Akkas TCP/IP bibliotek.
 \subsection{Algoritmer}
-För att spelarna alltid skall få  nya och intressanta upplevelser bestämde vi oss för att skriva en algoritm för slumpmässig generering av rum som spelarna kan utforska. Vi
-bestämde oss för att nyttja ett rutnät där varje cell representerar ett rum. Spelare kan ta sig från rum till rum via utgångar placerade på några av eller alla rummens fyra väggar.
-Vår algoritm skall även säkerställa att inga rum skapas som inte går att nå från ingången.
-Nedan beskrivs med pseudokod den algoritm vi bestämde oss för att använda.
+Vår algoritm skall även säkerställa att inga rum skapas som inte går att nå från ingången. Algoritm \ref{alg:RoomGen} beskriver med pseudokod den algoritm vi bestämde oss för att använda.
+
 I kort fungerar algoritmen så att först slumpas koordinaterna till ett rum som blir startrummet.
-Därefter slumpas koordinaterna till ett annat rum varefter programmet går i slumpad riktning från det nya rummet till angränsande rum, samtidigt som nya rum skapas i varje ny besökt koordinatruta, tills det nya rummet har fått en anknytning till startrummet.
+Därefter slumpas koordinaterna till ett annat rum varefter programmet går i slumpad riktning från det nya rummet 
+till angränsande rum, samtidigt som nya rum skapas i varje ny besökt koordinatruta, tills det nya rummet har fått 
+en anknytning till startrummet.
 \begin{algorithm}
@@
 \subsection{Datastrukturer}
+Under projektets gång har vi använt oss av Scalas standarbibliotek för datastrukturer där vi behövt använda datasamlingar.
+
+Förutom arräer och listor har vi använt oss av Hashmap för att kunna koppla spelarnamn med aktörer och spelargrupper, vilket ses i klasserna
+PlayerMap och GroupMap.
 
 \subsection{Concurrency}
-Flera spelare samtidigt
-Skicka meddelanden - jobbigt när man bara vill ta reda på ett värde - skicka meddelanden fram och tillbaka. Men ingen risk för deadlock då all kommunikation sker via meddelanden. 
-Meddelanden är ej synkrona, vilket märks då en spelare ibland kan bli slagen efter att den har dött (det ser uut så i prompten eftersom meddelandena kommer så, men det är inte sant)
-För att skapa en slags synkronisering har vi använt FSM, vilket kräver att man är i en särskild state för att kunna ta emot ett särskilt meddelanden.
+Som nämnts tidigare valde vi att använda Aktörsmodellen som vår concurrencymodell därför att vi vid designen såg hur de olika
+
+delarna av servern kunde delas in i till stor del självständiga moduler där minne inte behövde delas. Detta underlättade
+skapandet av deadlock-säker kod men vår ovana i hur Akka biblioteket fungerade gav oss vissa svårigheter i synkronisering av
+meddelanden som skickades mellan aktörerna. Det var inte förrän sent under projektets gång som vi lyckades få Futures, ett sätt att 
+vänta på resultat från en annan aktör, att fungera på rätt sätt och i det stadiet hade vi redan skapat andra, dock ej optimala,
+lösningar på synkroniseringsproblemen.
+
+Akkas meddelandeskickning är även icke garanterad, vilket innebär att meddelanden kan
+tappas, speciellt på väg från klient till server över nätverk, vilket vi inte på ett okomplicerat sätt kunde ta hänsyn till utan
+synkronisering och meddelande time-out hantering som vi inte implementerat. Dessutom är inte heller ordningsföljden av meddelanden
+garanterade, så utan någon form av tidsstämpling finns inget okomplicerat sätt att sortera meddelanden som inkommer till aktörer.
+
+Implementationen visade sig vara svårtestad, integrationstester av aktörerna krävde mer specialkunskap om Akkas bibliotek än vi
+hann skaffa oss och vi fick istället nöja oss med enhetstester av de aktörer där detta är aktuellt.
+
+Som alternativ till komplicerad synkronisering vid strider mellan spelare och monster eller enbart strid mellan spelare valde vi att 
+skapa en speciell typ av aktör som använder en finit tillståndsmaskin.
+
+Vår implementation av servern skapar ett stort antal aktörer även för få klienter. Dels skapas alltid ett flertal aktörer som
+agerar som verktyg för systemet, exempelvis för att hantera inkommande anslutningar eller binda samman spelarnamn och spelaraktörer.
+
+Det skapas även två nya aktörer för varje nyinkommen anslutning, en aktör för varje nyskapad dungeon, en aktör för varje
+nystartad strid och en aktör för varje levande monsterkaraktär.
+
+Tack vare Akka och Scalas skalbarhet har vi dock inte sett något problem i detta.
 

### 2014-05-29 doc/src/draft.tex

--- 2014-05-29 doc/src/draft.tex
@@
 PlayerMap mappar på en uppkopplad spelares användarnamn till spelarens Playeraktör.
-Genom PlayerMap kan en aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - ett viktigt kommando som agerar på följande sätt är exempelvis \textit{WHISPER}.
+Genom PlayerMap kan en aktör snabbt och enkelt skicka meddelanden till en specifik spelare baserat på dess namn - ett viktigt kommando som agerar på följande sätt är exempelvis “WHISPER”.
 Det är även via PlayerMap som Playeraktören ser till att samma användarnamn inte används av flera uppkopplade spelare samtidigt.
@@
 
-Det finns även en aktör som kallas CheatActor som agerar som ett administrationsverkyg.
-Den har befogenheter som överstiger alla andra aktörer som agerar på spelet och detta med anledning till att värden för servern ska kunna administrera i spelet utan att vara i spelet.
-Aktören kan leta reda på spelaraktörer via PlayerMapAktören och därefter utföra ett antal operationer som påverkar spelaren i fråga.
-Dessa operationer består av: att skada spelare, att läka spelare, att leta efter föremål och NPCs, prata med spelare, skapa spelare och NPCs samt operationen som endast påverkar servern själv vilket är operationen för omstart av servern.
-
 De två resterande lagren av aktörer som servern använder är Dungeonlagret och Stridslagret, och det är dessa som utför spelets logik.
@@
 \section{Appendix}
-\subsection{Använda externa bibliotek}
-För licensinformation angående följande bibliotek, se .license filer i projektets rotmapp.
-\begin{description}
-\item[Scala 2.10.4] \hfill \\ Copyright © 2002-2014 EPFL, Copyright (c) 2011-2014 Typesafe, Inc.\hfill \\http://scala-lang.org/
-\item[Akka 2.3.2] \hfill \\ Copyright © 2009-2014 Typesafe Inc.\hfill \\ http://akka.io/
-\item[SLF4J 1.7.7] \hfill \\ Copyright © 2004-2013 QOS.ch\hfill \\ http://www.slf4j.org/
-\item[Slick 2.0.2] \hfill \\ Copyright © 2011-2014 Typesafe, Inc.\hfill \\ http://slick.typesafe.com
-\item[SQLite JDBC 3.7.2] \hfill \\ Copyright © Taro L. Saito\hfill \\ http://bitbucket.org/xerial/sqlite-jdbc
-\end{description}
 
-\subsection{Tillgänglighet}
-Projektet finns tillgängligt för nedladdning på https://github.com/senilica/LostVaults/
+Scala 2.10.4, Akka 2.3.2, SLF4J 1.7.7, Slick 2.0.2, SQLite JDBC 3.7.2
 
-\subsection{Kompilering}
-Kompilering av systemet sker med hjälp av ANT, Apache's byggsystem, och är automatiserat. Byggskriptet använder följande byggmål:
-\begin{description}
-\item[build\_server] \hfill \\ Kompilerar alla serverns scalafiler.
-\item[build\_client] \hfill \\ Kompilerar alla klientens scalafiler.
-\item[build\_tools] \hfill \\ Kompilerar alla databasverktygens scalafiler samt skapar körbara \textbf{.jar} arkiv i rotmappen.
-\item[server] \hfill \\ Kompilerar alla serverns scalafiler och skapar ett körbart \textbf{server.jar} arkiv i rotmappen.
-\item[client] \hfill \\ Kompilerar alla klientens scala- och javafiler och skapar ett körbart \textbf{client.jar} arkiv i rotmappen.
-\item[clean] \hfill \\ Återställer kompilartoromgivningen och tvingar ny kompilering av all källkod.
-\item[doc] \hfill \\ Skapar html-baserad Scaladoc dokumentation av projektet.
-\item[run\_tests] \hfill \\ Kompilerar alla testens scalafiler och kör automatiska enhetstester genom Scalatest.
-\item[archive] \hfill \\ Återställer kompilatoromgivningen samt skapar .tar.gz arkiv som följer projektanvisningarnas namn och katalogstruktur.
-\item[run\_server] \hfill \\ Kompilerar alla serverns scalafiler, skapar samt kör ett körbart \textbf{server.jar} arkiv i rotmappen.
-\item[run\_client] \hfill \\ Kompilerar alla klientens scala- och javafiler, skapar samt kör ett körbart \textbf{client.jar} arkiv i rotmappen.
-\end{description}
+https://github.com/senilica/LostVaults/
 
-\subsection{Körning}
-Körning av systemet kräver kompilering och körning av serverns och klientens java arkiv, och kan göras antingen via byggsystemet
-eller från terminal via \textit{java -jar server.jar} respektive  \textit{java -jar client.jar}.
+Vilka versioner av till exempel Erlang, Java, Python etc har använts?
+Hur kan koden laddas ner? Finns koden tillgänglig på till exempel GitHub eller Bitbucket eller som Tar arkiv?  Beskriv projektets katalogstruktur.
+Vilket stöd för automatiserad testning finns och hur används det, till exempel JUnit (Java), EUnint (Erlang) eller PyUnit (Python)?
+%Vilket stöd för automatiserad generering av dokumentation finns och hur används det, till exempel Doxygen (C, C++, C\#, Fortran, Java, Objective\­C, PHP, Python), EDoc (Erlang), Pydoc (Python), Javadoc (Java)?
+Hur kompileras systemet?
+Hur startas systemet? tryck på play
 

### 2014-05-29 doc/src/networkmessages.tex

\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{appendix}
\usepackage{longtable}
\begin{document}
\section{Network Messages}\label{app:NetworkMessages}
List of network messages sent and received by the client/server
\begin{longtable}{|l|c|p{8 cm}|}
\hline
Message & Direction & Description\\
\hline
\endhead
\textit{SAY [msg]} & Client $\rightarrow$ Server & Chat message sent from client to server.\\
\hline
\textit{SAY [name] [msg]} & Client $\leftarrow$ Server & The Chat message sent by [name] and relayed to the relevant clients.\\
\hline
\textit{WHISPER [to] [msg]} & Client $\rightarrow$ Server & A private message sent from a player to another player named [to].\\
\hline
\textit{WHISPER [from] [to] [msg]} & Client $\leftarrow$ Server & A private message sent from a player named [from], to another player named [to].\\
\hline
\textit{LOGIN [name]} & Client $\rightarrow$ Server & A request to sign onto the server using [name] as the player's username.\\
\hline
\textit{LOGOUT} & Client $\rightarrow$ Server & A Request to sign out of the server.\\
\hline
\textit{LOGINOK} & Client $\leftarrow$ Server & Response from server that a login request has been accepted.\\
\hline
\textit{LOGINFAIL} & Client $\leftarrow$ Server & Response from server that a login request has been denied.\\
\hline
\textit{BYE} & Client $\leftarrow$ Server & Connection Closed message sent from server to client.\\
\hline
\textit{SYSTEM} & Client $\leftarrow$ Server & System mesage sent from the server to the client.\\
\hline
\textit{INVENTORY} & Client $\rightarrow$ Server & Request from a client to list a player's current inventory.\\
\hline
\textit{INVENTORY [list]} & Client $\leftarrow$ Server & Response to a client's inventory request. [list] is a comma delimited list of item names.\\
\hline
\textit{ROOMENTER [name]} & Client $\leftarrow$ Server & Notification that a player named [name] has entered the room which the client receiving the message is in.\\
\hline
\textit{ROOMLEAVE [name]} & Client $\leftarrow$ Server & Notification that a player named [name] has left the room which the client receiving the message is in.\\
\hline
\textit{ROOMLIST [list]} & Client $\leftarrow$ Server & Notification that the list of players in the client's current room should be repopulated. [list] is a newline-delimited list of names.\\
\hline
\textit{NPCLIST [list]}  & Client $\leftarrow$ Server & Notification that the list of NPCs should be updated. [list] is a newline-delimited list of NPC names.\\
\hline
\textit{ROOMITEMS [list]} & Client $\leftarrow$ Server & Notification of all the items in the current room. [list] is a newline- delimited list of all the items in the room.\\
\hline
\textit{ROOMDESC [description} & Client $\leftarrow$ Server & Notification of the client's current room's description.\\
\hline
\textit{ROOMEXITS [list]} & Client $\leftarrow$ Server & Notification of all possible exits from the client's current room.\\
\hline
\textit{ROOMPLAYERS} & Client $\rightarrow$ Server & Request for a list of players in the client's current room.\\
\hline
\textit{DUNGEONPLAYERS} & Client $\rightarrow$ Server & Request for a list of players in the client's current dungeon.\\
\hline
\textit{ROOMNPCS} & Client $\rightarrow$ Server & Request for a list of NPCs in the client's current room.\\
\hline
\textit{DESCRIBE} & Client $\rightarrow$ Server & Request for a room description of the client's current room.\\
\hline
\textit{ITEMS} & Client $\rightarrow$ Server & Request for a list of items in the client's current room.\\
\hline
\textit{EXITS} & Client $\rightarrow$ Server & Request for a list of exits in the client's current room.\\
\hline
\textit{HELP} & Client $\rightarrow$ Server & Request for a list of available commands and their descriptions.\\
\hline
\textit{DUNGEONENTER [name]} & Client $\leftarrow$ Server & Notification that a player named [name] has entered the same dungeon the client is currently in.\\
\hline
\textit{DUNGEONLEAVE [name]} & Client $\leftarrow$ Server & Notification that a player named [name] has left the room which the client receiving the message is in.\\
\hline
\textit{DUNGEONLIST [list]} & Client $\leftarrow$ Server & Notification that the list of players in the client's current room should be repopulated. [list] is a newline-delimited list of names.\\
\hline
\end{longtable}
\end{document}

### 2014-05-29 src/lostvaults/server/Dungeon.scala
manny meseeges

@@ -48,7 +48,7 @@ class Dungeon extends Actor {
         }
       }
       if (matches == 0) // Check the reverse as well.
-        for (i <- str2.length until 0 by -1)
+        for (i <- (str1.length - 1) to 0 by -1)
           if (str1(i).toString().compareToIgnoreCase(str2(i).toString()) == 0) {
             matches += 1
           }
@@ -106,6 +106,7 @@ class Dungeon extends Actor {
       rooms(entrance).addPlayer(name)
       PMap ! PMapSendGameMessage(name, GameDungeonMove(entrance, true))
       PMap ! PMapSendGameMessage(name, GameSystem(rooms(entrance).getDescription(name)))
+      PMap ! PMapSendGameMessage(name, GameMessage("ROOMEXITS " + rooms(entrance).getExitsString + " City"))
     }
 
     case GamePlayerMove(name, dir, index) => {
@@ -149,8 +150,8 @@ class Dungeon extends Actor {
         PMap ! PMapSendGameMessage(name, GameSystem(rooms(nextRoom).getDescription(name)))
         rooms(nextRoom).getPlayerList.foreach(c => if (c != name) { PMap ! PMapSendGameMessage(c, GameMessage("ROOMJOIN " + name)) })
         PMap ! PMapSendGameMessage(name, GameMessage("ROOMLIST " + rooms(nextRoom).getPlayerList.foldRight("")((pName, s) => if (pName != name) { pName + "\n" + s } else { "" + s })))
-        if(rooms(nextRoom).getItemList.isEmpty) {
-            PMap ! PMapSendGameMessage(name, GameMessage("ITEMLIST  "))
+        if (rooms(nextRoom).getItemList.isEmpty) {
+          PMap ! PMapSendGameMessage(name, GameMessage("ITEMLIST  "))
         } else {
           var retString = ""
           rooms(nextRoom).getItemList.foreach(c => (retString += c.name + "\n"))
@@ -279,7 +280,9 @@ class Dungeon extends Actor {
       if (items.isEmpty) {
         PMap ! PMapSendGameMessage(name, GameMessage("There are no items in this rooms to pick up."))
       } else {
+        println("kkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkk")
         items foreach (it => { itemMatch = (compareStrings(item, it.name), i) :: itemMatch; i += 1 })
[…]

### 2014-05-29 doc/src/draft.tex

--- 2014-05-29 doc/src/draft.tex
@@
 \subsection{Algoritmer}
+För att spelarna alltid skall få  nya och intressanta upplevelser bestämde vi oss för att skriva en algoritm för slumpmässig generering av rum som spelarna kan utforska. Vi
+bestämde oss för att nyttja ett rutnät där varje cell representerar ett rum. Spelare kan ta sig från rum till rum via utgångar placerade på några av eller alla rummens fyra väggar.
+
 Vår algoritm skall även säkerställa att inga rum skapas som inte går att nå från ingången. Algoritm \ref{alg:RoomGen} beskriver med pseudokod den algoritm vi bestämde oss för att använda.

### 2014-05-29 src/lostvaults/server/Dungeon.scala
klart? :(

@@ -106,7 +106,7 @@ class Dungeon extends Actor {
       rooms(entrance).addPlayer(name)
       PMap ! PMapSendGameMessage(name, GameDungeonMove(entrance, true))
       PMap ! PMapSendGameMessage(name, GameSystem(rooms(entrance).getDescription(name)))
-      PMap ! PMapSendGameMessage(name, GameMessage("ROOMEXITS " + rooms(entrance).getExitsString + " City"))
+      PMap ! PMapSendGameMessage(name, GameMessage("ROOMEXITS " + rooms(entrance).getExitsString))
     }
 
     case GamePlayerMove(name, dir, index) => {

### 2014-05-29 src/lostvaults/server/Room.scala

@@ -66,7 +66,10 @@ class Room() {
       s = s + "South "
     }
     if (exits(3)) {
-      s = s + "West"
+      s = s + "West "
+    }
+    if (startRoom) {
+      s = s + "City"
     }
     s
   }

### 2014-06-03 doc/src/review.tex
Added Peer Review

\documentclass[a4paper]{article}
\usepackage[swedish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png}

\title{Mandelpool\\\small{Operativsystem och Multicoreprogrammering (1DT089) våren 2014. Peer review på grupp 20 genomförd av grupp 04}}

\author{Felix Färjsjö\\(19911225-4678) \and Jimmy Holm\\(19870928-0138) \and Fredrik Larsson\\(19890422-0590) \and Anna Nilsson\\(19910804-0628) \and Philip Åkerfeldt\\(19920508-1335)}

\date{\today\\Version 1.0}

\begin{document}
\maketitle
\newpage

\section{Helhetsintryck}
När vi läste igenom grupp 20:s rapportutkast var det första vi märkte att den inte var i närheten av en färdig rapport. Det var många strukturella och formmässiga fel, flertalet avsnitt var
inte färdigskrivna och tillsynes ej genomlästa av gruppen själv innan inlämning. Vi fick känslan att de olika avsnitten hade klistrats samman utan hänsyn till övriga avsnitt, då språkbruket
var överlag väldigt inkonsekvent. Det fanns flertalet språkliga fel, såsom felaktig användning av bindestreck, och stavfel, vilket vi diskuterar vidare senare i denna review. Mycket av
innehållet i rapporten var god och informativ men dispositionen och de språkliga felen gjorde det svårt att ta till sig av den.

Avsnittet för implementationen av trådpoolen och Mandelbrotuträknaren innehåller god, väl utvald och relevant information men är något kort. Djupare diskussion av implementationen skulle vara
till fördel då det är detta som bör vara fokus för rapporten då en diskussion om implementationen är en diskussion om problemlösningen som föreslagits, och ge bättre insikt i vad som gör detta
en trådpool en bra lösning.

Inledningens innehåll är mestadels välskriven, informativ och intressant dock saknas själva inledningen. Det vill säga det saknas en introduktion till problemet som söks att lösa, utan går
direkt in på en beskrivning av lösningen som föreslås i rapporten, trådpoolen, och det förslagsproblem som lösningen ska appliceras på, Mandelbrotsmängden. Beskrivningen av Mandelbrotmängden
är utförlig och på god nivå men trådpoolen beskrivs endast ytligt och utan motivering till varför en trådpool är ett bra lösningsförslag till det problem som den ska appliceras på.

\section{Struktur och disposition}
Överlag följer rapporten den givna strukturen bortsett från ett stort problem, avsnittet Slutsats. Slutsatsavsnittet i rapporten innehåller inte slutsater utan är en resultat och analys
av trådpoolens prestanda. Det finns ingen reflektion eller återkoppling i slutsatsen utan bara ny information och dess analys.

I övrigt är styckesindelningen god, texten flyter väl bortsett från vissa språkliga fel, men innehållet i sig är väl motiverat för det mesta. Som sagt tidigare saknas dock en faktisk slutsats,
det finns ingen avslutning utan texten tar slut med en icke färdigskriven lista av möjliga förbättringar.

Dispositionen inom avsnitten är bra men sammanhållningen mellan avsnitt är dock inte lika bra. Texten har mycket inkonsekvent språkbruk och vid läsning ser det ut som om de olika avsnitten
var skrivna separat och sedan ihopsatta utan att se till att de stilistikt och språkligt håller ihop. Detta leder till att det blir svårt att följa någon röd tråd i hur rapporten är
upplagd.

Rapporten behöver korrekturläsning för att sammanfoga de olika avsnitten och förena dessa.

\section{Språk och formattering}
Då rapporten tillsynes inte har undergått korrekturläsning innehåller den ett stort antal språkliga fel. Det största felet är brist på konsekvent användning av uttryck, exempelvis finnes
tre olika bestämda former av GUI: GUI:et, GUIet och GUI:t. Det finns många stavfel och många ord sammanskrivs felaktigt med bindestreck, exempelvis Mandelbrot-mängd istället för Mandelbrotmängd
och det finns ingen konsekvent användning av engelska respektive svenska ord och uttryck. Exempelvis används jobb och task godtyckligt. Det skulle ligga till fördel att bestämma sig för att
använda ett av dessa ord och sedan hålla sig till det genom hela rapporten.

Fackuttryck används på rätt sätt, förutom vissa små problem exempelvis ska API och OS skrivas med stora bokstäver och ``svengelska'' bör undvikas där det är möjligt. Exempelvis bör jobbkö användas
över taskkö. Vidare bör Mandelbrotmängden skrivas med stor bokstav, då det är en namngiven mängd.

Språket i rapporten känns för löst för en akademisk rapport. Den innehåller många talspråkiga uttryck vilket får den att kännas mindre proffesionell. Exempelvis introduceras avsnittet om
förbättringar med att ``till och med solen har sina fläckar'' vilket ger ett oseriöst intryck.

\section{Sammanfattning och slutsats}
Mycket av de fel som vi stötte på är enkla språkfel som lätt skulle kunna åtgärdas genom korrekturläsning av dokumentet och bättre sammanfogning av de olika avsnitten. Det syns tydligt att
de olika delarna skrevs av olika personer då det är mycket inkonsekvent språkbruk vilket korrekturläsning som sagt skulle kunna åtgärda. Vidare är det svårt att ge vad som känns som relevant
kritik då detta endast var ett grovutkast av rapporten. Mycket text ser ut att saknas, avsnitt är ofärdiga med kommentarer som ``Vidare utveckling i slutrapporten'' och ``Adam förklarar varför
work stealing skulle leda till en snabbare thread pool''. Det saknas sidnumrering, sidhänvisningar i innehållsförteckning, texten är inte marginaljusterad och liknande formateringsfel. Men
då rapporten är uppenbart ofärdig är det troligen en följd av att slutdisposition inte skett.

En följd av att rapporten är ofärdig är att vi känner att vår kritik tappar tyngd. Mycket av meningen med en kritisk review förloras då vi istället måste agera korrekturläsare snarare
än ge kritik på innehåll och struktur. Som ett grovt utkast är dessa problem små men som slutgiltigt utkast blir de genast väldigt stora, då de bryter mot stil, form och inte
uppfyller den mall som gavs.
\end{document}

### 2014-06-03 src/lostvaults/server/Dungeon.scala
Update Dungeon.scala

@@ -298,7 +298,7 @@ class Dungeon extends Actor {
           } else if (pItem.isArmor) {
             rooms(index).addItem(ItemRepo.getById(currentArmor))
             rooms(index).getPlayerList().foreach(n =>
-              (PMap ! PMapSendGameMessage(n, GameMessage("TEMJOIN " + ItemRepo.getById(currentArmor).name))))
+              (PMap ! PMapSendGameMessage(n, GameMessage("ITEMJOIN " + ItemRepo.getById(currentArmor).name))))
 
           }
           PMap ! PMapSendGameMessage(name, GameUpdateItem(pItem))

### 2014-06-03 src/lostvaults/server/Combat.scala
Combat takes arguments

@@ -79,6 +79,9 @@ case class RestData(PlayerList: List[Tuple3[String, Int, ActorRef]], Duration: I
  * @param CombatsPerPlayer A list with all players in combat, and with each player a list of that player's enemies, element in list looks like: Tuple2(name, List(name of players))
  */
 case class ActionData(PlayerList: List[Tuple3[String, Int, ActorRef]], TurnList: List[String], Duration: Int, CombatsPerPlayer: List[Tuple2[String, List[String]]]) extends CombatData
+
+
+
 object Combat {
   def props(dungeon: ActorRef, roomIndex: Int): Props = Props(new Combat(dungeon: ActorRef, roomIndex: Int))
 }
@@ -172,7 +175,7 @@ class Combat (_dungeon: ActorRef, _roomIndex: Int) extends Actor with FSM[Combat
 
   when(Action) {
     case Event(AttackPlayer(name, target, strength), data: ActionData) => {
-      println("COMBAT: AttackPlayer received")
+      println("COMBAT: AttackPlayer received attacking " + target)
       val turnPlayer = data.TurnList.head
       if (data.PlayerList.exists(c => c._1.compareToIgnoreCase(target) == 0)) {
         println("COMBAT: Target exists")

### 2014-06-03 src/lostvaults/server/Dungeon.scala

@@ -201,7 +201,6 @@ class Dungeon extends Actor {
         val npcs = rooms(findRoom(attacker)).NPCList
         npcs foreach (name => {
           nameMatches = (compareStrings(attackee, name._1), name._1) :: nameMatches
-          println(compareStrings(attackee, name._1))
         })
         if (nameMatches isEmpty)
           PMap ! PMapSendGameMessage(attacker, GameMessage("There is no one with that name to attack."))
@@ -218,8 +217,8 @@ class Dungeon extends Actor {
           if (rooms(currentRoom).hasPlayer(attackee)) {
             println(attacker + " attacks player " + attackee)
             if (rooms(currentRoom).activeCombat == None) {
-              println("New combat actor created.")
-              rooms(currentRoom).activeCombat = Some(context.actorOf(Props[Combat]))
+              println("New combat actor created - attackee == Player")
+              rooms(currentRoom).activeCombat = Some(context.actorOf(Combat.props(self, currentRoom)))
               rooms(currentRoom).activeCombat.get ! self
             }
             println("Adding " + attackee + " to combat")
@@ -231,8 +230,8 @@ class Dungeon extends Actor {
           } else if (rooms(currentRoom).hasNPC(attackee)) {
             println(attacker + " attacks player " + attackee)
             if (rooms(currentRoom).activeCombat == None) {
-              println("New combat actor created.")
-              rooms(currentRoom).activeCombat = Some(context.actorOf(Props[Combat]))
+              println("New combat actor created - attackee == Monster")
+              rooms(currentRoom).activeCombat = Some(context.actorOf(Combat.props(self, currentRoom)))
               rooms(currentRoom).activeCombat.get ! self
             }
             println("Adding " + attackee + " to combat")

### 2014-06-03 src/lostvaults/server/NPC.scala

@@ -35,14 +35,14 @@ class NPC(_name: String, _hp: Int, _rating: Int, _dungeon: ActorRef, _room: Int)
   }
 
   def receive = {
-    case GamePlayerJoinBattle(_battle, enemy) => {
-      println("NPC: GamePlayerJoinBattle received")
+    case GamePlayerJoinBattle(_battle, enemy) => {      
+      println("NPC: GamePlayerJoinBattle received, target is \"" + target + "\"")
       battle = Some(_battle)
       _battle ! AddPlayer(self, name, getSpeed, enemy)
       target = enemy
     }
     case GameYourTurn => {
-      println("NPC: GameYourTurn received")
+      println("NPC: GameYourTurn received attacking \"" + target + "\"")
       if (battle != None) {
         battle.get ! AttackPlayer(name, target, getAttack)
       }

### 2014-06-03 src/lostvaults/server/RoomGenerator.scala

@@ -61,7 +61,7 @@ class RoomGenerator {
   }
   def addNPCToRoom(system: ActorSystem, dungeon: ActorRef, X: Int, Y: Int) {
     if (X != startRoom._1 || Y != startRoom._2) {
-      var howMany = rand(0, 1)
+      var howMany = rand(1, 2)
       var range = (((((startRoom._1 - X).abs.asInstanceOf[Double] + (startRoom._2 - Y).abs.asInstanceOf[Double])) / 16.0) * 10.0).ceil.asInstanceOf[Int] - 1
       if (range == 0) range = 1
       println("ROOMGENERATOR-addNPCToRoom: This is the range: " + range)

### 2014-06-03 src/lostvaults/server/Combat.scala
--

@@ -80,13 +80,14 @@ case class RestData(PlayerList: List[Tuple3[String, Int, ActorRef]], Duration: I
  */
 case class ActionData(PlayerList: List[Tuple3[String, Int, ActorRef]], TurnList: List[String], Duration: Int, CombatsPerPlayer: List[Tuple2[String, List[String]]]) extends CombatData
 object Combat {
-  def props(dungeon: ActorRef, roomIndex: Int): Props = Props(new Combat(dungeon: ActorRef, roomIndex: Int))
+  def props(dungeon: ActorRef, roomIndex: Int, id: Int): Props = Props(new Combat(dungeon: ActorRef, roomIndex: Int, id:Int))
 }
 
 
-class Combat (_dungeon: ActorRef, _roomIndex: Int) extends Actor with FSM[CombatState, CombatData] {
+class Combat (_dungeon: ActorRef, _roomIndex: Int, id: Int) extends Actor with FSM[CombatState, CombatData] {
   var dungeon = _dungeon
   var roomIndex = _roomIndex
+  var myID = id
 
   
   startWith(Rest, RestData(List(), 0, List()))
@@ -97,18 +98,18 @@ class Combat (_dungeon: ActorRef, _roomIndex: Int) extends Actor with FSM[Combat
       var nextTurnList: List[String] = List()
       data.PlayerList.foreach(c => if (nextDuration % c._2 == 0) nextTurnList = c._1 :: nextTurnList)
       if (nextTurnList isEmpty) {
-        println("COMBAT-Rest: New round, no player up for their turn.")
+        println("(Combat " + myID + ") COMBAT-Rest: New round, no player up for their turn.")
         stay using RestData(data.PlayerList, nextDuration, data.CombatsPerPlayer)
       } else {
-        println("COMBAT-Rest: New round, players " + nextTurnList + " up for their turn.")
+        println("(Combat " + myID + ") COMBAT-Rest: New round, players " + nextTurnList + " up for their turn.")
         val nextPlayer = nextTurnList.head
-        println("COMBAT-Rest: It's " + nextPlayer + "'s turn to take an action.")
+        println("(Combat " + myID + ") COMBAT-Rest: It's " + nextPlayer + "'s turn to take an action.")
         combatSendGameMsg(nextPlayer, data.PlayerList, GameYourTurn)
         goto(Action) using ActionData(data.PlayerList, nextTurnList, nextDuration, data.CombatsPerPlayer)
       }
     }
[…]

### 2014-06-03 src/lostvaults/server/Dungeon.scala

@@ -10,13 +10,18 @@ import lostvaults.Parser
 case object DungeonMakeCity
 
 case object NewDungeon
+
+object Dungeon {
+  def props(id: Int): Props = Props(new Dungeon(id))
+}
+
 /**
  * Dungeon is an actor class in charge of carrying the Main logic of the game,
  *  either as a dungeon or as the special-case City actor. The dungeon allows for
  *  interaction between players, such as chatting etc, while making sure that
  *  players who are not in the same logical space cannot interact with each other.
  */
-class Dungeon extends Actor {
+class Dungeon(id: Int) extends Actor {
   import context.become
   import scala.collection.mutable.Set
   var PSet: Set[String] = Set()
@@ -25,7 +30,9 @@ class Dungeon extends Actor {
   var rooms: Array[Room] = Array()
   var entrance: Int = 0
   val gen = new RoomGenerator
-
+  var myID = id
+  var nextID = id + 1
+  var nextCombat = 1
   def indexToCoords(index: Int): (Int, Int) = {
     (index % gen.Width, index / gen.Width)
   }
@@ -75,7 +82,7 @@ class Dungeon extends Actor {
     case NewDungeon => {
       entrance = gen.coordToIndex(gen.startRoom)
       rooms = gen.generateDungeon(context.system, self)
-      println("New dungeon generated!")
+      println("New dungeon (ID: " + myID + ") generated!")
     }
     case GameSay(name, msg) => {
       val roomNum = findRoom(name)
@@ -96,7 +103,7 @@ class Dungeon extends Actor {
     }
 
     case GameAddPlayer(name) => {
-      println("Adding player " + name)
+      println("(Dungeon: " + myID + ") Adding player " + name)
       PSet foreach (c => if (name.compareToIgnoreCase(c) != 0) PMap ! PMapSendGameMessage(c, GamePlayerEnter(name)))
       var PString = ""
       PSet foreach (c => PString = c + "\n" + PString)
@@ -110,12 +117,11 @@ class Dungeon extends Actor {
     }
 
     case GamePlayerMove(name, dir, index) => {
-      println("Moving player " + name)
+      println("(Dungeon: " + myID + ") Moving player " + name)
       //val room = findRoom(name)
       rooms(index).getPlayerList.foreach(c => if (c != name) { PMap ! PMapSendGameMessage(c, GameMessage("ROOMLEFT " + name)) })
       val coord = indexToCoords(index)
       if (rooms(index).canMove(dir)) {
-        println("Can move player.")
         val move =
           dir match {
[…]

### 2014-06-03 src/lostvaults/server/Player.scala

@@ -110,7 +110,7 @@ class Player extends Actor {
       connection = sender
       db = Some(Database.forURL("jdbc:sqlite:lostvaults.db", driver = "org.sqlite.JDBC"))
       val decodedMsg = msg.decodeString(java.nio.charset.StandardCharsets.UTF_8.name)
-      println("(Player) Received message: " + decodedMsg)
+      println("(Player ["+ name + "]) sent message: " + decodedMsg)
       if (Parser.findWord(decodedMsg, 0) == "LOGIN") {
         name = Parser.findWord(decodedMsg, 1)
         PMap ! PMapIsOnline(name, decodedMsg)
@@ -120,13 +120,11 @@ class Player extends Actor {
       {
         println("PMap Response.")
         if (Parser.findWord(purpose, 0) == "LOGIN") {
-          println("Login detected!")
+          println("Login detected.")
           if (response) {
-            println("Player already logged in.")
             pushToNetwork("LOGINFAIL")
             context stop self
           } else {
-            println("Checking for player exists...")
             implicit val session = db.get.createSession()
             // This guy's not online, check if the passwords match.
             val pass = Parser.findRest(purpose, 1)
@@ -186,7 +184,7 @@ class Player extends Actor {
         }
         case Received(msg) => {
           val decodedMsg = msg.decodeString(java.nio.charset.StandardCharsets.UTF_8.name())
-          println("(Player[" + name + "]) Received message: " + decodedMsg)
+          println("(Player[" + name + "]) sent message: " + decodedMsg)
           val action = Parser.findWord(decodedMsg, 0).toUpperCase
           action match {
             case "ACK" => {
@@ -487,7 +485,6 @@ class Player extends Actor {
         }
 
         case _: ConnectionClosed => {
-          println("Connection closed event.")
           dungeon ! GameRemovePlayer(name)
           PMap ! PMapRemovePlayer(name)
           context stop self

### 2014-06-03 src/lostvaults/server/RoomGenerator.scala
-

@@ -31,7 +31,7 @@ class RoomGenerator {
     (c._1 < 0 || c._1 >= Width || c._2 < 0 || c._2 >= Height)
   }
   def rand(min: Int, max: Int) = {
-    (min + (Rnd.nextFloat() * (max - min))).asInstanceOf[Int]
+    min + (Rnd.nextFloat() * (max - min).asInstanceOf[Float]).asInstanceOf[Int]
   }
 
   def findEmptyRoom(depth: Int): (Int, Int) = {
@@ -42,11 +42,9 @@ class RoomGenerator {
 
   def addItemsToRoom(X: Int, Y: Int) {
     if (X != startRoom._1 || Y != startRoom._2) {
-      var howMany = rand(0, 3)
+      var howMany = rand(1, 3)
       var range = (((((startRoom._1 - X).abs.asInstanceOf[Double] + (startRoom._2 - Y).abs.asInstanceOf[Double])) / 16.0) * 10.0).ceil.asInstanceOf[Int] - 1
       if (range == 0) range = 1
-      println(startRoom._1 + " - " + X + " + " + startRoom._2 + " - " + Y + " / 16 *  10 = " + range)
-      println("ROOMGENERATOR-addItemsToRoom: This is the range: " + range)
       var items = ItemRepo.getManyRandom(howMany, "NoTreasure", range)
       items foreach (i => rooms(coordToIndex(X, Y)).addItem(i))
       itemcnt += items.length
@@ -54,7 +52,6 @@ class RoomGenerator {
       items = ItemRepo.getManyRandom(howMany, "Treasure", range)
       items foreach (i => rooms(coordToIndex(X, Y)).addItem(i))
       items foreach (i => print(i.name))
-      println("\nROOMGENERATOR-addItemsToRoom: This is the range: " + range)
       itemcnt += items.length
       itemrooms += 1
     }
@@ -64,11 +61,8 @@ class RoomGenerator {
       var howMany = rand(0, 1)
       var range = (((((startRoom._1 - X).abs.asInstanceOf[Double] + (startRoom._2 - Y).abs.asInstanceOf[Double])) / 16.0) * 10.0).ceil.asInstanceOf[Int] - 1
       if (range == 0) range = 1
-      println("ROOMGENERATOR-addNPCToRoom: This is the range: " + range)
-      println(startRoom._1 + " - " + X + " + " + startRoom._2 + " - " + Y + " / 16 *  10 = " + range)
[…]

### 2014-06-03 doc/src/draft.tex

@@
 
-Vi har också skapat ett administrationsverktyg som gör att man i terminalen kan ge spelare objekt, återställa hälsan så att spelaren får fullt HP\footnote{HP står för Health Points, vilket är hur mycket liv spelaren har vid givet tillfälle} och skada den genom att bestämma hur mycket HP som ska dras av (man kan inte döda en spelare).
-Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla salarna.
+Vi har också skapat ett administrationsverktyg som gör att man i terminalen kan ge spelare föremål, återställa hälsan så att spelaren får fullt HP\footnote{HP står för Health Points, vilket är hur mycket liv spelaren har vid givet tillfälle} och skada den genom att bestämma hur mycket HP som ska dras av (man kan inte döda en spelare).
+Detta gjorde vi för att kunna testa spelet och för att kunna visa upp hur det faktiskt fungerar utan att behöva leta genom alla rum.
 
 Något vi gjorde bra var att vi gjorde klart det essentiella för huvudmålet med projektet, att uppnå concurrency på något sätt.
-Spelet hanterar många individuella aktörer, och klarar av att hantera massiva uppkopplingar mot dess server.
+Spelet hanterar många individuella aktörer, och klarar av att hantera flertalet uppkopplingar mot dess server.
 Då den delen av projektet var klart kunde vi utöka produkten med funktioner för att göra spelet roligare och mer interaktivt.
-Implementation av föremål och monster att slåss mot i grottan. 
-Något vi lärt oss är att skriva nätverkskod. Vi har även fått kunskap i ett nytt programspråk.
-Det vi tycker har varit svårt var bland annat att integrationstesta våra aktörer. Svårigheterna uppstod på grund av bristande 
-information att ta del av om hur vi skulle gå till väga för att göra detta. En annan sak som också varit relativt svår var att 
+
+Något vi lärt oss är att skriva nätverkskod. Det var ganska komplicerat och svårt att förstå akkas dokumentation, vilket vi hade problem med i början. Vi har även fått kunskap i ett nytt programspråk.
+
+Vi tyckte det var svårt att bland annat integrationstesta våra aktörer. Svårigheterna uppstod på grund av bristande information att ta del av om hur vi skulle gå till väga för att göra detta.
+Vi har arbetat med automatiserad testing medan vi har byggt upp vårt spel.
+Men på grund av aktöruppbyggnaden av vårt program har det vara svårt att göra annat än enhetstester, och dessa har endast gett ytlig testning av spelet, då mängder av olika händelseförlopp kan inträffa.
+Så för att uppväga våra brister i automatiserade tester har vi helt enkelt testkört spelet många gånger.
+
+ En annan sak som vi tyckte var svårt var att 
 begränsa oss när det gällde den utsträckning för vilket spelet skulle utvecklas. Att begränsa utvecklingen till en rimlig nivå för spelet 
@@
 
-En stor sak som vi inte han med under projektets gång är att implementera uppdrag. Detta är vad vårt nästa steg skulle vara, nu när det grundläggande fungerar som det ska.
+En stor sak som vi inte hann med under projektets gång är att implementera uppdrag.
+Utan uppdrag missar spelet sitt djup, och lyckas inte riktigt fånga spelaren.
+Dessutom ska spelet ha fällor i vissa rum, för att göra färden genom grottorna blir farligare.
+
+Något som förvånade oss med projektet var hur lång tid saker tar att få klart.
+I många delar hittade vi buggar som var tvugna att åtgärdas, vilket ledde till att den delen drog ut på tiden.
+Men vi blev ändå klara så långt som var vår minimumplan.
+
+Vi gjorde aldrig någon långsiktig planering, som t.ex.
+en ordning av när saker ska göras och vem som skulle göra det.
+Vi arbetade ganska fritt utifrån vår ursprungliga idé och kom på vad som var nästa sak som skulle fokuseras på då en sak hade blivit färdigt.
+Detta fungerade ganska bra, men krävde att vi ofta hade gruppmöten för att planera vad som skulle göras härnäst.
+
+Överlag har projektet gått bra. Vi har fungerat bra som grupp, haft bra kommunikation och arbetet har fortskridit på ett bra sätt.
 

### 2014-06-03 src/lostvaults/client/GUI.java
Fixed combat

@@ -26,6 +26,10 @@ public class GUI {
 	JTextArea exits = new JTextArea();
 	JLabel healthStats = new JLabel();
 	JLabel combatStats = new JLabel();
+	JLabel playersInDungeon = new JLabel(" Players In City: ");
+	JLabel playersInRoom = new JLabel(" Players In Room: ");
+	JLabel itemsInRoom = new JLabel(" Items In Room: ");
+	JLabel npcsInRoom = new JLabel(" NPC In Room: ");
 	JFrame window = new JFrame("The Lost Vaults");
 
 	Color darkBackground = new Color(0x800000);
@@ -82,12 +86,12 @@ public class GUI {
 		statsPanel.add(healthStats, BorderLayout.NORTH);
 		statsPanel.add(combatStats, BorderLayout.CENTER);
 
-		JPanel dungeonPlayersPanel = createRightBox(dungeonPlayers,
+		JPanel dungeonPlayersPanel = createRightBox(dungeonPlayers, playersInDungeon,
 				"Players in Dungeon: ");
-		JPanel roomPlayersPanel = createRightBox(roomPlayers,
+		JPanel roomPlayersPanel = createRightBox(roomPlayers, playersInRoom,
 				"Players in Room: ");
-		JPanel npcsPanel = createRightBox(npcs, "NPCs in Room: ");
-		JPanel itemsPanel = createRightBox(items, "Items in Room: ");
+		JPanel npcsPanel = createRightBox(npcs, npcsInRoom, "NPCs in Room: ");
+		JPanel itemsPanel = createRightBox(items, itemsInRoom, "Items in Room: ");
 
 		exits.setFont(font);
 		exits.setForeground(textColor);
@@ -158,14 +162,13 @@ public class GUI {
 	/*******************************************
 	 * * Right window in the GUI * *
 	 *******************************************/
-	public JPanel createRightBox(JTextArea c, String label) {
+	public JPanel createRightBox(JTextArea c, JPanel cLabel, String label) {
 		c.setFont(font);
 		c.setForeground(textColor);
 		c.setBackground(mediumBackground);
 		c.setEditable(false);
 		JScrollPane cScroll = new JScrollPane(c);
 		cScroll.setBorder(BorderFactory.createEmptyBorder());
-		JLabel cLabel = new JLabel(label);
 		cLabel.setForeground(textColor);
 		cLabel.setFont(bigFont);
 		JPanel cPanel = new JPanel(new BorderLayout());

### 2014-06-03 src/lostvaults/server/NPC.scala

@@ -7,7 +7,6 @@ object NPC {
   def props(name: String, hp: Int, rating: Int, dungeon: ActorRef, room: Int): Props = Props(new NPC(name, hp, rating, dungeon, room: Int))
 }
 
-
 class NPC(_name: String, _hp: Int, _rating: Int, _dungeon: ActorRef, _room: Int) extends Actor {
   var rand = new Random(System.currentTimeMillis())
   var name = _name
@@ -23,9 +22,8 @@ class NPC(_name: String, _hp: Int, _rating: Int, _dungeon: ActorRef, _room: Int)
   var battle: Option[ActorRef] = None
   var rating = _rating
 
-
   def getSpeed = {
-    weapon.speed + armor.speed + rating/2
+    weapon.speed + armor.speed + rating / 2 + 1
   }
   def getAttack = {
     weapon.attack + armor.attack
@@ -35,7 +33,7 @@ class NPC(_name: String, _hp: Int, _rating: Int, _dungeon: ActorRef, _room: Int)
   }
 
   def receive = {
-    case GamePlayerJoinBattle(_battle, enemy) => {      
+    case GamePlayerJoinBattle(_battle, enemy) => {
       println("NPC: GamePlayerJoinBattle received, target is \"" + target + "\"")
       battle = Some(_battle)
       _battle ! AddPlayer(self, name, getSpeed, enemy)
@@ -59,18 +57,17 @@ class NPC(_name: String, _hp: Int, _rating: Int, _dungeon: ActorRef, _room: Int)
           battle.get ! RemovePlayer(name)
           battle = None
         }
-        target = ""
         context stop self
       } else {
         dungeon ! GameNotifyRoom(room, "NPC " + name + " has received " + damage + " damage from " + from + ".")
         if (battle != None) {
           battle.get ! DamageAck
         }
-        target = ""
       }
     }
     case GameCombatWin => {
       battle = None
+      target = ""
     }
   }
 }

### 2014-06-03 src/lostvaults/server/Dungeon.scala
--

@@ -244,6 +244,7 @@ class Dungeon(id: Int) extends Actor {
             println("(Dungeon: " + myID + ") Adding " + attacker + " to combat")
             PMap ! PMapSendGameMessage(attacker, GamePlayerJoinBattle(rooms(currentRoom).activeCombat.get, attackee))
             PMap ! PMapSendGameMessage(attacker, GameMessage("You have attacked " + attackee))
+            PMap ! PMapSendGameMessage(attacker, GamePlayerSetTarget(attackee))
           } else {
             PMap ! PMapSendGameMessage(attacker, GameAttackNotInRoom(attackee))
           }
@@ -336,9 +337,11 @@ class Dungeon(id: Int) extends Actor {
 
   def CityReceive: Receive = {
     case GMapJoin(joinee, group) => {
+      println("(City) Player " + joinee + " wants to join " + group + "'s group.")
       GMap ! GMapJoin(joinee, group)
     }
     case GMapLeave(name) => {
+      println("(City) Player " + name + " wants to leave their group.")
       GMap ! GMapLeave(name)
     }
     case GameSay(name, msg) => {
@@ -347,6 +350,7 @@ class Dungeon(id: Int) extends Actor {
     }
 
     case GameAddPlayer(name) => {
+      println("(City) Player " + name + " joined the City.")
       PSet foreach (c => if (name != c) PMap ! PMapSendGameMessage(c, GamePlayerEnter(name)))
       var PString = ""
       PSet foreach (c => PString = c + "\n" + PString)
@@ -356,6 +360,7 @@ class Dungeon(id: Int) extends Actor {
     }
 
     case GameRemovePlayer(name) => {
+      println("(City) Player " + name + " left the City.")
       PSet -= name
       PSet foreach (c => if (name != c) PMap ! PMapSendGameMessage(c, GamePlayerLeft(name))) // Send "GamePlayerLeft" to all other players*/
     }
@@ -370,7 +375,7 @@ class Dungeon(id: Int) extends Actor {
       GMap ! GMapEnterDungeon(name)
     }
     case PMapFailure => {
-      println("(Dungeon: " + myID + ") Failed to send a player a message.")
+      println("(City) Failed to send a player a message.")
     }
   }
 }

### 2014-06-03 src/lostvaults/server/Player.scala

@@ -483,6 +483,10 @@ class Player extends Actor {
             }
           }
         }
+        
+        case GamePlayerSetTarget(newTarget) => {
+          target = newTarget
+        }
 
         case _: ConnectionClosed => {
           dungeon ! GameRemovePlayer(name)

### 2014-06-03 src/lostvaults/server/GameMsg.scala
---

@@ -1,3 +1,4 @@
+
 package lostvaults.server
 import akka.actor.{ActorRef}
 /**
@@ -197,5 +198,6 @@ case class GameHarm(amnt: Int) extends GameMsg
  * @param name The name of the NPC
  * @param room The room the NPC is in
  */
-case class GameRemoveNPCFromRoom(name: String, room: Int)
+case class GameRemoveNPCFromRoom(name: String, room: Int) extends GameMsg
 
+case class GamePlayerSetTarget(newTarget: String) extends GameMsg

### 2014-06-03 src/lostvaults/server/GroupMap.scala

@@ -68,6 +68,7 @@ case class GMapEnterDungeon(name: String) extends GMapMsg
 case class GMapExitDungeon(name: String) extends GMapMsg
 
 class GroupMap extends Actor {
+  var nextID = 1
   val PMap = Main.PMap.get
   var groupMap: HashMap[String, PlayerGroup] = HashMap()
   def _FindName(name: String): Option[PlayerGroup] = {
@@ -149,7 +150,8 @@ class GroupMap extends Actor {
         var join = new PlayerGroup
         join.addPlayer(name)
         PMap ! PMapSendGameMessage(name, GameSystem("Entering dungeon..."))
-        val newDungeon = context.actorOf(Props[Dungeon])
+        val newDungeon = context.actorOf(Dungeon.props(nextID))
+        nextID += 1
         newDungeon ! NewDungeon
         newDungeon ! GameAddPlayer(name)
         groupMap(name) = join
@@ -158,7 +160,8 @@ class GroupMap extends Actor {
         group.setReady(name)
         if (group isGroupReady) {
           group.groupSendMessage(GameSystem("All players ready! Entering dungeon..."))
-          val newDungeon = context.actorOf(Props[Dungeon])
+          val newDungeon = context.actorOf(Dungeon.props(nextID))
+          nextID += 1
           newDungeon ! NewDungeon
           val list = group.listPlayers
           println("Putting players " + list + " into new dungeon.")

### 2014-06-03 src/lostvaults/server/Main.scala

@@ -17,7 +17,7 @@ object Main {
     val gmap = system.get.actorOf(Props[GroupMap])
     GMap = Some(gmap)
     val conMan = system.get.actorOf(Props[ConMan])
-    City = Some(system.get.actorOf(Props[Dungeon]))
+    City = Some(system.get.actorOf(Dungeon.props(0)))
     City.get ! DungeonMakeCity
     CheatActor = Some(system.get.actorOf(Props[CheatActor]))
   }

### 2014-06-03 src/lostvaults/server/NPCRepo.scala

@@ -21,7 +21,7 @@ object NPCRepo {
   }
   populateArray
   def rand(min: Int, max: Int) = {
-    (min + (random.nextFloat() * (max - min))).asInstanceOf[Int]
+    min + (random.nextFloat() * (max - min).asInstanceOf[Float]).asInstanceOf[Int]
   }
   def getRandomNPC(system: ActorSystem, dungeon: ActorRef, rating: Int, room: Int): (String, ActorRef) = {
     val ratingList = npcList.filter(c => c.rating <= rating)

### 2014-06-03 src/lostvaults/server/Room.scala

@@ -241,7 +241,6 @@ class Room() {
 
   def createRoomDesc {
     roomDesc = RoomDescGen.generateDescription(NPCList.map(c => c._1), itemList.map(c => c.name), getExitsList)
-    println(roomDesc)
   }
   
   /**

### 2014-06-03 src/lostvaults/server/RoomGenerator.scala

@@ -51,7 +51,6 @@ class RoomGenerator {
       howMany = rand(0, 3)
       items = ItemRepo.getManyRandom(howMany, "Treasure", range)
       items foreach (i => rooms(coordToIndex(X, Y)).addItem(i))
-      items foreach (i => print(i.name))
       itemcnt += items.length
       itemrooms += 1
     }
@@ -62,7 +61,6 @@ class RoomGenerator {
       var range = (((((startRoom._1 - X).abs.asInstanceOf[Double] + (startRoom._2 - Y).abs.asInstanceOf[Double])) / 16.0) * 10.0).ceil.asInstanceOf[Int] - 1
       if (range == 0) range = 1
       var npcs = NPCRepo.getManyRandom(howMany, system, dungeon, range, coordToIndex(X, Y))
-      npcs foreach (i => print(i._1))
       npcs foreach (i => rooms(coordToIndex(X, Y)).addNPC(i))
     }
   }

### 2014-06-03 src/lostvaults/client/GUI.java
Now Everythaaangh is workaang

@@ -11,7 +11,7 @@ public class GUI {
 	 *******************************************/
 	String name;
 	String passwordstr;
-	
+
 	int screenWidth;
 	int screenHeight;
 
@@ -86,12 +86,13 @@ public class GUI {
 		statsPanel.add(healthStats, BorderLayout.NORTH);
 		statsPanel.add(combatStats, BorderLayout.CENTER);
 
-		JPanel dungeonPlayersPanel = createRightBox(dungeonPlayers, playersInDungeon,
-				"Players in Dungeon: ");
+		JPanel dungeonPlayersPanel = createRightBox(dungeonPlayers,
+				playersInDungeon, "Players in Dungeon: ");
 		JPanel roomPlayersPanel = createRightBox(roomPlayers, playersInRoom,
 				"Players in Room: ");
 		JPanel npcsPanel = createRightBox(npcs, npcsInRoom, "NPCs in Room: ");
-		JPanel itemsPanel = createRightBox(items, itemsInRoom, "Items in Room: ");
+		JPanel itemsPanel = createRightBox(items, itemsInRoom,
+				"Items in Room: ");
 
 		exits.setFont(font);
 		exits.setForeground(textColor);
@@ -162,7 +163,7 @@ public class GUI {
 	/*******************************************
 	 * * Right window in the GUI * *
 	 *******************************************/
-	public JPanel createRightBox(JTextArea c, JPanel cLabel, String label) {
+	public JPanel createRightBox(JTextArea c, JLabel cLabel, String label) {
 		c.setFont(font);
 		c.setForeground(textColor);
 		c.setBackground(mediumBackground);
@@ -338,7 +339,7 @@ public class GUI {
 	public String getName() {
 		return name;
 	}
-	
+
 	public String getPass() {
 		return passwordstr;
 	}
@@ -346,6 +347,13 @@ public class GUI {
 	public void updateDynamicInfo(String msg) {
 		dynamicInfo.append(msg + "\n");
 		dynamicInfo.setCaretPosition(dynamicInfo.getDocument().getLength());
+	}
+	public void setLabelCity() {
+		playersInDungeon.setText(" Players In City: ");
+	}
+
+	public void setLabelDungeon() {
+		playersInDungeon.setText(" Players In Dungeon: ");
 	}
 
 	public void setHealthStats(String stats) {
@@ -412,7 +420,7 @@ public class GUI {
 		item = item.replace(")", "\\)");
[…]

### 2014-06-03 src/lostvaults/client/PlayGameCommunication.scala

@@ -47,6 +47,12 @@ object playGameCommunication {
 	def setCombatStats(stats: String) {
 		gui.setCombatStats(stats)
 	}
+	def setLabelCity {
+	  gui.setLabelCity
+	}
+	def setLabelDungeon {
+	  gui.setLabelDungeon
+	}
   /**
    * s
    * This method will replace the current list of players in the dungeon, shown by the GUI, with the given list of players.

### 2014-06-03 src/lostvaults/server/Room.scala
Room cleanup

@@ -107,8 +107,6 @@ class Room() {
     playerList.find(f => f.compareToIgnoreCase(player) == 0) != None
   }
 
-  // TESTAT FRAM TILL DENNA PUNKT
-
   /**
    * This method adds an item to the list of items in a room.
    * @param newItem The name of the item to be added.
@@ -119,29 +117,26 @@ class Room() {
 
   /**
    * This method removes an item from the list of items in a room.
-   * @param item The name of the item to be removed.
+   * @param item The name of the Item to be removed.
    */
   def removeItem(item: Item) = {
     itemList = itemList.filterNot((c => c == item))
   }
 
   /**
-   * This method returns the list of items in a room.
-   * @return the items in the room
+   * This method returns the list of Items in a room.
+   * @return the Items in the room
    */
   def getItemList(): List[Item] = {
     itemList
   }
 
   /**
-   *
+   * Removes an Item from this Room and returns it.
+   * @param the name of the Item
    */
   def takeItem(_name: String): Item = {
     val ret = itemList.find(i => i.name.compareToIgnoreCase(_name) == 0).get
-    //    if (ret != None) {
-    //      removeItem(ret)
-    //      ret
-    //    }
     removeItem(ret)
     ret
   }
@@ -202,43 +197,17 @@ class Room() {
     }
   }
 
-  /**
-   * This method returns a string describing the
-   * players, items and possible exits in this room.
-   * @param name the name of the player wanting the description
-   * @return representation of the exits,items  and players in this room
-   */
-  /*def getDescription(name: String): String = {
-    var ret = "You are standing in a wide, open room.\n"
-    ret += "You see exits to the:" + "\n"
-    if (exits(0))
-      ret += "North\n"
-    if (exits(1))
-      ret += "East\n"
-    if (exits(2))
-      ret += "South\n"
-    if (exits(3))
-      ret += "West\n"
-    if (startRoom)
-      ret += "You also see an exit to the city above.\n"
-    if (!itemList.isEmpty) {
-      ret += "On the floor you find: \n"
-      itemList.foreach(item => ret += item.name + "\n")
-    }
-    if (!NPCList.isEmpty) {
-      ret += "You suddenly see: \n"
-      NPCList.foreach(npc => ret += npc._1 + "\n")
-    }
-    if (playerList.size > 1) {
-      ret += "With you is: \n"
[…]

### 2014-06-03 src/lostvaults/server/Dungeon.scala
dungeon city

@@ -176,6 +176,7 @@ class Dungeon extends Actor {
       PSet -= name
       PSet foreach (c => if (name != c) PMap ! PMapSendGameMessage(c, GamePlayerLeft(name))) // Send "GamePlayerLeft" to all other players
       Main.City.get ! GameAddPlayer(name)
+      PMap ! PMapSendGameMessage(name, GameMessage("GUICITY"))
       PMap ! PMapSendGameMessage(name, GameMoveToDungeon(Main.City.get))
       GMap ! GMapExitDungeon(name)
       if (PSet isEmpty) {

### 2014-06-03 src/lostvaults/server/GroupMap.scala

@@ -149,6 +149,7 @@ class GroupMap extends Actor {
         var join = new PlayerGroup
         join.addPlayer(name)
         PMap ! PMapSendGameMessage(name, GameSystem("Entering dungeon..."))
+        PMap ! PMapSendGameMessage(name, GameMessage("GUIDUNGEON"))
         val newDungeon = context.actorOf(Props[Dungeon])
         newDungeon ! NewDungeon
         newDungeon ! GameAddPlayer(name)
@@ -158,6 +159,7 @@ class GroupMap extends Actor {
         group.setReady(name)
         if (group isGroupReady) {
           group.groupSendMessage(GameSystem("All players ready! Entering dungeon..."))
+          PMap ! PMapSendGameMessage(name, GameMessage("GUIDUNGEON"))
           val newDungeon = context.actorOf(Props[Dungeon])
           newDungeon ! NewDungeon
           val list = group.listPlayers

### 2014-06-04 src/lostvaults/server/Combat.scala
---

@@ -143,8 +143,9 @@ class Combat (_dungeon: ActorRef, _roomIndex: Int, dungeonId: Int, id: Int) exte
       combatList = combatList map (c => (c._1, c._2 filterNot (d => d.equals(name))))
       var nextPlayerList = data.PlayerList.filterNot(x => x._1.equals(name))
       nextTurnList = data.TurnList.filterNot(x => x.equals(name))
+      dungeon ! GameRemoveFromRoom(name, roomIndex) 
       /**Now all ocurrences of name has been removed, lets remove all players that had name as their last enemy: **/
-
+      
       //Removes players that has emptied their combatPerPlayer list from nextPlayerList and nextTurnList, and notifies them that they won
       combatList foreach (c => if (c._2 isEmpty) { combatSendGameMsg(c._1, data.PlayerList, GameCombatWin); nextPlayerList = nextPlayerList filterNot (d => d._1 == c._1) })
       combatList foreach (c => if (c._2 isEmpty) { nextTurnList = nextTurnList filterNot (d => d == c._1) })

### 2014-06-04 src/lostvaults/server/Dungeon.scala

@@ -108,7 +108,7 @@ class Dungeon(id: Int) extends Actor {
       var PString = ""
       PSet foreach (c => PString = c + "\n" + PString)
       PSet += name
-      PMap ! PMapSendGameMessage(name, GameMoveToDungeon(self))
+      //PMap ! PMapSendGameMessage(name, GameMoveToDungeon(self))
       PMap ! PMapSendGameMessage(name, GameMessage("DUNGEONLIST " + PString))
       rooms(entrance).addPlayer(name)
       PMap ! PMapSendGameMessage(name, GameDungeonMove(entrance, true))
@@ -167,6 +167,11 @@ class Dungeon(id: Int) extends Actor {
         PMap ! PMapSendGameMessage(name, GameSystem("You cannot move in that direction."))
       }
     }
+    
+    case GameRemoveFromRoom(name, roomIndex) => {
+    	rooms(roomIndex).removePlayer(name)
+    }
+    
     case GameExitDungeon(name) => {
       val room = findRoom(name)
       if (room != entrance)
@@ -178,10 +183,13 @@ class Dungeon(id: Int) extends Actor {
     case GameRemovePlayer(name) => {
       PSet -= name
       PSet foreach (c => if (name != c) PMap ! PMapSendGameMessage(c, GamePlayerLeft(name))) // Send "GamePlayerLeft" to all other players
-      Main.City.get ! GameAddPlayer(name)
       PMap ! PMapSendGameMessage(name, GameMessage("GUICITY"))
       PMap ! PMapSendGameMessage(name, GameMoveToDungeon(Main.City.get))
       GMap ! GMapExitDungeon(name)
+      PMap ! PMapSendGameMessage(name, GameMessage("ROOMEXITS "))
+      PMap ! PMapSendGameMessage(name, GameMessage("NPCLIST "))
+      PMap ! PMapSendGameMessage(name, GameMessage("ITEMLIST "))
+      PMap ! PMapSendGameMessage(name, GameMessage("ROOMLIST "))
       if (PSet isEmpty) {
         // Give quest rewards.
         context stop self
@@ -200,14 +208,10 @@ class Dungeon(id: Int) extends Actor {
           nameMatches = (compareStrings(attackee, name), name) :: nameMatches
         }
       })
-      if (nameMatches isEmpty) { // Not a player, check NPCs.
-        val npcs = rooms(findRoom(attacker)).NPCList
-        npcs foreach (name => {
[…]

### 2014-06-04 src/lostvaults/server/GroupMap.scala

@@ -160,6 +160,7 @@ class GroupMap extends Actor {
         var group = groupOp.get
         group.setReady(name)
         if (group isGroupReady) {
+          group.inDungeon = true
           group.groupSendMessage(GameSystem("All players ready! Entering dungeon..."))
           val newDungeon = context.actorOf(Dungeon.props(nextID))
           nextID += 1
@@ -167,7 +168,7 @@ class GroupMap extends Actor {
           newDungeon ! NewDungeon
           val list = group.listPlayers
           println("Putting players " + list + " into new dungeon.")
-          list.foreach(n => { groupMap(n) = group; newDungeon ! GameAddPlayer(n) })
+          list.foreach(n => { groupMap(n) = group; /*newDungeon ! GameAddPlayer(n); */PMap ! PMapSendGameMessage(n, GameMoveToDungeon(newDungeon)) })
         } else {
           group.groupSendMessage(GameSystem(name + " is ready to enter the dungeon!"))
         }

### 2014-06-04 doc/src/draft.tex
added the latest changes to the draft

@@
 Systemarkitekturen som beskrivs i detta dokument är uppdelat i två delar vilka beskriver akritekturen för klienten samt servern.
-På grund av att både klienten och servern är skrivna i Scala och körs via Java Virtual Maschine kan de köras på alla plattformar som stödjer Java VM 1.7.
+På grund av att både klienten och servern är skrivna i Scala och körs via Java Virtual Machine kan de köras på alla plattformar som stödjer Java VM 1.7.
 \begin{figure}[hbt]
@@
 Det textbaserade gränssnittet tillåter utökning av serversidan utan att kräva att användaren återinstallerar sin klient.
-Detta innebär att det är enkelt att åtgärda buggar och bygga ut spelet utan att söra användaren.
+Detta innebär att det är enkelt att åtgärda buggar och bygga ut spelet utan att störa användaren.
 
@@
 \includegraphics[width=1.0\textwidth]{serverActorModel2-1}
-\caption{\label{fig:ConManPlayer}Figur över förhållandet mellan ConMan och Player.}
+\caption{\label{fig:ConManPlayer}Figur över hur ConMan hanterar inkommande anslutningar.}
 \end{figure}
@@
 Anslutningslagret är ingångspunkten till servern över nätverket genom Akkas TCP bibliotek.
-Vår anslutningshanterare, ConMan, agerar som en singleton och endast en instans av denna ska existera vid en given tidpunkt.
+Vår anslutningshanterare, ConMan, agerar som en singleton dvs endast en instans av denna ska existera vid varje given tidpunkt.
 ConMan är den klass som lyssnar efter och godtar anslutningar från klienter, samt skapar nya Player-instanser vid nyupprättad anslutning.
@@
 Rummen i sin tur ansvarar för aktiva strider samt icke-spelarkaraktärer och objekt.
-Tidigare design visar att Item klassen används som superklass till olika typer av objekt.
+Tidigare design visar att Itemklassen används som superklass till olika typer av objekt.
 Vi valde dock att platta till vår klasshierarki och förenkla designen genom att låta alla typer av objekt vara instanser av Item klassen med olika attribut.
@@
 
-Sammansättningen av dokumentationen utförs med Scaladoc på grund av dess likhet med JavaDoc, ett verktyg vi är vana med att använda, och Ant har omarbetats för att automatiskt bygga dokumentationen.
+Sammansättningen av dokumentationen utförs med Scaladoc på grund av dess likhet med JavaDoc, ett verktyg vi är vana med att använda, och Ant har konfigurerats för att automatiskt bygga dokumentationen.
 
@@
 
-Versionen av Scala vi valde att använda har valt att tillfrån gå sitt egna aktörsbibliotek och istället använda sig av ett externt
+Versionen av Scala vi valde att använda har valt att tillfrångå sitt egna aktörsbibliotek och istället använda sig av ett externt
 bibliotek kallat Akka. Vårt projekt använder till följd även det Akkas bibliotek för implementationen av det aktörssystem som
@@
 Som nämnts tidigare valde vi att använda Aktörsmodellen som vår concurrencymodell därför att vi vid designen såg hur de olika 
-
 delarna av servern kunde delas in i till stor del självständiga moduler där minne inte behövde delas. Detta underlättade
